### 2021-08-20 proposal.tex
Initial commit, with the blank project proposal document.

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{import}

%Referencing
\import{reference-styles/}{authoryear.tex}
\addbibresource{bibliography/references.bib}
\usepackage{placeins} %Provides \FloatBarrier

%Title Page
\title{BIOL424 Project Proposal}
\author{
	Christopher Brown\\15413822
}
\date{}

\begin{document}
\maketitle

\FloatBarrier
\printbibliography
\end{document}

### 2021-08-20 proposal.tex
Add the section headings to the project proposal.
Add the background to the project proposal.

@@
 
+\section{Background}
+
+The simplest standard model of community dynamics is the Lotka--Volterra model, and this is frequently analysed to answer questions of species coexistence, community stability, and the like.
+It is parameterised by a vector of intrinsic growth rates, and a matrix of interaction coefficients.
+But even for such a simple model, this leads to the number of parameters scaling quadratically with the number of species: $n(n+1)$ parameters for $n$ species.
+This makes it infeasible to experimentally parameterise the model for realistically-sized communities.
+Can we do better?
+
+Species come in groups: this is the basis of taxonomy.
+And we might expect that species in the same group interact in similar ways, either in their effect on other species, or their response to them.
+This, in turn, may reduce the number of parameters we require.
+
+\section{Question}
+
+\section{Hypotheses}
+
+\section{Related Literature}
+
+\section{Novelty}
+
+\section{Method Outline}
+
 \FloatBarrier

### 2021-08-20 proposal.tex
Add the question to the project proposal.
Add the hypotheses to the project proposal.

@@
 
+Do species form groups that are sufficiently similar in their interaction coefficients that they might be considered equivalent in parameterising a model?
+If so, how?
+
 \section{Hypotheses}
+
+\begin{enumerate}
+	\item There will be some grouping of species such that a Lotka--Volterra model will fit better when parameterised with that grouping than when parameterised entirely ungrouped.
+	\item There will be no substantial benefit to model fit from grouping competitive effect and response separately, i.e.
+it will be sufficient to use the same groups for the rows as for the columns of the interaction matrix.
+	\item Some grouping informed solely by phylogeny, at some taxonimic level or similar, will prove near-optimal among groupings.
+\end{enumerate}
 

### 2021-08-21 proposal.tex
Load hyperref in the proposal document, to ensure papers are linked to.
The project specifications require links to cited papers.
Including DOIs in the bibliography and loading hyperref should fulfil this.
Add the relevant literature section to the project proposal.

@@
 \usepackage{placeins} %Provides \FloatBarrier
+
+\usepackage{hyperref}
 
@@
 
+In no particular order:
+\begin{itemize}
+	\item
+		\Textcite{allesina2009food} addressed the optimal grouping of species in order to reduce the number of parameters in a model.
+		However, they deal with food webs, rather than competitive interactions, and with binary links, rather than quantitative interactions.
+	\item
+		\Textcite{maynard2020predicting} provide a method of predicting the outcomes of community dynamics given the results of smaller set of experiments than would traditionally be required.
+		However, they do not parameterise a model in doing so, and can predict only the equilibrium points of assemblages.
+	\item
+		\Textcite{uriarte2004spatially} is one of a number of studies that have attempted to group species using groups selected \emph{a priori} based upon functional or phylogenetic factors.
+		In particular, the authors of this paper consider and compare both functional and phylogenetic groupings.
+		However, they still only consider four groupings, selected \emph{a priori}, out of more than a googol possible groupings.
+	\item
+		\Textcite{ovaskainen2017species} fitted models of community dynamics that were not parameterised directly by interaction coefficients, but by the responses of species to ``community-level drivers'': weighted averages of the abundances of various species in the community.
+		This is a similar technique to grouping (and in fact includes grouping as a subcase where weights are restricted to zero and one), but requires \emph{a priori} definition of the number of community-level drivers.
+		Further, its interpretation may be rather distinct from grouping, depending upon results.
+	\item
+		\Textcite{weiss2021disentangling} address the problem of too many parameters by making the assumption that many of the interaction coefficients are zero.
+		Precisely which coefficients are zero is selected on the basis of model fit, rather than \emph{a priori}.
+		However, this still assumes that many pairs of species do not interact: an assumption that need not be made by a model based on grouping.
+\end{itemize}
+
 \section{Novelty}

### 2021-08-21 proposal.tex
Add the statement of novelty to the project proposal.
Add the method outline to the project proposal.

@@
 
+As far as I am aware, my study will constitute the first attempt to select the optimal grouping, from among all possible groupings, of a competitive interaction matrix based on quality of model fit.
+
 \section{Method Outline}
+
+Data will consist of the results of species interaction experiments, covering at least each monoculture and pairwise configuration of approximately 7--9 species.
+It will be obtained from the studies examined by \textcite{kinlock2019meta}, or similar.
+
+Every possible grouping will be tested using a brute force method.
+Given $n$ species, this yields $B_n$ groupings of the rows and $B_n$ groupings of the columns, for $B_n^2$ groupings overall, where $B_n$ is the $n$th Bell number.
+$B_9^2 = \num{447195609}$, indicating that $9$ species will be approximately the upper feasible limit for this analysis.
+
+For each possible grouping, a Lotka--Volterra model, with intrinsic growth rates parameterised individually and competition coefficients parameterised according to the groupings, will be fitted to the model.
+The AIC of each such model shall be taken as the result, and the AIC values of different models may be examined to test the different hypotheses listed above.
+Particular attention will also be paid to the lowest AIC value of all configurations: the optimal model.
 

### 2021-10-05 src/io.hpp
Use const references to speed up output functions.

@@ -37,7 +37,7 @@ template<typename T> class OutputColumn {
 //The following functions use a template parameter pack.
 //It's impractical to explicitly instantiate this, so alas it must live in the header file.
 
-template<class T, class... OutputColumnTs> void outputTableHeader(std::ostream &stream, OutputColumn<T> column, OutputColumnTs... columns) {
+template<class T, class... OutputColumnTs> void outputTableHeader(std::ostream &stream, const OutputColumn<T>& column, const OutputColumnTs&... columns) {
 	column.printHeader(stream);
 	if constexpr(sizeof...(columns) > 0) {
 		stream << OUTPUT_TABLE_SEPARATOR;
@@ -45,7 +45,7 @@ template<class T, class... OutputColumnTs> void outputTableHeader(std::ostream &
 	}
 }
 
-template<class T, class... OutputColumnTs> void outputTableRow(std::ostream &stream, size_t row, OutputColumn<T> column, OutputColumnTs... columns) {
+template<class T, class... OutputColumnTs> void outputTableRow(std::ostream &stream, size_t row, const OutputColumn<T>& column, const OutputColumnTs&... columns) {
 	column.printElement(stream, row);
 	if constexpr(sizeof...(columns) > 0) {
 		stream << OUTPUT_TABLE_SEPARATOR;
@@ -53,7 +53,7 @@ template<class T, class... OutputColumnTs> void outputTableRow(std::ostream &str
 	}
 }
 
-template<class T, class... OutputColumnTs> void outputTable(const char *filename, OutputColumn<T> column, OutputColumnTs... columns) {
+template<class T, class... OutputColumnTs> void outputTable(const char *filename, const OutputColumn<T>& column, const OutputColumnTs&... columns) {
 	//We can't really iterate over the columns to check they're all the same length, so we're just going to assume.
 	//TODO: Improve this.
 	size_t numRows = column.getLength();

### 2021-10-05 src/data.hpp
Use const references throughout the code, for speed's sake.

@@ -19,7 +19,7 @@ class Data {
 		//The design density matrix, with numSpecies columns and numObservations rows.
 		Eigen::MatrixXd design;
 	public:
-		Data(std::vector<size_t> focal, Eigen::VectorXd response, Eigen::MatrixXd design):
+		Data(std::vector<size_t> focal, const Eigen::VectorXd &response, const Eigen::MatrixXd &design):
 			numSpecies(design.cols()), numObservations(design.rows()), focal(focal), response(response), design(design)
 		{
 			assert(focal.size() == numObservations);

### 2021-10-05 src/nls.cpp

@@ -1,21 +1,21 @@
 #include <Eigen/SVD>
 #include "nls.hpp"
 
-static bool checkTolerances(Eigen::VectorXd oldParameters, Eigen::VectorXd newParameters, Eigen::VectorXd tolerances) {
+static bool checkTolerances(const Eigen::VectorXd &oldParameters, const Eigen::VectorXd &newParameters, const Eigen::VectorXd &tolerances) {
 	for(size_t i = 0; i < (size_t)tolerances.size(); i++) {
 		if(abs(newParameters[i] - oldParameters[i]) > tolerances[i]) return false;
 	}
 	return true;
 }
 
-static Eigen::VectorXd gaussNewtonShift(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, Eigen::VectorXd parameters) {
+static Eigen::VectorXd gaussNewtonShift(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, const Eigen::VectorXd &parameters) {
 	//See https://eigen.tuxfamily.org/dox/group__LeastSquares.html for a comparison of methods.
 	Eigen::VectorXd residuals = residualsFunc(parameters);
 	Eigen::MatrixXd jacobian = jacobianFunc(parameters);
 	return jacobian.bdcSvd(Eigen::ComputeThinU | Eigen::ComputeThinV).solve(residuals);
 }
 
-Eigen::VectorXd gaussNewtonNLS(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, Eigen::VectorXd parameters, Eigen::VectorXd tolerances) {
+Eigen::VectorXd gaussNewtonNLS(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, Eigen::VectorXd parameters, const Eigen::VectorXd &tolerances) {
 	while(true) {
 		Eigen::VectorXd shift = gaussNewtonShift(residualsFunc, jacobianFunc, parameters);
 		Eigen::VectorXd newParameters = parameters - shift;

### 2021-10-05 src/nls.hpp

@@ -6,10 +6,10 @@
 //These functions take a vector of parameters, and return:
 //a vector of residuals, and
 //the Jacobian of the residuals with respect to the parameters.
-typedef std::function<Eigen::VectorXd(Eigen::VectorXd parameters)> ResidualsFunc;
-typedef std::function<Eigen::MatrixXd(Eigen::VectorXd parameters)> JacobianFunc;
+typedef std::function<Eigen::VectorXd(const Eigen::VectorXd &parameters)> ResidualsFunc;
+typedef std::function<Eigen::MatrixXd(const Eigen::VectorXd &parameters)> JacobianFunc;
 
 //Methods require a function to calculate the residuals, a function to calculate the Jacobian, an initial guess at the parameters, and tolerances for each parameter.
-extern Eigen::VectorXd gaussNewtonNLS(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, Eigen::VectorXd parameters, Eigen::VectorXd tolerances);
+extern Eigen::VectorXd gaussNewtonNLS(ResidualsFunc residualsFunc, JacobianFunc jacobianFunc, Eigen::VectorXd parameters, const Eigen::VectorXd &tolerances);
 
 #endif

### 2021-10-05 src/solver.cpp

@@ -7,11 +7,11 @@ size_t Solver::getGrowthRateIndex(size_t growthGroup) const {
 	return growthGroup;
 }
 
-double Solver::getGrowthRate(Solver::ParameterVector parameters, size_t growthGroup) const {
+double Solver::getGrowthRate(const Solver::ParameterVector &parameters, size_t growthGroup) const {
 	return parameters(getGrowthRateIndex(growthGroup));
 }
 
-Eigen::VectorXd Solver::getGrowthRates(Solver::ParameterVector parameters) const {
+Eigen::VectorXd Solver::getGrowthRates(const Solver::ParameterVector &parameters) const {
 	return parameters.segment(getGrowthRateIndex(0), growthGrouping.getNumGroups());
 }
 
@@ -19,11 +19,11 @@ size_t Solver::getCompetitionCoefficientIndex(size_t rowGroup, size_t colGroup) 
 	return growthGrouping.getNumGroups() + colGrouping.getNumGroups() * rowGroup + colGroup;
 }
 
-double Solver::getCompetitionCoefficient(Solver::ParameterVector parameters, size_t rowGroup, size_t colGroup) const {
+double Solver::getCompetitionCoefficient(const Solver::ParameterVector &parameters, size_t rowGroup, size_t colGroup) const {
 	return parameters(getCompetitionCoefficientIndex(rowGroup, colGroup));
 }
 
-Eigen::VectorXd Solver::getCompetitionCoefficientsRow(Solver::ParameterVector parameters, size_t rowGroup) const {
+Eigen::VectorXd Solver::getCompetitionCoefficientsRow(const Solver::ParameterVector &parameters, size_t rowGroup) const {
 	return parameters.segment(getCompetitionCoefficientIndex(rowGroup, 0), colGrouping.getNumGroups());
 }
 
@@ -89,7 +89,7 @@ Solver::ParameterVector Solver::getParameterTolerances() const {
 	return tolerances;
 }
 
-Eigen::VectorXd Solver::getPredictions(ParameterVector parameters) {
+Eigen::VectorXd Solver::getPredictions(const ParameterVector &parameters) {
 	Eigen::VectorXd predictions = Eigen::VectorXd::Zero(data.numObservations);
 	
 	Eigen::MatrixXd colGroupedDesign = getColGroupedDesign();
@@ -111,11 +111,11 @@ Eigen::VectorXd Solver::getPredictions(ParameterVector parameters) {
[…]

### 2021-10-05 src/solver.hpp

@@ -81,11 +81,11 @@ class Solver {
 		}
 	protected:
 		size_t getGrowthRateIndex(size_t growthGroup) const;
-		double getGrowthRate(ParameterVector parameters, size_t growthGroup) const;
-		Eigen::VectorXd getGrowthRates(ParameterVector parameters) const;
+		double getGrowthRate(const ParameterVector &parameters, size_t growthGroup) const;
+		Eigen::VectorXd getGrowthRates(const ParameterVector &parameters) const;
 		size_t getCompetitionCoefficientIndex(size_t rowGroup, size_t colGroup) const;
-		double getCompetitionCoefficient(ParameterVector parameters, size_t rowGroup, size_t colGroup) const;
-		Eigen::VectorXd getCompetitionCoefficientsRow(ParameterVector parameters, size_t rowGroup) const;
+		double getCompetitionCoefficient(const ParameterVector &parameters, size_t rowGroup, size_t colGroup) const;
+		Eigen::VectorXd getCompetitionCoefficientsRow(const ParameterVector &parameters, size_t rowGroup) const;
 		
 		void calculateColGroupedDesign();
 		Eigen::MatrixXd getColGroupedDesign();
@@ -93,10 +93,10 @@ class Solver {
 		ParameterVector getInitialParameterValues() const;
 		ParameterVector getParameterTolerances() const;
 		
-		Eigen::VectorXd getPredictions(ParameterVector parameters);
-		Eigen::VectorXd getResiduals(ParameterVector parameters);
+		Eigen::VectorXd getPredictions(const ParameterVector &parameters);
+		Eigen::VectorXd getResiduals(const ParameterVector &parameters);
 		
-		Jacobian getJacobian(ParameterVector parameters);
+		Jacobian getJacobian(const ParameterVector &parameters);
 		
 		void calculateSolution();
 	public:

### 2021-10-05 src/solver.cpp
Add Solver::getDeviance() and refactor Solver::getAIC() to use it.
I wanted to pull this function out earlier.
But negativeTwiceLogLikelihood was a terrible name, and I didn't know there was a better one.
Now I know that's called the deviance, so function extracted.
This will it easy to write Solver::getBIC() without code duplication.

@@ -163,7 +163,9 @@ Solver::ParameterVector Solver::getSolution() {
 	return solution;
 }
 
-double Solver::getAIC() {
+double Solver::getDeviance() {
+	//Returns the deviance.
+	//That is, the negative of twice the log likelihood.
 	ParameterVector parameters = getSolution();
 	Eigen::VectorXd residuals = getResiduals(parameters);
 	double sumOfSquares = residuals.dot(residuals);
@@ -180,11 +182,18 @@ double Solver::getAIC() {
 	//So the log likelihood is:
 	//-1/2 * log(2 * pi * variance) - 1/2 * residual^2 / variance
 	//And the total log likehood is just the sum of these.
-	//Note that, for AIC, we will be using twice the negative log likelihood.
+	//Note that the deviance is twice the negative log likelihood.
 	//This cancels the factor of -1/2.
-	double twiceNegativeLogLikelihood = residuals.size() * log(2 * M_PI * variance) + sumOfSquares / variance;
+	double deviance = residuals.size() * log(2 * M_PI * variance) + sumOfSquares / variance;
 	
-	double aic = 2 * parameters.size() + twiceNegativeLogLikelihood;
+	return deviance;
+}
+
+double Solver::getAIC() {
+	ParameterVector parameters = getSolution();
+	double deviance = getDeviance();
+	
+	double aic = 2 * parameters.size() + deviance;
 	
 	return aic;
 }

### 2021-10-05 src/solver.hpp

@@ -101,6 +101,7 @@ class Solver {
 		void calculateSolution();
 	public:
 		ParameterVector getSolution();
+		double getDeviance();
 		double getAIC();
 };
 

### 2021-10-05 article.rnw
Add the document for the article itself.

--- 2021-08-20 proposal.tex
@@
 
+\usepackage{hyperref}
+
 %Title Page
-\title{BIOL424 Project Proposal}
+\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping}
 \author{
-	Christopher Brown\\15413822
+	Christopher R. P. Brown
 }
@@
 
-\section{Background}
-
-The simplest standard model of community dynamics is the Lotka--Volterra model, and this is frequently analysed to answer questions of species coexistence, community stability, and the like.
-It is parameterised by a vector of intrinsic growth rates, and a matrix of interaction coefficients.
-But even for such a simple model, this leads to the number of parameters scaling quadratically with the number of species: $n(n+1)$ parameters for $n$ species.
-This makes it infeasible to experimentally parameterise the model for realistically-sized communities.
-Can we do better?
-
-Species come in groups: this is the basis of taxonomy.
-And we might expect that species in the same group interact in similar ways, either in their effect on other species, or their response to them.
-This, in turn, may reduce the number of parameters we require.
-
-\section{Question}
-
-Do species form groups that are sufficiently similar in their interaction coefficients that they might be considered equivalent in parameterising a model?
-If so, how?
-
-\section{Hypotheses}
-
-\begin{enumerate}
-	\item There will be some grouping of species such that a Lotka--Volterra model will fit better when parameterised with that grouping than when parameterised entirely ungrouped.
-	\item There will be no substantial benefit to model fit from grouping competitive effect and response separately, i.e.
-it will be sufficient to use the same groups for the rows as for the columns of the interaction matrix.
-	\item Some grouping informed solely by phylogeny, at some taxonimic level or similar, will prove near-optimal among groupings.
-\end{enumerate}
-
-\section{Related Literature}
-
-\section{Novelty}
-
-\section{Method Outline}
-
 \FloatBarrier

### 2021-10-05 r/brute-post-process.R
Add a helper script for post-processing the brute force data.

@@ -1,0 +1,5 @@
+#A set of helper functions for post-processing the data from brute forcing.
+#Does not read in any data; data must all be passed in by arguments.
+#Data is assumed to be passed as produced by the C++ program, however, with column names preserved.
+#Additionally, some of the functions rely on a vector of species names.
+#These must be provided in the order that the C++ program indexed the species.

### 2021-10-05 r/brute-post-process.R
Add a post processing function to validate the data.

@@ -3,3 +3,13 @@
 #Data is assumed to be passed as produced by the C++ program, however, with column names preserved.
 #Additionally, some of the functions rely on a vector of species names.
 #These must be provided in the order that the C++ program indexed the species.
+
+validate_data <- function(data, species_names) {
+	#Ensures that this is data for the correct number of species.
+	if(
+		length(grep("row_group", names(data))) != length(species_names) |
+		length(grep("col_group", names(data))) != length(species_names)
+	) {
+		stop("Data frame has the wrong number of species.")
+	}
+}

### 2021-10-05 src/solver.cpp
Add Solver::getR2() to get the coefficient of determination.

@@ -197,3 +197,17 @@ double Solver::getAIC() {
 	
 	return aic;
 }
+
+double Solver::getR2() {
+	//Returns R^2, the coefficient of determination.
+	
+	Eigen::VectorXd response = data.getResponse();
+	Eigen::VectorXd normalisedResponse = response - Eigen::VectorXd::Constant(response.size(), response.mean());
+	double totalSS = normalisedResponse.dot(normalisedResponse);
+	
+	ParameterVector parameters = getSolution();
+	Eigen::VectorXd residuals = getResiduals(parameters);
+	double residualSS = residuals.dot(residuals);
+	
+	return 1.0 - (residualSS / totalSS);
+}

### 2021-10-05 src/solver.hpp

@@ -103,6 +103,7 @@ class Solver {
 		ParameterVector getSolution();
 		double getDeviance();
 		double getAIC();
+		double getR2();
 };
 
 #endif

### 2021-10-05 src/brute.cpp
Add R squared values to the brute force output table.

@@ -62,16 +62,18 @@ int main(int argc, char **argv) {
 	OutputColumn<Grouping> outputRowGroupings("row_group");
 	OutputColumn<Grouping> outputColGroupings("col_group");
 	OutputColumn<double> outputAICs("aic");
+	OutputColumn<double> outputR2s("R2");
 	
 	do {
 		do {
 			outputRowGroupings.insert(solver.getRowGrouping());
 			outputColGroupings.insert(solver.getColGrouping());
 			outputAICs.insert(solver.getAIC());
+			outputR2s.insert(solver.getR2());
 		} while(solver.updateRowGrouping(&Grouping::advance));
 	} while(solver.updateColGrouping(&Grouping::advance));
 	
-	outputTable(outputFile, outputRowGroupings, outputColGroupings, outputAICs);
+	outputTable(outputFile, outputRowGroupings, outputColGroupings, outputAICs, outputR2s);
 	
 	return 0;
 }

### 2021-10-05 r/brute-post-process.R
Add functions for extracting groups to the brute helper code.

@@ -13,3 +13,10 @@ validate_data <- function(data, species_names) {
 		stop("Data frame has the wrong number of species.")
 	}
 }
+
+get_grouping <- function(data, index, grouping_prefix) {
+	as.vector(as.matrix(data[index, grep(grouping_prefix, names(data))]))
+}
+
+get_row_grouping <- function(data, index) {get_grouping(data, index, "row_group")}
+get_col_grouping <- function(data, index) {get_grouping(data, index, "col_group")}

### 2021-10-05 r/brute-post-process.R
Add a function for finding the number of species to the brute helper code.

@@ -14,6 +14,10 @@ validate_data <- function(data, species_names) {
 	}
 }
 
+get_num_species <- function(data) {
+	length(grep("row_group", names(data)))
+}
+
 get_grouping <- function(data, index, grouping_prefix) {
 	as.vector(as.matrix(data[index, grep(grouping_prefix, names(data))]))
 }

### 2021-10-05 r/brute-post-process.R
Rewrite the brute force post processing code using R6.

@@ -1,26 +1,43 @@
 #A set of helper functions for post-processing the data from brute forcing.
-#Does not read in any data; data must all be passed in by arguments.
-#Data is assumed to be passed as produced by the C++ program, however, with column names preserved.
-#Additionally, some of the functions rely on a vector of species names.
+#Works in an object-oriented fashion.
+#Constructing the central object requires a data file produced by the C++ program, with column names preserved.
+#Additionally, it requires a vector of species names.
 #These must be provided in the order that the C++ program indexed the species.
 
-validate_data <- function(data, species_names) {
-	#Ensures that this is data for the correct number of species.
-	if(
-		length(grep("row_group", names(data))) != length(species_names) |
-		length(grep("col_group", names(data))) != length(species_names)
-	) {
-		stop("Data frame has the wrong number of species.")
-	}
-}
-
-get_num_species <- function(data) {
-	length(grep("row_group", names(data)))
-}
-
-get_grouping <- function(data, index, grouping_prefix) {
-	as.vector(as.matrix(data[index, grep(grouping_prefix, names(data))]))
-}
-
-get_row_grouping <- function(data, index) {get_grouping(data, index, "row_group")}
-get_col_grouping <- function(data, index) {get_grouping(data, index, "col_group")}
+BruteData <- R6::R6Class("BruteData",
+	public = list(
+		num_species = NULL,
+		species_names = NULL,
+		row_groupings = NULL, #A data frame of row groupings, named by the species names.
+		col_groupings = NULL, #As above, for col groupings.
+		statistics = NULL, #A data frame of all output values besides groupings.
+		
+		initialize = function(data_file_name, species_names) {
+			data_table <- read.table(data_file_name, header=TRUE)
+			
+			self$num_species <- length(species_names)
+			self$species_names <- species_names
+			
+			private$validate_data(data_table, self$num_species)
+			
+			#Extract the groupings and other data.
+			self$row_groupings <- data_table[,grep("row_group", names(data_table))]
+			self$col_groupings <- data_table[,grep("col_group", names(data_table))]
+			names(self$row_groupings) <- species_names
+			names(self$col_groupings) <- species_names
+			self$statistics <- data_table[,grep("row_group|col_group", names(data_table), invert=TRUE)]
+		}
+	),
+	
+	private = list(
+		validate_data = function(data_table, num_species) {
+			#Checks whether a data table is for the correct number of species.
+			if(
[…]

### 2021-10-05 r/brute-post-process.R
1-index the groupings when reading them into R.

@@ -21,8 +21,9 @@ BruteData <- R6::R6Class("BruteData",
 			private$validate_data(data_table, self$num_species)
 			
 			#Extract the groupings and other data.
-			self$row_groupings <- data_table[,grep("row_group", names(data_table))]
-			self$col_groupings <- data_table[,grep("col_group", names(data_table))]
+			#Add one to the groupings to make them 1-indexed, as R prefers.
+			self$row_groupings <- data_table[,grep("row_group", names(data_table))] + 1
+			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
 			names(self$row_groupings) <- species_names
 			names(self$col_groupings) <- species_names
 			self$statistics <- data_table[,grep("row_group|col_group", names(data_table), invert=TRUE)]

### 2021-10-05 r/brute-post-process.R
Add functions to the brute post processing to select the fully grouped and fully separated cases.

@@ -39,6 +39,37 @@ BruteData <- R6::R6Class("BruteData",
 			) {
 				stop("Data table has the wrong number of species.")
 			}
+		},
+		
+		match_grouping = function(desired_grouping, grouping_table) {
+			#Returns the indices at which a row of grouping_table is equal to the vector desired_grouping.
+			
+			elementwise_match <- lapply(1:ncol(grouping_table), function(i) {
+				return(grouping_table[[i]] == desired_grouping[i])
+			})
+			
+			rowwise_match <- Reduce("&", elementwise_match)
+			
+			return(which(rowwise_match))
+		},
+		
+		get_statistics_row = function(row_grouping, col_grouping) {
+			#row_grouping and col_grouping should be vectors representing the groupings.
+			#Extracts one row of statistics, matching those groupings.
+			row_matches <- private$match_grouping(row_grouping, self$row_groupings)
+			col_matches <- private$match_grouping(col_grouping, self$col_groupings)
+			return(self$statistics[intersect(row_matches, col_matches),])
+		}
+	),
+	
+	active = list(
+		fully_grouped_statistics = function() {
+			grouping <- rep(1, self$num_species)
+			return(private$get_statistics_row(grouping, grouping))
+		},
+		fully_separated_statistics = function() {
+			grouping <- 1:self$num_species
+			return(private$get_statistics_row(grouping, grouping))
 		}
 	)
 )

### 2021-10-05 r/brute-post-process.R
Add a post processing function to calculate information criterion weights.

@@ -4,6 +4,14 @@
 #Additionally, it requires a vector of species names.
 #These must be provided in the order that the C++ program indexed the species.
 
+information_criterion_weights <- function(information_criterion) {
+	#Calculates Akaike weights from AIC values (or Schwarz weights from BIC values, etc.).
+	information_criterion <- information_criterion - min(information_criterion)
+	weights <- exp(-0.5 * information_criterion)
+	weights <- weights / sum(weights)
+	return(weights)
+}
+
 BruteData <- R6::R6Class("BruteData",
 	public = list(
 		num_species = NULL,

### 2021-10-05 r/brute-post-process.R
Add post processing code to get weighted coclassification matrices.

@@ -67,6 +67,24 @@ BruteData <- R6::R6Class("BruteData",
 			row_matches <- private$match_grouping(row_grouping, self$row_groupings)
 			col_matches <- private$match_grouping(col_grouping, self$col_groupings)
 			return(self$statistics[intersect(row_matches, col_matches),])
+		},
+		
+		get_coclassification_matrix = function(grouping_table, index) {
+			#Returns a binary matrix of whether two species are grouped together in a given row a grouping table.
+			grouping <- as.vector(as.matrix(grouping_table[index,]))
+			mat <- as.matrix(sapply(grouping, function(group) {
+				return(grouping == group)
+			}))
+			return(mat)
+		},
+		
+		get_weighted_coclassification_matrix = function(grouping_table) {
+			#Returns a coclassification matrix, as above, weighted by AIC weights.
+			weights <- information_criterion_weights(self$statistics$aic)
+			weighted_matrices <- lapply(1:nrow(grouping_table), function(i) {
+				return(private$get_coclassification_matrix(grouping_table, i) * weights[i])
+			})
+			return(Reduce("+", weighted_matrices))
 		}
 	),
 	
@@ -78,6 +96,13 @@ BruteData <- R6::R6Class("BruteData",
 		fully_separated_statistics = function() {
 			grouping <- 1:self$num_species
 			return(private$get_statistics_row(grouping, grouping))
+		},
+		
+		weighted_row_coclassification_matrix = function() {
+			return(private$get_weighted_coclassification_matrix(self$row_groupings))
+		},
+		weighted_col_coclassification_matrix = function() {
+			return(private$get_weighted_coclassification_matrix(self$col_groupings))
 		}
 	)
 )

### 2021-10-05 r/brute-post-process.R
Annotate weighted coclassification matrices with species names in post processing.

@@ -69,6 +69,13 @@ BruteData <- R6::R6Class("BruteData",
 			return(self$statistics[intersect(row_matches, col_matches),])
 		},
 		
+		annotate_matrix = function(mat) {
+			#Annotates a num_species by num_species matrix with the species names.
+			rownames(mat) <- self$species_names
+			colnames(mat) <- self$species_names
+			return(mat)
+		},
+		
 		get_coclassification_matrix = function(grouping_table, index) {
 			#Returns a binary matrix of whether two species are grouped together in a given row a grouping table.
 			grouping <- as.vector(as.matrix(grouping_table[index,]))
@@ -99,10 +106,10 @@ BruteData <- R6::R6Class("BruteData",
 		},
 		
 		weighted_row_coclassification_matrix = function() {
-			return(private$get_weighted_coclassification_matrix(self$row_groupings))
+			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$row_groupings)))
 		},
 		weighted_col_coclassification_matrix = function() {
-			return(private$get_weighted_coclassification_matrix(self$col_groupings))
+			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$col_groupings)))
 		}
 	)
 )

### 2021-10-06 r/brute-post-process.R
Make the post-processing code perform Shapiro-Wilk tests upon the residuals.

@@ -53,6 +53,7 @@ BruteData <- R6::R6Class("BruteData",
 			
 			#Add additional columns of statistics.
 			if(!is.null(self$statistics$aic)) private$add_aic_weights()
+			if(ncol(self$residuals) > 0) private$add_shapiro_p()
 		}
 	),
 	
@@ -69,6 +70,12 @@ BruteData <- R6::R6Class("BruteData",
 		
 		add_aic_weights = function() {
 			self$statistics$aic_weight <- information_criterion_weights(self$statistics$aic)
+		},
+		
+		add_shapiro_p = function() {
+			self$statistics$shapiro_p <- sapply(1:nrow(self$residuals), function(i) {
+				return(shapiro.test(as.vector(as.matrix(self$residuals[i,])))$p.value)
+			})
 		},
 		
 		match_grouping = function(desired_grouping, grouping_table) {

### 2021-10-06 r/brute-post-process.R
Revert the commits including residuals in the output and post-processing.
This reverts commits b2df57e961363901a90197c9a0be11d3f2d0b616, 0275a16b37c36743b2a20af8489aa8443257a031, and 0771b38665b17777dde746426daef5445270d4d6.
Most sets of residuals are not normal, per these Shapiro-Wilk tests.
As such, we need to do something better.
Or find some other way to justify what we have done.
The code slows down post-processing too much to be left in.

@@ -31,8 +31,7 @@ BruteData <- R6::R6Class("BruteData",
 		species_names = NULL,
 		row_groupings = NULL, #A data frame of row groupings, named by the species names.
 		col_groupings = NULL, #As above, for col groupings.
-		residuals = NULL, #A data frame of residuals.
-		statistics = NULL, #A data frame of all output values besides the above.
+		statistics = NULL, #A data frame of all output values besides groupings.
 		
 		initialize = function(data_file_name, species_names) {
 			data_table <- read.table(data_file_name, header=TRUE)
@@ -48,12 +47,10 @@ BruteData <- R6::R6Class("BruteData",
 			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
 			names(self$row_groupings) <- species_names
 			names(self$col_groupings) <- species_names
-			self$residuals <- data_table[,grep("residual", names(data_table))]
-			self$statistics <- data_table[,grep("row_group|col_group|residual", names(data_table), invert=TRUE)]
+			self$statistics <- data_table[,grep("row_group|col_group", names(data_table), invert=TRUE)]
 			
 			#Add additional columns of statistics.
 			if(!is.null(self$statistics$aic)) private$add_aic_weights()
-			if(ncol(self$residuals) > 0) private$add_shapiro_p()
 		}
 	),
 	
@@ -70,12 +67,6 @@ BruteData <- R6::R6Class("BruteData",
 		
 		add_aic_weights = function() {
 			self$statistics$aic_weight <- information_criterion_weights(self$statistics$aic)
-		},
-		
-		add_shapiro_p = function() {
-			self$statistics$shapiro_p <- sapply(1:nrow(self$residuals), function(i) {
-				return(shapiro.test(as.vector(as.matrix(self$residuals[i,])))$p.value)
-			})
 		},
 		
 		match_grouping = function(desired_grouping, grouping_table) {

### 2021-10-06 src/brute.cpp

@@ -63,7 +63,6 @@ int main(int argc, char **argv) {
 	OutputColumn<Grouping> outputColGroupings("col_group");
 	OutputColumn<double> outputAICs("aic");
 	OutputColumn<double> outputR2s("R2");
-	OutputColumn<Eigen::VectorXd> outputResiduals("residual");
 	
 	do {
 		do {
@@ -71,11 +70,10 @@ int main(int argc, char **argv) {
 			outputColGroupings.insert(solver.getColGrouping());
 			outputAICs.insert(solver.getAIC());
 			outputR2s.insert(solver.getR2());
-			outputResiduals.insert(solver.getSolutionResiduals());
 		} while(solver.updateRowGrouping(&Grouping::advance));
 	} while(solver.updateColGrouping(&Grouping::advance));
 	
-	outputTable(outputFile, outputRowGroupings, outputColGroupings, outputAICs, outputR2s, outputResiduals);
+	outputTable(outputFile, outputRowGroupings, outputColGroupings, outputAICs, outputR2s);
 	
 	return 0;
 }

### 2021-10-06 article.rnw
Read the brute force output into the article's R code.
Add the species names to the article's R code.
Add a helper script for post-processing the brute force data.
Add a post processing function to validate the data.
Rewrite the brute force post processing code using R6.
Add a note to methods, justifying the use of normal likelihood.

@@
 
+<<include=FALSE>>=
+	source("r/brute-post-process.R")
+	brute_data <- BruteData$new(
+		"output/brute.data",
+		c(
+			"D. birchii",
+			"D. pallidifrons",
+			"D. pandora",
+			"D. pseudoananassae",
+			"D. simulans",
+			"D. sulfurigaster"
+		)
+	)
+@
+
 \begin{document}
 \maketitle
+
+\section{Methods}
+
+\subsection{Model fitting}
+
+The model was fitted by least squares regression, with a normal likelihood.\footnote{
+	I recognise that this is erroneous, and a likelihood directly suited to count data would be more appropriate.
+	The choice to fit the Lotka--Volterra model specifically, rather than a generic regression model, prohibited the use of a link function.
+	This prevented me from using the typical methods of generalised nonlinear regression, and I have not yet managed to develop the methods necessary to fit the model using a Poisson or negative binomial likelihood.
+}
 

### 2021-10-06 src/data.hpp
Add another use of a const reference to the code for speed's sake.

@@ -19,7 +19,7 @@ class Data {
 		//The design density matrix, with numSpecies columns and numObservations rows.
 		Eigen::MatrixXd design;
 	public:
-		Data(std::vector<size_t> focal, const Eigen::VectorXd &response, const Eigen::MatrixXd &design):
+		Data(const std::vector<size_t> &focal, const Eigen::VectorXd &response, const Eigen::MatrixXd &design):
 			numSpecies(design.cols()), numObservations(design.rows()), focal(focal), response(response), design(design)
 		{
 			assert(focal.size() == numObservations);

### 2021-10-06 src/solver.cpp
Fix a bug in getting the parameter tolerances in the C++ code.

@@ -73,7 +73,7 @@ Solver::ParameterVector Solver::getParameterTolerances() const {
 	double growthRateTolerance = data.getResponse().mean() / data.getDesign().mean() * RELATIVE_TOLERANCE;
 	//For the competition coefficients, we will assume that with all species present at average density, growth halts.
 	//This gives us 1, divided by the square of average density, divided by the number of species.
-	double competitionCoefficientTolerance = 1.0 / pow(data.getResponse().mean(), 2.0) / data.numSpecies * RELATIVE_TOLERANCE;
+	double competitionCoefficientTolerance = 1.0 / pow(data.getDesign().mean(), 2.0) / data.numSpecies * RELATIVE_TOLERANCE;
 	
 	size_t numGrowthRates = growthGrouping.getNumGroups();
 	size_t numCompetitionCoefficients = rowGrouping.getNumGroups() * colGrouping.getNumGroups();

### 2021-10-06 src/brute.cpp
Add an option to the Data class, and thereby to the Solver class, to specify whether the response variable is per capita.

@@ -53,7 +53,8 @@ int main(int argc, char **argv) {
 	Data data = Data(
 		focal,
 		response,
-		design
+		design,
+		false
 	);
 	
 	Solver solver = Solver(data);

### 2021-10-06 src/data.hpp

@@ -9,6 +9,7 @@ class Data {
 	public:
 		const size_t numSpecies;
 		const size_t numObservations;
+		const bool isPerCapita; //Is the response variable total, or per capita?
 	protected:
 		//The index of the species used as the focal in each observation.
 		std::vector<size_t> focal;
@@ -19,8 +20,8 @@ class Data {
 		//The design density matrix, with numSpecies columns and numObservations rows.
 		Eigen::MatrixXd design;
 	public:
-		Data(const std::vector<size_t> &focal, const Eigen::VectorXd &response, const Eigen::MatrixXd &design):
-			numSpecies(design.cols()), numObservations(design.rows()), focal(focal), response(response), design(design)
+		Data(const std::vector<size_t> &focal, const Eigen::VectorXd &response, const Eigen::MatrixXd &design, bool isPerCapita):
+			numSpecies(design.cols()), numObservations(design.rows()), isPerCapita(isPerCapita), focal(focal), response(response), design(design)
 		{
 			assert(focal.size() == numObservations);
 			assert((size_t)response.size() == numObservations);

### 2021-10-06 src/solver.cpp

@@ -49,8 +49,10 @@ Solver::ParameterVector Solver::getInitialParameterValues() const {
 	//It is reasonable to guess that all the competition coefficients are zero.
 	double competitionCoefficient = 0.0;
 	//As for the growth rates, we might assume that all the species are in one group, and that all competition coefficients are zero.
-	//This gives us, approximately, the average observed response divided by the average species density in the design.
-	double growthRate = data.getResponse().mean() / data.getDesign().mean();
+	//This gives us the average observed response.
+	//If this is total, rather than per capita, we must divide by the average species density in the design.
+	double growthRate = data.getResponse().mean();
+	if(!data.isPerCapita) growthRate /= data.getDesign().mean();
 	
 	size_t numGrowthRates = growthGrouping.getNumGroups();
 	size_t numCompetitionCoefficients = rowGrouping.getNumGroups() * colGrouping.getNumGroups();
@@ -70,7 +72,8 @@ Solver::ParameterVector Solver::getParameterTolerances() const {
 	//We need somewhat reasonable guesses for the magnitudes of the growth rates and the competition coefficients.
 	//We will then multiply these by the RELATIVE_TOLERANCE.
 	//For the growth rates, we will use the same guess as for the initial values.
-	double growthRateTolerance = data.getResponse().mean() / data.getDesign().mean() * RELATIVE_TOLERANCE;
+	double growthRateTolerance = data.getResponse().mean() * RELATIVE_TOLERANCE;
+	if(!data.isPerCapita) growthRateTolerance /= data.getDesign().mean();
 	//For the competition coefficients, we will assume that with all species present at average density, growth halts.
 	//This gives us 1, divided by the square of average density, divided by the number of species.
 	double competitionCoefficientTolerance = 1.0 / pow(data.getDesign().mean(), 2.0) / data.numSpecies * RELATIVE_TOLERANCE;
@@ -102,7 +105,8 @@ Eigen::VectorXd Solver::getPredictions(const ParameterVector &parameters) {
 		double focalGrowthRate = getGrowthRate(parameters, focalGrowthGroup);
 		double focalDensity = data.getDesign()(obs, focal);
 		
-		double intrinsicGrowth = focalGrowthRate * focalDensity;
+		double intrinsicGrowth = focalGrowthRate;
+		if(!data.isPerCapita) intrinsicGrowth *= focalDensity;
[…]

### 2021-10-06 src/brute.cpp
Allow the brute force program to accomodate per capita data with a flag.

@@ -19,16 +19,25 @@ static void printUsage(int argc, const char **argv) {
 		
 		"\t-?\n"
 		"\t\tShow this help message and exit.\n"
+		
+		"\t-p\n"
+		"\t\tResponse variables are per capita growth/fecundity.\n"
+		"\t\tOtherwise, the response is assumed to be a measure of the total size of the next generation.\n"
 		,
 		argv[0]
 	);
 }
 
 int main(int argc, char **argv) {
+	bool isPerCapita = false;
+	
 	//Parse the options. getopt should shuffle all the mandatory arguments to the end by itself.
 	int opt;
-	while((opt = getopt(argc, argv, "")) != -1) { //No initial colon means leaving on automatic error reporting.
+	while((opt = getopt(argc, argv, "p")) != -1) { //No initial colon means leaving on automatic error reporting.
 		switch(opt) {
+			case 'p':
+				isPerCapita = true;
+				break;
 			case '?': //This covers an explicit ? as well as other errors.
 				//TODO: Some additional error parsing. Perhaps see https://stackoverflow.com/a/44371579
 				printUsage(argc, (const char**)argv);
@@ -54,7 +63,7 @@ int main(int argc, char **argv) {
 		focal,
 		response,
 		design,
-		false
+		isPerCapita
 	);
 	
 	Solver solver = Solver(data);

### 2021-10-06 src/solver.cpp
Add Solver::getSolutionPredictions().

@@ -169,6 +169,11 @@ Solver::ParameterVector Solver::getSolution() {
 	return solution;
 }
 
+Eigen::VectorXd Solver::getSolutionPredictions() {
+	//TODO: Memoise.
+	return getPredictions(getSolution());
+}
+
 Eigen::VectorXd Solver::getSolutionResiduals() {
 	//TODO: Memoise.
 	return getResiduals(getSolution());

### 2021-10-06 src/solver.hpp

@@ -101,6 +101,7 @@ class Solver {
 		void calculateSolution();
 	public:
 		ParameterVector getSolution();
+		Eigen::VectorXd getSolutionPredictions();
 		Eigen::VectorXd getSolutionResiduals();
 		double getDeviance();
 		double getAIC();

### 2021-10-06 r/brute-post-process.R
Refactor the post processing code for extensibility.
The statistics table now just includes any column that isn't a multi-column.

@@ -31,7 +31,7 @@ BruteData <- R6::R6Class("BruteData",
 		species_names = NULL,
 		row_groupings = NULL, #A data frame of row groupings, named by the species names.
 		col_groupings = NULL, #As above, for col groupings.
-		statistics = NULL, #A data frame of all output values besides groupings.
+		statistics = NULL, #A data frame of all output values besides the above.
 		
 		initialize = function(data_file_name, species_names) {
 			data_table <- read.table(data_file_name, header=TRUE)
@@ -47,7 +47,7 @@ BruteData <- R6::R6Class("BruteData",
 			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
 			names(self$row_groupings) <- species_names
 			names(self$col_groupings) <- species_names
-			self$statistics <- data_table[,grep("row_group|col_group", names(data_table), invert=TRUE)]
+			self$statistics <- data_table[,grep("_[0-9]*$", names(data_table), invert=TRUE)]
 			
 			#Add additional columns of statistics.
 			if(!is.null(self$statistics$aic)) private$add_aic_weights()

### 2021-10-07 article.rnw
Add a section on how the data was gathered.

@@
 
+\subsection{Data}
+
+The data I used in this study were drawn from the work of \textcite{terry2021natural}.
+The data consist of fecundity measurements for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
+In this, they form essentially the standard experimental design for parameterising a Lotka--Volterra model, as described by \textcite{hart2018quantify}.
+
+I shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
+
+\subsubsection{Summary of the experimental methodology}
+
+The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D.
+birchii}, \emph{D.
+pallidifrons}, \emph{D.
+pandora}, \emph{D.
+pseudoananassae}, \emph{D.
+simulans}, and \emph{D.
+sulfurigaster}.
+The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
+A number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
+The number of adult pairs of each species emerging from these eggs---i.e.\ the size of the next generation---was the response variable.
+
+Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
+The single-species densities were 3, 9, or 12 pairs per vial, each replicated six times per species.
+The two-species densities were, giving the densities of each of the two species, (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial, each replicated three times per pair of species.
+
+The experiment also included a number of other vials that were excluded for various reasons.
+The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
+That is irrelevant to this study, so was excluded.
+Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accomodate.
+Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.
+
 \subsection{Model fitting}

### 2021-10-07 article.rnw
Add a local bibliography file.
Add the forest package, and define a style for phylogenetic trees.
Add the phylogeny of the study species to the methods.

@@
 
+%Images
+\usepackage{tikz}
+\usepackage[edges]{forest}
+
 %Referencing
@@
 \addbibresource{bibliography/references.bib}
+\addbibresource{references.bib}
 \usepackage{placeins} %Provides \FloatBarrier
@@
 \usepackage{hyperref}
+\usepackage{cleveref}
+
+\forestset{
+	phylogeny/.style={
+		forked edges,
+		delay={where content={}{shape=coordinate}{}}, %Make empty nodes leave no gaps.
+		before typesetting nodes={
+			where n children=0{tier=terminus}{},
+		},
+		for tree={
+			grow=east,
+			align=left,
+			anchor=west,
+			s sep=0, %Reduce the separation between the leaf nodes.
+		}
+	}
+}
 
@@
 
+\subsubsection{Phylogeny}
+
+I determined the phylogenic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
+No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
+Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.
+
+\Textcite{terry2021natural} give the subgroups of the genus to which each study species belongs.
+\Textcite{lewis2005phylogeny} gives the relationship between three of these subgroups (melanogaster, ananassae, and montium), all of the subgenus Sophophora, while \textcite{izumitani2016phylogeography} describe the fourth subgroup (nasuta) as belonging to the distinct Drosophila subgenus.
+From this can be constructed the necessary relationships, which are depicted in \cref{fig:phylogeny}.
+
+\begin{figure}
+	\centering
+	\begin{forest} phylogeny
+		[
+			[
+				[
+					[\emph{D. melanogaster}]
+					[\emph{D. birchii}]
+				]
+				[
+					[\emph{D. pandora}]
+					[\emph{D. pseudoananassae}]
+				]
+			]
+			[
+				[
+					[\emph{D. pallidifrons}]
+					[\emph{D. sulfurigaster}]
+				]
+			]
+		]
+	\end{forest}
+
+	\caption{%
+		The phylogenetic relationships between the six \emph{Drosophila} species in the study.
+		The relationships depicted are purely qualitative; no implication of phylogenetic distance is made.
+	}
+	\label{fig:phylogeny}
+\end{figure}
+
 \subsection{Model fitting}

### 2021-10-07 article.rnw
Extract the definition of the phylogeny forest style to its own document.
Add a pgfplotstable style for heatmaps.
Make knitr output as-is in the article document.

@@
 \usepackage{import}
-
-%Images
-\usepackage{tikz}
-\usepackage[edges]{forest}
 
@@
 
-\forestset{
-	phylogeny/.style={
-		forked edges,
-		delay={where content={}{shape=coordinate}{}}, %Make empty nodes leave no gaps.
-		before typesetting nodes={
-			where n children=0{tier=terminus}{},
-		},
-		for tree={
-			grow=east,
-			align=left,
-			anchor=west,
-			s sep=0, %Reduce the separation between the leaf nodes.
-		}
-	}
-}
+\import{latex/}{forest-phylogeny}
+\import{latex/}{pgfplotstable-color-cells}
 
@@
 \date{}
+
+<<include=FALSE>>=
+	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
+@
 

### 2021-10-07 r/brute-post-process.R
Add a post processing function for printing coclassification matrices as heat maps.

@@ -4,6 +4,8 @@
 #Additionally, it requires a vector of species names.
 #These must be provided in the order that the C++ program indexed the species.
 
+library(magrittr)
+
 information_criterion_weights <- function(information_criterion) {
 	#Calculates Akaike weights from AIC values (or Schwarz weights from BIC values, etc.).
 	information_criterion <- information_criterion - min(information_criterion)
@@ -156,3 +158,70 @@ BruteData <- R6::R6Class("BruteData",
 		}
 	)
 )
+
+strip_booktabs_rules <- function(tab) {
+	#Strips out all the rules and such added by booktabs.
+	#This produces a table without rules.
+	#This actually removes dependency on booktabs.
+	#But it's easier to remove booktab's rules than *all* the standard rules.
+	tab %>%
+		sub("\\\\toprule", "", .) %>%
+		sub("\\\\midrule", "", .) %>%
+		sub("\\\\addlinespace", "", .) %>%
+		sub("\\\\bottomrule", "", .)
+}
+
+weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
+	#colourmap is the name of a pgfplots colourmap.
+	
+	format_num <- function(num) {
+		sprintf(paste0("%.",digits,"f"), num) %>%
+			sub("0.", ".", .) #Strip the leading 0.
+	}
+	
+	#LaTeX doesn't like us using \pgfplotscolormapaccess mid-table.
+	#So we will use it beforehand, define colours, then acces them.
+	#This requires us to generate a unique colour name for each cell.
+	#We will make it verbose to reduce the risk of a clash.
+	get_colour_name <- function(row, col) {
+		paste("weighted coclassification table colour", row, col)
+	}
+	
+	#Now, the colour definitions.
+	colour_definitions <- sapply(1:ncol(mat), function(col) {
+		sapply(1:nrow(mat), function(row) {
+			paste0(
+				"\\pgfplotscolormapaccess[0:1]{",mat[row,col],"}{",colourmap,"}\n",
+				"\\definecolor{",get_colour_name(row,col),"}{rgb}{\\pgfmathresult}"
+			)
+		})
+	})
+	colour_definitions <- paste(as.vector(colour_definitions), collapse="\n")
+	
+	#To include the \cellcolor commands, the entries of the table must be strings.
[…]

### 2021-10-08 r/brute-post-process.R
Increase vertical cell size in coclassification heat maps.

@@ -174,6 +174,12 @@ strip_booktabs_rules <- function(tab) {
 weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	#colourmap is the name of a pgfplots colourmap.
 	
+	array_stretch <- 1.5
+	
+	#Need \bgroup \egroup to contain the redefinition of \arraystretch.
+	begin_string <- paste0("\\bgroup\n\\renewcommand{\\arraystretch}{",array_stretch,"}")
+	end_string <- "\\egroup"
+	
 	format_num <- function(num) {
 		sprintf(paste0("%.",digits,"f"), num) %>%
 			sub("0.", ".", .) #Strip the leading 0.
@@ -220,8 +226,8 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	) %>%
 		strip_booktabs_rules()
 	
-	#TODO: Increase cell height.
-	
+	cat(begin_string)
 	cat(colour_definitions)
 	cat(tab)
+	cat(end_string)
 }

### 2021-10-08 r/brute-post-process.R
Add a colourbar to the coclassification matrices.

@@ -175,10 +175,23 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	#colourmap is the name of a pgfplots colourmap.
 	
 	array_stretch <- 1.5
+	colour_bar_height <- "6cm"
 	
-	#Need \bgroup \egroup to contain the redefinition of \arraystretch.
-	begin_string <- paste0("\\bgroup\n\\renewcommand{\\arraystretch}{",array_stretch,"}")
-	end_string <- "\\egroup"
+	colourbar_code <- paste(
+		"\\begin{tikzpicture}[baseline=(current bounding box.south)]",
+			"\\begin{axis}[",
+				paste0("colormap name=",colourmap,","),
+				"colorbar left,",
+				"point meta min=0,",
+				"point meta max=1,",
+				"colorbar style={",
+					paste0("height=",colour_bar_height,","),
+				"},",
+				"%Disable the axes themselves; we only want the colourbar.",
+				"hide axis, scale only axis, width=0pt, height=0pt,",
+			"]\\end{axis}",
+		"\\end{tikzpicture}",
+	sep="\n")
 	
 	format_num <- function(num) {
 		sprintf(paste0("%.",digits,"f"), num) %>%
@@ -221,13 +234,27 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 		paste0("\\emph{",rownames(mat),"}"),
 	ncol=1))
 	
-	tab <- knitr::kable(string_mat, escape=FALSE, booktabs=TRUE,
+	matrix_tab <- knitr::kable(string_mat, escape=FALSE, booktabs=TRUE,
 		align=c(rep("c",ncol(mat)),"l")
 	) %>%
-		strip_booktabs_rules()
+		strip_booktabs_rules() %>%
+		sub("\\begin{tabular}", "\\begin{tabular}[b]", ., fixed=TRUE) #Baseline at the bottom, for colourbar alignment.
 	
-	cat(begin_string)
+	#Need \bgroup \egroup to contain the redefinition of \arraystretch.
+	matrix_tab <- paste(
+		paste0("\\bgroup\n\\renewcommand{\\arraystretch}{",array_stretch,"}"),
+		matrix_tab,
+		"\\egroup",
+	sep="\n")
+	
+	outer_tab <- paste(
+		"\\begin{tabular}{rl}",
+		colourbar_code,
+		"&",
[…]

### 2021-10-08 r/brute-post-process.R
Shift the colourbars down and towards the coclassification matrices.

@@ -178,7 +178,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	colour_bar_height <- "6cm"
 	
 	colourbar_code <- paste(
-		"\\begin{tikzpicture}[baseline=(current bounding box.south)]",
+		"\\begin{tikzpicture}[baseline]",
 			"\\begin{axis}[",
 				paste0("colormap name=",colourmap,","),
 				"colorbar left,",
@@ -186,6 +186,8 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 				"point meta max=1,",
 				"colorbar style={",
 					paste0("height=",colour_bar_height,","),
+					"at={(parent axis.south east)},",
+					"anchor=south west,",
 				"},",
 				"%Disable the axes themselves; we only want the colourbar.",
 				"hide axis, scale only axis, width=0pt, height=0pt,",

### 2021-10-08 r/brute-post-process.R
Make colourbar heights automatically determined by table sizes.

@@ -175,7 +175,22 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	#colourmap is the name of a pgfplots colourmap.
 	
 	array_stretch <- 1.5
-	colour_bar_height <- "6cm"
+	
+	#\dimexpr can't work with floating point multipliers, so we need rationals.
+	as_rational_string <- function(x) {
+		as.character(gmp::as.bigq(x))
+	}
+	
+	#\baselineskip seemingly doesn't work inside a tikzpicture, so we save it elsewhere.
+	length_definition <- paste(
+		"\\ifdefined\\coclassificationtextheight\\else\\newlength{\\coclassificationtextheight}\\fi",
+		"\\setlength{\\coclassificationtextheight}{\\baselineskip}",
+	sep="\n")
+	
+	#The height of the whole table.
+	table_height <- paste0("{\\dimexpr\\coclassificationtextheight * ",as_rational_string(array_stretch)," * ",nrow(mat),"}")
+	#The difference between the baseline of the bottom row and the bottom of the table.
+	baseline_drop <- paste0("{\\dimexpr -\\coclassificationtextheight * ",as_rational_string(array_stretch-1)," / 2}")
 	
 	colourbar_code <- paste(
 		"\\begin{tikzpicture}[baseline]",
@@ -185,9 +200,10 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 				"point meta min=0,",
 				"point meta max=1,",
 				"colorbar style={",
-					paste0("height=",colour_bar_height,","),
+					paste0("height=",table_height,","),
 					"at={(parent axis.south east)},",
 					"anchor=south west,",
+					paste0("yshift=",baseline_drop,","),
 				"},",
 				"%Disable the axes themselves; we only want the colourbar.",
 				"hide axis, scale only axis, width=0pt, height=0pt,",
@@ -257,6 +273,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 		"\\end{tabular}",
 	sep="\n")
 	
+	cat(length_definition)
 	cat(colour_definitions)
 	cat(outer_tab)
 }

### 2021-10-08 r/brute-post-process.R
Rotate the column headers of the coclassification matrices.

@@ -175,6 +175,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	#colourmap is the name of a pgfplots colourmap.
 	
 	array_stretch <- 1.5
+	header_angle <- 30
 	
 	#\dimexpr can't work with floating point multipliers, so we need rationals.
 	as_rational_string <- function(x) {
@@ -245,7 +246,8 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 		})
 	})
 	
-	colnames(string_mat) <- paste0("\\rotatebox{90}{\\emph{",colnames(mat),"}}")
+	#\rotatebox makes things wider, so we enclose in a fixed width \makebox.
+	colnames(string_mat) <- paste0("\\makebox[1em][l]{\\rotatebox{",header_angle,"}{\\emph{",colnames(mat),"}}}")
 	#We don't set row names for mat, because we want the species labels on the right instead of the left.
 	#We cbind instead.
 	string_mat <- cbind(string_mat, matrix(

### 2021-10-08 article.rnw
Add a post processing function for printing coclassification matrices as heat maps.
Remove pgfplotstable-color-cells.tex.
The R code renders it irrelevant.
Fix an incorrect species in the phylogenetic tree.
Add the coclassification matrices to the article.

@@
 \usepackage{import}
+
+\usepackage{subcaption}
+\usepackage{pgfplots}
+\usepackage{colortbl}
 
@@
 \import{latex/}{forest-phylogeny}
-\import{latex/}{pgfplotstable-color-cells}
 
@@
 				[
-					[\emph{D. melanogaster}]
+					[\emph{D. simulans}]
 					[\emph{D. birchii}]
@@
 
+\section{Results}
+
+\pgfplotsset{%
+	colormap={coclassification}{color=(white) color=(red)}
+}
+\begin{figure}
+	\centering
+	\begin{subfigure}{\textwidth}
+		<<echo=FALSE>>=
+			weighted_coclassification_kable(
+				brute_data$weighted_col_coclassification_matrix,
+				colourmap="coclassification"
+			)
+		@
+		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
+		\label{fig:coclassification-cols}
+	\end{subfigure}
+
+	\bigskip
+
+	\begin{subfigure}{\textwidth}
+		<<echo=FALSE>>=
+			weighted_coclassification_kable(
+				brute_data$weighted_row_coclassification_matrix,
+				colourmap="coclassification"
+			)
+		@
+		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
+		\label{fig:coclassification-rows}
+	\end{subfigure}
+
+	\caption{%
+		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
+		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
+		\Cref{fig:coclassification-cols} represents the grouping of species' competetive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
+	}
+	\label{fig:coclassification}
+\end{figure}
+
 \FloatBarrier

### 2021-10-08 article.rnw
Correct spelling.

@@
 That is irrelevant to this study, so was excluded.
-Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accomodate.
+Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accommodate.
 Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.
@@
 
-I determined the phylogenic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
+I determined the phylogenetic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
 No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
@@
 		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
-		\Cref{fig:coclassification-cols} represents the grouping of species' competetive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
+		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
 	}

### 2021-10-08 r/brute-post-process.R
Add an option for colouring the diagonal cells to the coclassification matrix function.

@@ -171,7 +171,7 @@ strip_booktabs_rules <- function(tab) {
 		sub("\\\\bottomrule", "", .)
 }
 
-weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
+weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray", digits=3) {
 	#colourmap is the name of a pgfplots colourmap.
 	
 	array_stretch <- 1.5
@@ -240,7 +240,9 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", digits=3) {
 	#So we convert to a string matrix, inserting cell colourings.
 	string_mat <- sapply(1:ncol(mat), function(col) {
 		sapply(1:nrow(mat), function(row) {
-			if(row == col) return("") #We want to leave the diagonals blank.
+			if(row == col) { #No numbers on the diagonals.
+				return(paste0("\\cellcolor{",diagonal_colour,"}"))
+			}
 			value <- format_num(mat[row,col])
 			paste0("\\cellcolor{",get_colour_name(row,col),"}",value)
 		})

### 2021-10-08 article.rnw
Set the diagonal colour for the coclassification matrices.

@@
 }
+\colorlet{coclassification diagonal}{black!20}
 \begin{figure}
@@
 				brute_data$weighted_col_coclassification_matrix,
-				colourmap="coclassification"
+				colourmap="coclassification", diagonal_colour="coclassification diagonal"
 			)
@@
 				brute_data$weighted_row_coclassification_matrix,
-				colourmap="coclassification"
+				colourmap="coclassification", diagonal_colour="coclassification diagonal"
 			)

### 2021-10-09 article.rnw
Replace the excuse in the model fitting methods with a better explanation, based on using per capita fecundity.

@@
 
-The model was fitted by least squares regression, with a normal likelihood.\footnote{
-	I recognise that this is erroneous, and a likelihood directly suited to count data would be more appropriate.
-	The choice to fit the Lotka--Volterra model specifically, rather than a generic regression model, prohibited the use of a link function.
-	This prevented me from using the typical methods of generalised nonlinear regression, and I have not yet managed to develop the methods necessary to fit the model using a Poisson or negative binomial likelihood.
-}
+The models were fitted to the data using regression techniques.
+Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
+As such, I assumed a normal error distribution, and fitted a least squares regression.
+To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
+\[
+	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_j \alpha_{ij}\right)
+.\]
 

### 2021-10-09 article.rnw
Explain the use of non-linear least squares in the methods.

@@
 
+The Lotka--Volterra model is not linear in the parameters.
+With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
+With the rows grouped, however, this becomes impossible, for each species sill has its own growth rate.
+As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
+
 \section{Results}

### 2021-10-20 r/brute-post-process.R
Split the code for the coclassification LaTeX table into its own file.

@@ -158,126 +158,3 @@ BruteData <- R6::R6Class("BruteData",
 		}
 	)
 )
-
-strip_booktabs_rules <- function(tab) {
-	#Strips out all the rules and such added by booktabs.
-	#This produces a table without rules.
-	#This actually removes dependency on booktabs.
-	#But it's easier to remove booktab's rules than *all* the standard rules.
-	tab %>%
-		sub("\\\\toprule", "", .) %>%
-		sub("\\\\midrule", "", .) %>%
-		sub("\\\\addlinespace", "", .) %>%
-		sub("\\\\bottomrule", "", .)
-}
-
-weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray", digits=3) {
-	#colourmap is the name of a pgfplots colourmap.
-	
-	array_stretch <- 1.5
-	header_angle <- 30
-	
-	#\dimexpr can't work with floating point multipliers, so we need rationals.
-	as_rational_string <- function(x) {
-		as.character(gmp::as.bigq(x))
-	}
-	
-	#\baselineskip seemingly doesn't work inside a tikzpicture, so we save it elsewhere.
-	length_definition <- paste(
-		"\\ifdefined\\coclassificationtextheight\\else\\newlength{\\coclassificationtextheight}\\fi",
-		"\\setlength{\\coclassificationtextheight}{\\baselineskip}",
-	sep="\n")
-	
-	#The height of the whole table.
-	table_height <- paste0("{\\dimexpr\\coclassificationtextheight * ",as_rational_string(array_stretch)," * ",nrow(mat),"}")
-	#The difference between the baseline of the bottom row and the bottom of the table.
-	baseline_drop <- paste0("{\\dimexpr -\\coclassificationtextheight * ",as_rational_string(array_stretch-1)," / 2}")
-	
-	colourbar_code <- paste(
-		"\\begin{tikzpicture}[baseline]",
-			"\\begin{axis}[",
-				paste0("colormap name=",colourmap,","),
-				"colorbar left,",
-				"point meta min=0,",
-				"point meta max=1,",
-				"colorbar style={",
-					paste0("height=",table_height,","),
-					"at={(parent axis.south east)},",
-					"anchor=south west,",
-					paste0("yshift=",baseline_drop,","),
-				"},",
[…]

### 2021-10-20 r/coclassification-table.R

@@ -1,0 +1,128 @@
+#A function for printing a coclassification matrix as a coloured table using knitr.
+#Expects a coclassification matrix (with numeric entries in [0,1]), with row and column names.
+#Uses a pgfplots colour map and xcolor colour name for the diagonal.
+
+library(magrittr)
+
+strip_booktabs_rules <- function(tab) {
+	#Strips out all the rules and such added by booktabs.
+	#This produces a table without rules.
+	#This actually removes dependency on booktabs.
+	#But it's easier to remove booktab's rules than *all* the standard rules.
+	tab %>%
+		sub("\\\\toprule", "", .) %>%
+		sub("\\\\midrule", "", .) %>%
+		sub("\\\\addlinespace", "", .) %>%
+		sub("\\\\bottomrule", "", .)
+}
+
+weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray", digits=3) {
+	#colourmap is the name of a pgfplots colourmap.
+	
+	array_stretch <- 1.5
+	header_angle <- 30
+	
+	#\dimexpr can't work with floating point multipliers, so we need rationals.
+	as_rational_string <- function(x) {
+		as.character(gmp::as.bigq(x))
+	}
+	
+	#\baselineskip seemingly doesn't work inside a tikzpicture, so we save it elsewhere.
+	length_definition <- paste(
+		"\\ifdefined\\coclassificationtextheight\\else\\newlength{\\coclassificationtextheight}\\fi",
+		"\\setlength{\\coclassificationtextheight}{\\baselineskip}",
+	sep="\n")
+	
+	#The height of the whole table.
+	table_height <- paste0("{\\dimexpr\\coclassificationtextheight * ",as_rational_string(array_stretch)," * ",nrow(mat),"}")
+	#The difference between the baseline of the bottom row and the bottom of the table.
+	baseline_drop <- paste0("{\\dimexpr -\\coclassificationtextheight * ",as_rational_string(array_stretch-1)," / 2}")
+	
+	colourbar_code <- paste(
+		"\\begin{tikzpicture}[baseline]",
+			"\\begin{axis}[",
+				paste0("colormap name=",colourmap,","),
+				"colorbar left,",
+				"point meta min=0,",
+				"point meta max=1,",
+				"colorbar style={",
[…]

### 2021-10-21 src/parameters.cpp
Add a numSpecies member to the Parameters class.

@@ -28,7 +28,9 @@ size_t Parameters::getNumParameters() const {
 	return growthRates.size() + competitionCoefficients.size();
 }
 
-Parameters::Parameters(Data data, GroupingSet groupings) {
+Parameters::Parameters(Data data, GroupingSet groupings):
+	numSpecies(groupings[GROWTH].numSpecies)
+{
 	//This is the standard constructor.
 	//It will try to make somewhat reasonable initial guesses for all the parameter values.
 	double growthRate = data.guessGrowthRate();
@@ -53,7 +55,9 @@ Eigen::VectorXd Parameters::getTolerances(Data data, GroupingSet groupings) {
 	).finished();
 }
 
-Parameters::Parameters(Eigen::VectorXd parameters, GroupingSet groupings) {
+Parameters::Parameters(Eigen::VectorXd parameters, GroupingSet groupings):
+	numSpecies(groupings[GROWTH].numSpecies)
+{
 	size_t numGrowthRates = groupings[GROWTH].getNumGroups();
 	size_t numRowGroups = groupings[ROW].getNumGroups();
 	size_t numColGroups = groupings[COL].getNumGroups();

### 2021-10-21 src/parameters.hpp

@@ -15,6 +15,7 @@ typedef std::function<double(double)> RandomVariableDensityFunc;
 
 class Parameters {
 	protected:
+		size_t numSpecies = 0;
 		//The grouping sizes will be implicitly stored in the sizes of the growth rates vector and competition coefficients matrix.
 		//The matrix will be stored in row-major order.
 		Eigen::VectorXd growthRates;

### 2021-10-21 src/io.cpp
Correct spelling.

@@ -93,7 +93,7 @@ static void printMultiHeader(std::ostream &stream, const std::string name, size_
 }
 
 //When using printMultiHeader, we will need to assume every entry in the column has the same length.
-//The calling function checks that there is at least one entry in the column, sow e can just grab the first.
+//The calling function checks that there is at least one entry in the column, so we can just grab the first.
 
 template<> void OutputColumn<Grouping>::printHeader(std::ostream &stream) const {
 	size_t numSpecies = column[0].numSpecies;

### 2021-10-21 src/parameters.cpp
Add Parameters::getNumSpecies().

@@ -2,6 +2,10 @@
 
 #define RELATIVE_TOLERANCE 1e-6
 
+double Parameters::getNumSpecies() const {
+	return numSpecies;
+}
+
 double Parameters::getGrowthRate(size_t index) const {
 	return growthRates[index];
 }

### 2021-10-21 src/parameters.hpp

@@ -21,6 +21,7 @@ class Parameters {
 		Eigen::VectorXd growthRates;
 		Eigen::Matrix<double, Eigen::Dynamic, Eigen::Dynamic, Eigen::RowMajor> competitionCoefficients;
 	public:
+		double getNumSpecies() const;
 		double getGrowthRate(size_t index) const;
 		const Eigen::VectorXd &getGrowthRates() const;
 		double getCompetitionCoefficient(size_t rowIndex, size_t colIndex) const;

### 2021-10-21 src/io.cpp
Add the ability to print Parameters class objects.

@@ -3,9 +3,13 @@
 #include <fstream>
 #include <iterator>
 #include "grouping.hpp"
+#include "parameters.hpp"
 #include "io.hpp"
 
 const char *OUTPUT_TABLE_SEPARATOR = "\t";
+const char *OUTPUT_GROWTH_RATE_STRING = "r";
+const char *OUTPUT_COMPETITION_COEFFICIENT_STRING = "alpha";
+const char *OUTPUT_NULL_VALUE_STRING = "NA";
 
 template<typename StreamT> static StreamT &openFile(const char *filename) {
 	StreamT &file = *(new StreamT);
@@ -105,6 +109,17 @@ template<> void OutputColumn<Eigen::VectorXd>::printHeader(std::ostream &stream)
 	printMultiHeader(stream, name, numCols);
 }
 
+template<> void OutputColumn<Parameters>::printHeader(std::ostream &stream) const {
+	size_t numSpecies = column[0].getNumSpecies();
+	printMultiHeader(stream, name + "_" + OUTPUT_GROWTH_RATE_STRING, numSpecies);
+	stream << OUTPUT_TABLE_SEPARATOR;
+	
+	for(size_t i = 0; i < numSpecies; i++) {
+		printMultiHeader(stream, name + "_" + OUTPUT_COMPETITION_COEFFICIENT_STRING + "_" + std::to_string(i), numSpecies);
+		if(i != numSpecies-1) stream << OUTPUT_TABLE_SEPARATOR;
+	}
+}
+
 template<typename T> void OutputColumn<T>::printElement(std::ostream &stream, size_t index) const {
 	stream << column[index];
 }
@@ -125,8 +140,35 @@ template<> void OutputColumn<Eigen::VectorXd>::printElement(std::ostream &stream
 	}
 }
 
+template<> void OutputColumn<Parameters>::printElement(std::ostream &stream, size_t index) const {
+	size_t numSpecies = column[index].getNumSpecies();
+	
+	Eigen::VectorXd growthRates = column[index].getGrowthRates();
+	for(size_t i = 0; i < numSpecies; i++) {
+		if(i < (size_t)growthRates.size()) {
+			stream << growthRates[i];
+		} else {
+			stream << OUTPUT_NULL_VALUE_STRING;
+		}
+		stream << OUTPUT_TABLE_SEPARATOR;
+	}
+	
+	Eigen::MatrixXd competitionCoefficients = column[index].getCompetitionCoefficients();
+	for(size_t i = 0; i < numSpecies; i++) {
[…]

### 2021-10-21 src/rjmcmc.cpp
Also print the parameters in the reversible jump output.

@@ -21,13 +21,15 @@ int main(int argc, char **argv) {
 	
 	OutputColumn<Grouping> outputRowGroupings("row_group");
 	OutputColumn<Grouping> outputColGroupings("col_group");
+	OutputColumn<Parameters> outputParameters("parameters");
 	for(size_t i = 0; i < NUM_STEPS; i++) {
 		solver.makeJump();
 		outputRowGroupings.insert(solver.getGrouping(ROW));
 		outputColGroupings.insert(solver.getGrouping(COL));
+		outputParameters.insert(solver.getParameters());
 	}
 	
-	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings);
+	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters);
 	
 	return 0;
 }

### 2021-10-21 src/parameters.hpp
Add a refactor to use AugmentedParameters::getAdditionalParameter().
The plural version already existed; this is the singular.

@@ -60,6 +60,10 @@ template<size_t nAug> class AugmentedParameters : public Parameters {
 		AugmentedParameters(Data data, GroupingSet groupings, std::array<double, nAug> additionalParameters):
 			Parameters(data, groupings), additionalParameters(additionalParameters) {};
 		
+		const double &getAdditionalParameter(size_t index) const {
+			return additionalParameters[index];
+		}
+		
 		const std::array<double, nAug> &getAdditionalParameters() const {
 			return additionalParameters;
 		}

### 2021-10-21 src/rjsolver.cpp

@@ -223,7 +223,7 @@ void ReversibleJumpSolver::rejectJump() {
 
 double ReversibleJumpSolver::getErrorVariance() const {
 	//This is the additional parameter, and is used in calculating the likelihood.
-	return getParameters().getAdditionalParameters()[0];
+	return getParameters().getAdditionalParameter(0);
 }
 
 Eigen::VectorXd ReversibleJumpSolver::getResiduals() {

### 2021-10-21 src/rjmcmc.cpp
Add the error variance to the output of the reversible jump program.

@@ -22,14 +22,16 @@ int main(int argc, char **argv) {
 	OutputColumn<Grouping> outputRowGroupings("row_group");
 	OutputColumn<Grouping> outputColGroupings("col_group");
 	OutputColumn<Parameters> outputParameters("parameters");
+	OutputColumn<double> outputErrorVariance("parameters_error_variance");
 	for(size_t i = 0; i < NUM_STEPS; i++) {
 		solver.makeJump();
 		outputRowGroupings.insert(solver.getGrouping(ROW));
 		outputColGroupings.insert(solver.getGrouping(COL));
 		outputParameters.insert(solver.getParameters());
+		outputErrorVariance.insert(solver.getParameters().getAdditionalParameter(0));
 	}
 	
-	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters);
+	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters, outputErrorVariance);
 	
 	return 0;
 }

### 2021-10-21 r/brute-post-process.R
Print the parameter values in the brute force output, and adjust the post processing code to account for this.

@@ -33,6 +33,7 @@ BruteData <- R6::R6Class("BruteData",
 		species_names = NULL,
 		row_groupings = NULL, #A data frame of row groupings, named by the species names.
 		col_groupings = NULL, #As above, for col groupings.
+		parameters = NULL, #A data frame of parameter values.
 		statistics = NULL, #A data frame of all output values besides the above.
 		
 		initialize = function(data_file_name, species_names) {
@@ -49,7 +50,8 @@ BruteData <- R6::R6Class("BruteData",
 			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
 			names(self$row_groupings) <- species_names
 			names(self$col_groupings) <- species_names
-			self$statistics <- data_table[,grep("_[0-9]*$", names(data_table), invert=TRUE)]
+			self$parameters <- data_table[,grep("parameters", names(data_table))] + 1
+			self$statistics <- data_table[,grep("_[0-9]*$|parameters", names(data_table), invert=TRUE)]
 			
 			#Add additional columns of statistics.
 			if(!is.null(self$statistics$aic)) private$add_aic_weights()

### 2021-10-21 src/brute.cpp

@@ -11,6 +11,7 @@ int main(int argc, char **argv) {
 	OutputColumn<Grouping> outputColGroupings("col_group");
 	OutputColumn<double> outputAICs("aic");
 	OutputColumn<double> outputR2s("R2");
+	OutputColumn<Parameters> outputParameters("parameters");
 	
 	do {
 		do {
@@ -18,10 +19,11 @@ int main(int argc, char **argv) {
 			outputColGroupings.insert(solver.getGrouping(COL));
 			outputAICs.insert(solver.getAIC());
 			outputR2s.insert(solver.getR2());
+			outputParameters.insert(solver.getSolution());
 		} while(solver.updateGrouping(ROW, &Grouping::advance));
 	} while(solver.updateGrouping(COL, &Grouping::advance));
 	
-	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputAICs, outputR2s);
+	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters, outputAICs, outputR2s);
 	
 	return 0;
 }

### 2021-10-21 r/brute-post-process.R
Correct grammar.

@@ -109,7 +109,7 @@ BruteData <- R6::R6Class("BruteData",
 		},
 		
 		get_coclassification_matrix = function(grouping_table, index) {
-			#Returns a binary matrix of whether two species are grouped together in a given row a grouping table.
+			#Returns a binary matrix of whether two species are grouped together in a given row of a grouping table.
 			grouping <- as.vector(as.matrix(grouping_table[index,]))
 			mat <- as.matrix(sapply(grouping, function(group) {
 				return(grouping == group)

### 2021-10-21 r/brute-post-process.R
Make the BruteData post-processing class a subclass of Data, and split them into two files.
This will make it easier to post-process other sorts of data with the same code.
In particular, the output of the reversible jump program.

@@ -1,18 +1,7 @@
 #A set of helper functions for post-processing the data from brute forcing.
-#Works in an object-oriented fashion.
-#Constructing the central object requires a data file produced by the C++ program, with column names preserved.
-#Additionally, it requires a vector of species names.
-#These must be provided in the order that the C++ program indexed the species.
+#Depends upon post-process.R
 
 library(magrittr)
-
-information_criterion_weights <- function(information_criterion) {
-	#Calculates Akaike weights from AIC values (or Schwarz weights from BIC values, etc.).
-	information_criterion <- information_criterion - min(information_criterion)
-	weights <- exp(-0.5 * information_criterion)
-	weights <- weights / sum(weights)
-	return(weights)
-}
 
 prob_perm_test <- function(selected_probs, all_probs, num_iter = 1000) {
 	#Tests whether the sum of selected_probs is less than the sum of a random sample of all_probs of the same length.
@@ -28,124 +17,14 @@ prob_perm_test <- function(selected_probs, all_probs, num_iter = 1000) {
 }
 
 BruteData <- R6::R6Class("BruteData",
-	public = list(
-		num_species = NULL,
-		species_names = NULL,
-		row_groupings = NULL, #A data frame of row groupings, named by the species names.
-		col_groupings = NULL, #As above, for col groupings.
-		parameters = NULL, #A data frame of parameter values.
-		statistics = NULL, #A data frame of all output values besides the above.
-		
-		initialize = function(data_file_name, species_names) {
-			data_table <- read.table(data_file_name, header=TRUE)
-			
-			self$num_species <- length(species_names)
-			self$species_names <- species_names
-			
-			private$validate_data(data_table, self$num_species)
-			
-			#Extract the groupings and other data.
-			#Add one to the groupings to make them 1-indexed, as R prefers.
-			self$row_groupings <- data_table[,grep("row_group", names(data_table))] + 1
-			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
-			names(self$row_groupings) <- species_names
-			names(self$col_groupings) <- species_names
-			self$parameters <- data_table[,grep("parameters", names(data_table))] + 1
-			self$statistics <- data_table[,grep("_[0-9]*$|parameters", names(data_table), invert=TRUE)]
-			
-			#Add additional columns of statistics.
-			if(!is.null(self$statistics$aic)) private$add_aic_weights()
-		}
-	),
[…]

### 2021-10-21 r/post-process.R

@@ -1,0 +1,136 @@
+#A set of helper functions for post-processing the data from the C++ programs.
+#Works in an object-oriented fashion.
+#Constructing the central object requires a data file produced by the C++ program, with column names preserved.
+#Additionally, it requires a vector of species names.
+#These must be provided in the order that the C++ program indexed the species.
+
+library(magrittr)
+
+information_criterion_weights <- function(information_criterion) {
+	#Calculates Akaike weights from AIC values (or Schwarz weights from BIC values, etc.).
+	information_criterion <- information_criterion - min(information_criterion)
+	weights <- exp(-0.5 * information_criterion)
+	weights <- weights / sum(weights)
+	return(weights)
+}
+
+Data <- R6::R6Class("Data",
+	public = list(
+		num_species = NULL,
+		species_names = NULL,
+		row_groupings = NULL, #A data frame of row groupings, named by the species names.
+		col_groupings = NULL, #As above, for col groupings.
+		parameters = NULL, #A data frame of parameter values.
+		statistics = NULL, #A data frame of all output values besides the above.
+		
+		initialize = function(data_file_name, species_names) {
+			data_table <- read.table(data_file_name, header=TRUE)
+			
+			self$num_species <- length(species_names)
+			self$species_names <- species_names
+			
+			private$validate_data(data_table, self$num_species)
+			
+			#Extract the groupings and other data.
+			#Add one to the groupings to make them 1-indexed, as R prefers.
+			self$row_groupings <- data_table[,grep("row_group", names(data_table))] + 1
+			self$col_groupings <- data_table[,grep("col_group", names(data_table))] + 1
+			names(self$row_groupings) <- species_names
+			names(self$col_groupings) <- species_names
+			self$parameters <- data_table[,grep("parameters", names(data_table))] + 1
+			self$statistics <- data_table[,grep("_[0-9]*$|parameters", names(data_table), invert=TRUE)]
+			
+			#Add additional columns of statistics.
+			if(!is.null(self$statistics$aic)) private$add_aic_weights()
+		}
+	),
+	
+	private = list(
+		validate_data = function(data_table, num_species) {
+			#Checks whether a data table is for the correct number of species.
+			if(
+				length(grep("row_group", names(data_table))) != num_species |
+				length(grep("col_group", names(data_table))) != num_species
+			) {
[…]

### 2021-10-23 article.rnw
Fix an inconsistency in the formulation of the Lotka-Volterra model written in the article.
N_i had time subscripts, but not N_j.
N_j now has a time subscript.
Split the code for the coclassification LaTeX table into its own file.
Make the BruteData post-processing class a subclass of Data, and split them into two files.
This will make it easier to post-process other sorts of data with the same code.
In particular, the output of the reversible jump program.
Add the beginning of the introduction, explaining the problem and its importance.

@@
 <<include=FALSE>>=
+	source("r/post-process.R")
 	source("r/brute-post-process.R")
@@
 	)
+
+	source("r/coclassification-table.R")
 @
@@
 \maketitle
+
+\section{Introduction}
+
+Models have long been used in ecology community \parencite{lotka1925elements}.
+They allow us to make predictions about things we cannot directly observe, be it the response of a community to a novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel community \parencite{maynard2020predicting}.
+The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.
+
+However, making any use of a model requires experimentally or observationally determining the values of each parameter in the model.
+This poses a problem for species interacton models, due to the sheer number of parameters that must be determined.
+Even the simplest models, with no environmental dependence, require one parameter for the interaction of each pair of species \parencite{novak2016characterizing}.
+Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for a community of just \num{10} species.
+Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
+This is expensive, and requires a lot of effort.
+As such, these models are typically restricted to a small number of focal species \parencite{ovaskainen2017species}.
+Real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
+We need a way to reduce the number of parameters the models require, to regularise them.
+
+%Several methods have been applied to regularise species interaction models, each with their own limitations.
+%For example, it is often assumed that most pairs of species don't interact, setting many of the parameters to zero \parencite{mutshinda2009drives,ovaskainen2017species}.
+%TODO: Find a citation for why this assumption doesn't hold.
+
+Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
+Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriate2004spatially,ovaskainen2017species,weiss2021disentangling}.
+The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
+However, tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
+On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
+While attempts have been made to define functional groups more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
+As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
+In all, we are left with the question of how best to group species in community models.
 
@@
 \[
-	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_j \alpha_{ij}\right)
+	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
 .\]

### 2021-10-23 article.rnw
Add a final pargraph of specific aims to the introduction.

@@
 In all, we are left with the question of how best to group species in community models.
+
+I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which gives the most parsimonius model.
+In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
+I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
+I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
+Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
 

### 2021-10-23 article.rnw
Swap some secions in the methods around.
The model is more important than the phylogeny, and should come first.
Remove an extraneous comma.

@@
 
-\subsubsection{Phylogeny}
+\subsection{Model fitting}
 
-I determined the phylogenetic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
+The models were fitted to the data using regression techniques.
+Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
+As such, I assumed a normal error distribution, and fitted a least squares regression.
+To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
+\[
+	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
+.\]
+
+The Lotka--Volterra model is not linear in the parameters.
+With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
+With the rows grouped, however, this becomes impossible, for each species sill has its own growth rate.
+As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
+
+\subsection{Phylogeny}
+
+I determined the phylogenetic relationships between the six study species by examination of the literature, in order to compare these to the groupings generated by the models.
 No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
@@
 \end{figure}
-
-\subsection{Model fitting}
-
-The models were fitted to the data using regression techniques.
-Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-As such, I assumed a normal error distribution, and fitted a least squares regression.
-To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
-\[
-	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
-.\]
-
-The Lotka--Volterra model is not linear in the parameters.
-With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
-With the rows grouped, however, this becomes impossible, for each species sill has its own growth rate.
-As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
 

### 2021-10-23 article.rnw
Add a missing word.

@@
 That is irrelevant to this study, so was excluded.
-Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra cannot accommodate.
+Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
 Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.

### 2021-10-23 article.rnw
Change "Lotka-Volterra model" for "species interaction model" where specificity is inappropriate.

@@
 The data consist of fecundity measurements for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-In this, they form essentially the standard experimental design for parameterising a Lotka--Volterra model, as described by \textcite{hart2018quantify}.
+In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.
 

### 2021-10-23 article.rnw
Specify that fecundity is measured in *surviving* offspring.

@@
 The data I used in this study were drawn from the work of \textcite{terry2021natural}.
-The data consist of fecundity measurements for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
+The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
 In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.

### 2021-10-23 article.rnw
Specify that I used maximum likelihood.
Prevent knitr automatically formatting in-line material.
It converts 41209 to exponential notation,
when the number is small enough that it need not.
Explain the model used and the species grouping in the methods.

@@
 	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
+	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
 @
@@
 
-\subsection{Model fitting}
+\subsection{Model}
 
-The models were fitted to the data using regression techniques.
+I fitted the Lotka--Volterra competition model to the data.
+As the response variable was fecundity, I used a discrete-time version of the model, as follows:
+\[
+	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
+,\]
+where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $i$ upon species $j$.
+$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
+The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.
+
+\subsubsection{Species grouping}
+
+The competition coefficients of the Lotka--Volterra model are typically arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects upon a single species, and a column contains all the competitive effects produced by a single species.
+This interpretation was used in the grouping of species, as it was rows or columns of this matrix that were grouped.
+
+Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
+Each model fit was performed with one grouping of the interaction matrix's rows, and an independent grouping of the columns.
+A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
+Given $n$ species, there may be any integer number of groups from $1$ to $n$.
+With $n$ groups, the grouping places each species into its own group, as though there were no grouping at all.
+With $1$ group, every species is placed in the same group, such that all are considered to be equal in their competitive effect or response, reminiscent of the neutral model.
+Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups.
+The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
+With six species, and the row and column groupings chosen independently, the total number of possible models is $B_6^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
+
+Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same column grouping were contrained to have the same competitive response to all other species.
+Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}=\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}=\alpha_{bj} \, \forall j$.
+As such, the total number of free competition coefficients in the model was equal to the number of row groups times the number of column groups.
+The species' instrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
+
+\subsubsection{Model fitting}
+
+The models were fitted to the data using maximum likelihood regression techniques.
 Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.

### 2021-10-24 article.rnw
Add a section to the methods on assessing parsimony.

@@
 
+\subsubsection{Assessing parsimony}
+
+To assess the parsimony of each moel, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
+As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' \parencite{aho2014model}.
+Further, AIC will be more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
+As such, I calculated the AIC for each model.
+
+AIC values can be compared to determine which is the most parsimonious model, but cannot directly be interpreted to find the significance of the difference in parsimony.
+As such, I converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
+These give the probability, for each model, that it is the best among the models assessed.
+All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.
+
+%TODO: Explain the coclassification matrices and the tests.
+
 \subsection{Phylogeny}

### 2021-10-24 article.rnw
Add the text of the results.

@@
 @
+
+\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
+\newcommand\aicnum[1]{\num{#1}}
+\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
 
@@
 
+The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
+The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
+\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
+%TODO: The AIC histogram.
+
+The ``best'' model, as indicated by AIC, was not the best with any surety; the Akaike weights indicated only a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
+As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of together (coclassified the pair of species).
+These results are shown in \cref{fig:coclassification}.
+
+In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{60}{\percent}.
+Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
+
+The structure of the coclassifications was very different in the row groups than in the column groups.
+Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
+Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
+Overall, more coclassification occurred in the row groupings than in the column groupings.
+
+A high likelihood of coclassification in the row groupings was typically transitive: e.g.\ \emph{D.
+birchii}, \emph{D.
+pallidifrons} and \emph{D.
+sulfurigaster} each had a relatively high probability of being coclassified with one another.
+More intransitivity was observed in the column groupings: \emph{D.
+simulans} had a relatively high probability of being coclassified with \emph{D.
+sulfurigaster}, and \emph{D.
+sulfurigaster} had a substantial probability of being coclassified with \emph{D.
+pallidifrons}, but \emph{D.
+simulans} had a much lower probability of being coclassified with \emph{D.
+pallidifrons}.
+
 \pgfplotsset{%

### 2021-10-24 article.rnw
Add the relation between coclassification and phylogeny to the results.

@@
 	\end{forest}
+	%TODO: Mark subgroups and subgenuses on the diagram.
 
@@
 pallidifrons}.
+
+A high likelihood of coclassifcation was associated with phylogeny in one instance, but by no means consistently.
+The phylogeny divides the six spcies into three most closely related pairs (\cref{fig:phylogeny}).
+The pair of \emph{D.
+pallidifrons} and \emph{D.
+sulfurigaster}, which both belonged to a different subgenus than the other four species, were also the only pair of species to be coclassified with relatively high probability in both the row and column groupings.
+In constrast, each of the other pairs were coclassified with very low probabilities in both the row and column groupings.
+Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D.
+sulfurigaster} and \emph{D.
+simulans}, while the column groupings frequently coclassified both \emph{D.
+pallidifrons} and \emph{D.
+sulfurigaster} of the Drosophila subgenus with \emph{D.
+birchii} of the Sophophora subgenus.
 

### 2021-10-24 article.rnw
Add a quick and dirty AIC histogram.

@@
 \Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
-%TODO: The AIC histogram.
+
+\begin{figure}
+	<<echo=FALSE>>=
+		hist(brute_data$statistics$aic,
+			main="",
+			xlab="AIC",
+			xaxs='i',
+			yaxs='i'
+		)
+		abline(v = brute_data$fully_separated_statistics$aic, lwd=2, lty="dashed", col="green")
+		abline(v = brute_data$fully_grouped_statistics$aic, lwd=2, lty="dashed", col="red")
+	@
+
+	\caption{%
+		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
+		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
+		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair os species shares a single interaction coefficient.
+	}
+	\label{fig:aic}
+\end{figure}
+
+\subsection{Coclassification of species}
 

### 2021-10-24 r/brute-post-process.R
Change the brute post-processing prob_perm_test() to perform the test with whichever tail is appropriate.

@@ -4,7 +4,7 @@
 library(magrittr)
 
 prob_perm_test <- function(selected_probs, all_probs, num_iter = 1000) {
-	#Tests whether the sum of selected_probs is less than the sum of a random sample of all_probs of the same length.
+	#Tests whether the sum of selected_probs is more or less (as appropriate) than the sum of a random sample of all_probs of the same length.
 	#Returns the p value.
 	#TODO: Check that this is a valid statistical test.
 	selected_sum <- sum(selected_probs)
@@ -12,8 +12,11 @@ prob_perm_test <- function(selected_probs, all_probs, num_iter = 1000) {
 		sum(sample(all_probs, length(selected_probs)))
 	)
 	resamples <- c(selected_sum, resamples)
-	p <- mean(resamples <= selected_sum)
-	return(p)
+	
+	#Try the test both ways around, return whichever is appropriate.
+	p_less <- mean(resamples <= selected_sum)
+	p_more <- mean(resamples >= selected_sum)
+	return(min(p_less, p_more))
 }
 
 BruteData <- R6::R6Class("BruteData",

### 2021-10-24 article.rnw
Add a subheading for the coclassification section of the results.
I expect to add more results before this section,
so separating it will be useful.
Add some additional numbers to the results section.

@@
 The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
+The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}.
 \Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
@@
 \end{figure}
+
+The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
+The total Akaike weight assigned to models in which the rows and columns used the same grouping was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
 

### 2021-10-24 article.rnw
Correct a misspelled reference label.

@@
 Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
-Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriate2004spatially,ovaskainen2017species,weiss2021disentangling}.
+Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
 The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.

### 2021-10-24 article.rnw
Correct spelling.

@@
 		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair os species shares a single interaction coefficient.
+		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair of species shares a single interaction coefficient.
 	}

### 2021-10-24 article.rnw
Add the discussion.

@@
 
+\section{Discussion}
+
+The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}), but not confidently so.
+Which grouping might give the most parsimonious model also could not be determined with any confidence.
+The intransitivity of coclassification in some instances even suggests that, in some cases, there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+
+This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
+It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a qualitative competitive context.
+Perhaps species simply do not group to the same extent in a competitive context.
+The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
+Further, there is no reason to suspect that speies would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
+Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.
+
+I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species phylogenetic relationships.
+Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
+A study system with species spanning multiple functional groups, however, might have shown clearer groupings.
+While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
+In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonimically (with both groupings defined \emph{a priori}).
+Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
+
+Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
+Alas, the algorithmic complexity of the brute force method I employed in this study is abyssmal, preventing the application of the method to studies with more than seven or eight species.
+As such, a better method would be required to test for grouping of species interactions among a larger set of species.
+
+In light of the failure to produce clear groups, perhaps the most curious aspect of the results is the disagreement between the likely coclassifications of species in the groupings of rows and of columns.
+This is perhaps not surprising in hindsight, for there is no necessity that species respond to competition in the same manner that they cause it, especially in competition for certain resources such as space (the limiting resource presumed in these data) or light.
+Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
+These results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
+
+All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely reated set of species.
+However, the results suggest a number of pieces of advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.
+Firstly, there may be no single best grouping, but perhaps multiple rather distinct groupings which each perform similarly.
+Secondly, phylogeny does not appear to provide appropriate groupings.
+Lastly, one should not implicitly assume that species are grouped in the same way with regard to their effects upon other species and their response to them; distinct groupings of the two might well be considered.
+
 \FloatBarrier

### 2021-10-24 article.rnw
Correct spelling.

@@
 However, making any use of a model requires experimentally or observationally determining the values of each parameter in the model.
-This poses a problem for species interacton models, due to the sheer number of parameters that must be determined.
+This poses a problem for species interaction models, due to the sheer number of parameters that must be determined.
 Even the simplest models, with no environmental dependence, require one parameter for the interaction of each pair of species \parencite{novak2016characterizing}.
@@
 
-I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which gives the most parsimonius model.
+I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which gives the most parsimonious model.
 In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
@@
 
-Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same column grouping were contrained to have the same competitive response to all other species.
+Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same column grouping were constrained to have the same competitive response to all other species.
 Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}=\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}=\alpha_{bj} \, \forall j$.
 As such, the total number of free competition coefficients in the model was equal to the number of row groups times the number of column groups.
-The species' instrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
+The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
 
@@
 
-To assess the parsimony of each moel, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
+To assess the parsimony of each model, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
 As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' \parencite{aho2014model}.
@@
 	\end{forest}
-	%TODO: Mark subgroups and subgenuses on the diagram.
+	%TODO: Mark subgroups and subgenera on the diagram.
 
@@
 
-A high likelihood of coclassifcation was associated with phylogeny in one instance, but by no means consistently.
-The phylogeny divides the six spcies into three most closely related pairs (\cref{fig:phylogeny}).
+A high likelihood of coclassification was associated with phylogeny in one instance, but by no means consistently.
+The phylogeny divides the six species into three most closely related pairs (\cref{fig:phylogeny}).
 The pair of \emph{D.
@@
 sulfurigaster}, which both belonged to a different subgenus than the other four species, were also the only pair of species to be coclassified with relatively high probability in both the row and column groupings.
-In constrast, each of the other pairs were coclassified with very low probabilities in both the row and column groupings.
+In contrast, each of the other pairs were coclassified with very low probabilities in both the row and column groupings.
 Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D.
@@
 The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
-Further, there is no reason to suspect that speies would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
+Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
 Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.
@@
 While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
-In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonimically (with both groupings defined \emph{a priori}).
+In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
 Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
@@
 Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
-Alas, the algorithmic complexity of the brute force method I employed in this study is abyssmal, preventing the application of the method to studies with more than seven or eight species.
+Alas, the algorithmic complexity of the brute force method I employed in this study is abysmal, preventing the application of the method to studies with more than seven or eight species.
 As such, a better method would be required to test for grouping of species interactions among a larger set of species.
@@
 
-All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely reated set of species.
+All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely related set of species.
 However, the results suggest a number of pieces of advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.

### 2021-10-24 article.rnw
Add a TODO with potential expansion for the methods/results.
Add the main result to the title of the article.
Add the abstract.

@@
 %Title Page
-\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping}
+\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping: Optimal Groupings Are Unpredictable}
 \author{
@@
 \maketitle
+
+\section*{Abstract}
+
+Dynamic models of ecological communities require many parameters, making them expensive to fit.
+To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogeny or functional groups, and species within a group are assumed to behave identically.
+Herein, I assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to fecundity data from six competing species of \emph{Drosophila} in laboratory conditions.
+I find evidence that grouping can benefit the parsimony of species interaction models, but that there is no single optimal grouping.
+Further, those groupings that did prove beneficial could not be predicted from information available \emph{a priori}, calling the method of \emph{a priori} species grouping into question.
+Lastly, I find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.
 
@@
 
+%TODO: Use Terry et al. table S1 for additional classification information. The two species that coclassify in both columns and rows are substantially larger.
+
 \section{Results}

### 2021-10-24 article.rnw
Sentence-case the title, as the journal style requires.
Change to using the citation and bibliography for the "Ecology" journal.
As required by the assignment.
Add more details on the equivalently grouped models to the results.

@@
 %Referencing
-\import{reference-styles/}{authoryear.tex}
+\import{reference-styles/}{ecology.tex}
 \addbibresource{bibliography/references.bib}
@@
 %Title Page
-\title{Regularising Lotka--Volterra Interaction Matrices by Species Grouping: Optimal Groupings Are Unpredictable}
+\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
 \author{
@@
 The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
-The total Akaike weight assigned to models in which the rows and columns used the same grouping was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
+
+Considering only models in which the rows and columns used the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
+The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
 

### 2021-10-24 article.rnw
MMove the title onto its own page, as required by the journal style.
Move figures to the end of the document, as required by the journal style.
This is done using the endfloat package, creating some new intermediate files.
As such, the make clean rule and the gitignore files have also been updated.
Add author affiliation.
Rearrange the preamble with section header comments.
Set the page size and font size the journal requires.
Add line numbers and double spacing.
Begin page numbering from the title page.
COnfigure endfloat to handle tables.
Add a list of key words to the article.

@@
-\documentclass[a4paper,11pt]{article}
+\documentclass[12pt,titlepage]{article}
 \usepackage{amsmath}
@@
 \usepackage{import}
+\usepackage{authblk}
 
+%Images
 \usepackage{subcaption}
@@
 \usepackage{colortbl}
+
+\import{latex/}{forest-phylogeny}
+
+%Journal font & paper requirements
+\usepackage{newtxtext} %Times New Roman
+\usepackage[letterpaper,margin=1in]{geometry}
+
+%Preprint
+\usepackage{lineno} \linenumbers
+\usepackage{setspace} \doublespacing
+\usepackage[nomarkers,tablesfirst,notablist]{endfloat}
+\addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.
+
+%Ensure title page is numbered, as journal style requires it.
+%Using https://tex.stackexchange.com/a/172005, adapted not to bother with two column stuff.
+\makeatletter
+\renewenvironment{titlepage}{\thispagestyle{plain}}{\newpage}
+\makeatother
 
@@
 
-\import{latex/}{forest-phylogeny}
-
 %Title Page
 \title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
-\author{
-	Christopher R. P. Brown
-}
+\author{Christopher R. P. Brown}
+\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
 \date{}
@@
 
+\newcommand\keywords[1]{\emph{Key words: #1}}
+
 \begin{document}
@@
 Lastly, I find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.
+
+\keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony; phylogeny}
 

### 2021-10-24 article.rnw
Add the Acknowledgements.
Centre the coclassification matrix subfigures.
They had somehow become left aligned, possibly with the use of endfloat.

@@
 	\begin{subfigure}{\textwidth}
+		\centering
 		<<echo=FALSE>>=
@@
 
+\section*{Acknowledgements}
+
+I thank Daniel B. Stouffer for advice throughout the study, and particularly for making me aware of Akaike weights and suggesting the use of coclassification matrices.
+
 \FloatBarrier

### 2021-10-24 article.rnw
Perform a final copy-edit of the article before submission.

@@
 Models have long been used in ecology community \parencite{lotka1925elements}.
-They allow us to make predictions about things we cannot directly observe, be it the response of a community to a novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel community \parencite{maynard2020predicting}.
+They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
 The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.
@@
 On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
-While attempts have been made to define functional groups more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
+While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
 As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
@@
 
-I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which gives the most parsimonious model.
+I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which grouping gives the most parsimonious model.
 In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
@@
 
-The experiment also included a number of other vials that were excluded for various reasons.
+The experiment also included a number of other vials that were excluded from the analysis for various reasons.
 The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
@@
 ,\]
-where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $i$ upon species $j$.
+where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ upon species $i$.
 $N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
@@
 
-Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same column grouping were constrained to have the same competitive response to all other species.
+Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same row grouping were constrained to have the same competitive response to all other species.
 Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}=\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}=\alpha_{bj} \, \forall j$.
-As such, the total number of free competition coefficients in the model was equal to the number of row groups times the number of column groups.
+As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
 The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
@@
 With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
-With the rows grouped, however, this becomes impossible, for each species sill has its own growth rate.
+With the rows grouped, however, this becomes impossible, for each species still has its own growth rate.
 As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
@@
 To assess the parsimony of each model, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
-As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' \parencite{aho2014model}.
-Further, AIC will be more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
+As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
+Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
 As such, I calculated the AIC for each model.
@@
 
-\Textcite{terry2021natural} give the subgroups of the genus to which each study species belongs.
-\Textcite{lewis2005phylogeny} gives the relationship between three of these subgroups (melanogaster, ananassae, and montium), all of the subgenus Sophophora, while \textcite{izumitani2016phylogeography} describe the fourth subgroup (nasuta) as belonging to the distinct Drosophila subgenus.
+\Textcite{terry2021natural} gave the subgroups of the genus to which each study species belongs.
+\Textcite{lewis2005phylogeny} gave the relationship between three of these subgroups (melanogaster, ananassae, and montium), all of the subgenus Sophophora, while \textcite{izumitani2016phylogeography} described the fourth subgroup (nasuta) as belonging to the distinct Drosophila subgenus.
 From this can be constructed the necessary relationships, which are depicted in \cref{fig:phylogeny}.
@@
 
-Considering only models in which the rows and columns used the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
+Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
@@
 
-The ``best'' model, as indicated by AIC, was not the best with any surety; the Akaike weights indicated only a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
-As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of together (coclassified the pair of species).
+The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
+As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
 These results are shown in \cref{fig:coclassification}.
@@
 A high likelihood of coclassification was associated with phylogeny in one instance, but by no means consistently.
-The phylogeny divides the six species into three most closely related pairs (\cref{fig:phylogeny}).
+The phylogeny divided the six species into three pairs of most closely related species (\cref{fig:phylogeny}).
 The pair of \emph{D.
@@
 sulfurigaster}, which both belonged to a different subgenus than the other four species, were also the only pair of species to be coclassified with relatively high probability in both the row and column groupings.
-In contrast, each of the other pairs were coclassified with very low probabilities in both the row and column groupings.
+In contrast, both of the other most closely related pairs were coclassified with very low probabilities in both the row and column groupings.
 Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D.
-sulfurigaster} and \emph{D.
-simulans}, while the column groupings frequently coclassified both \emph{D.
+sulfurigaster}of the Drosophila subgenus and \emph{D.
+simulans} of the Sophophora subgenus, while the column groupings frequently coclassified both \emph{D.
 pallidifrons} and \emph{D.
@@
 
-The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}), but not confidently so.
+The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped, but not confidently so.
 Which grouping might give the most parsimonious model also could not be determined with any confidence.
-The intransitivity of coclassification in some instances even suggests that, in some cases, there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
 
@@
 
-I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species phylogenetic relationships.
+I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species' phylogenetic relationships.
 Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
@@
 While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
-In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
+In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based on light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
 Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
@@
 Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
-Alas, the algorithmic complexity of the brute force method I employed in this study is abysmal, preventing the application of the method to studies with more than seven or eight species.
-As such, a better method would be required to test for grouping of species interactions among a larger set of species.
+Alas, the brute force method I employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
+As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
 
@@
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
-These results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
+My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
+%TODO: Discuss the fact that species were coclassified more in the rows than in the columns.
 

### 2021-11-29 article.rnw
Fix a pair of swapped words.
Swap alpha_{ij} and N_j in the model formulation.
To conform to standard notation.

@@
 
-Models have long been used in ecology community \parencite{lotka1925elements}.
+Models have long been used in community ecology \parencite{lotka1925elements}.
 They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
@@
 \[
-	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
+	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
 ,\]
@@
 \[
-	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j N_{j,t} \alpha_{ij}\right)
+	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
 .\]

### 2021-11-29 article.rnw
Bracket (B_6)^2 for notational clarity.

@@
 The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
-With six species, and the row and column groupings chosen independently, the total number of possible models is $B_6^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
+With six species, and the row and column groupings chosen independently, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
 

### 2021-12-22 article.rnw
some DBS edits to and comments about the article up to the Discussion

--- 2021-11-29 article.rnw
@@
 
+% DBS: We should have a conversation regarding authorship.
+To me, it makes perfect sense thus far that you are the sole author.
+Depending on how revisions go and what anyone else or I do or do not contribute, it may be appropriate for this to change.
+In many such instances, I often think that the lead author (i.e., you) will have the best feeling for this relative to the criteria set out in the Vancouver guidelines for authorship.
+
 <<include=FALSE>>=
@@
 
+% DBS: I'll leave the abstract free of comments until the main text is closer to the final version.
+
 \section*{Abstract}
@@
 They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
-The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide.
+The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{XXX}.
 
-However, making any use of a model requires experimentally or observationally determining the values of each parameter in the model.
-This poses a problem for species interaction models, due to the sheer number of parameters that must be determined.
-Even the simplest models, with no environmental dependence, require one parameter for the interaction of each pair of species \parencite{novak2016characterizing}.
-Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for a community of just \num{10} species.
+Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
+This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
+Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
+Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
 Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
 This is expensive, and requires a lot of effort.
-As such, these models are typically restricted to a small number of focal species \parencite{ovaskainen2017species}.
-Real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
-We need a way to reduce the number of parameters the models require, to regularise them.
+As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
+However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
+To bridge this gap between XXX and YYY, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
 
@@
 
-Regularisation is often performed by assuming that species fall into groups, such that all species in the same group interact with other species in the same fashion, thereby collapsing interaction parameters for all the species in that group into one parameter \parencite{ovaskainen2017species,weiss2021disentangling}.
-Such groups have been defined \emph{a priori}, by phylogeny at some taxonomic level, or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
-The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
-However, tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
+In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}.
+One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}.
+XXX why this could be a problem XXX
+Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
+
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
+The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself \cite{XXX}) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
+% DBS: the preceding sentence could be simplified a fair bit
+However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
 On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
 While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
-As such, applying these to species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
-In all, we are left with the question of how best to group species in community models.
+As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
+In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful fashion with less data than required for a fully pairwise parameterisation.
 
-I propose that groups might be selected without regard to any \emph{a priori} definition, based purely upon which grouping gives the most parsimonious model.
-In this study, I investigate the usefulness and correctness of such a selection, using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
+I propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
+% DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks.
+I can point to some very good references along those lines.
+In this study, I investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
 I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
@@
 Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
+% DBS: I feel like the last sentences of this paragraph, from "In this study,..." onward should be rephrased to be more user friendly and without introducing new concepts (e.g., rows vs columns).
+If that info is important for the introduction, it ought to appear before the "This is what we do here" paragraph.
 
@@
 The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-In this, they form essentially the standard experimental design for parameterising a species interaction model, as described by \textcite{hart2018quantify}.
+This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \textcite{hart2018quantify, XXX}.
 
@@
 The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
-A number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
+A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
 The number of adult pairs of each species emerging from these eggs---i.e.\ the size of the next generation---was the response variable.
+% DBS: CRPB to fix this response variable when he fixes the model formula to reflect number of offspring.
 
@@
 
+% DBS: We should probably remove all of the following except the bit about a single founding pair since it's the only thing with direct bearing on how this model gets fit.
+For reference, it's not hard to add an Allee effect to a LV model if we wanted to add another set of parameters, though I understand why we probably don't!
 The experiment also included a number of other vials that were excluded from the analysis for various reasons.
@@
 
+Further details of the experimental methodology can be found in \textcite{terry2021natural}.
+
 \subsection{Model}
 
-I fitted the Lotka--Volterra competition model to the data.
-As the response variable was fecundity, I used a discrete-time version of the model, as follows:
+As the response variable was fecundity, I used a discrete-time version of the Lotka--Volterra competition model given by:
 \[
@@
 ,\]
-where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ upon species $i$.
+% DBS: CRPB to update the equation above after consideration of experimental response variable.
+where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ on species $i$.
 $N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
@@
 
+% DBS: We might want to be prepared for reviewers asking us to change from a linear LV model.
+
 \subsubsection{Species grouping}
 
-The competition coefficients of the Lotka--Volterra model are typically arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects upon a single species, and a column contains all the competitive effects produced by a single species.
+The set of competition coefficients in the Lotka--Volterra model can be  arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
 This interpretation was used in the grouping of species, as it was rows or columns of this matrix that were grouped.
+% DBS: Similar to my comment above, I'm not sure the rows vs column groupings is sufficiently introduced to this point.
+So I think we need more than a single sentence explaining this idea.
+Since it appears below, we can reiterate the meaning in terms of equivalence of competitive responses and equivalence of competitive effects.
 
 Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
-Each model fit was performed with one grouping of the interaction matrix's rows, and an independent grouping of the columns.
+Each model fit was performed with one grouping of the interaction matrix's rows and a second, independent grouping of the matrix's columns.
 A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.
-With $n$ groups, the grouping places each species into its own group, as though there were no grouping at all.
-With $1$ group, every species is placed in the same group, such that all are considered to be equal in their competitive effect or response, reminiscent of the neutral model.
-Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups.
+With $n$ groups, the grouping places each species into its own group, such that all species interact in a unique fashion.
+With $1$ group, every species is placed in the same group, such that all are equal in their competitive effects or responses, reminiscent of the neutral model.
+Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups. % DBS: Is this sentence essential?
 The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
-With six species, and the row and column groupings chosen independently, the total number of possible models is $B_6^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
+With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
 
 Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same row grouping were constrained to have the same competitive response to all other species.
-Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}=\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}=\alpha_{bj} \, \forall j$.
+Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$.
 As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
@@
 
+% DBS: I think my comments at the top of the previous section really boil down to simply reorganizing the pieces in the different paragraphs so that they more clearly build on each other linearly.
+
 \subsubsection{Model fitting}
 
-The models were fitted to the data using maximum likelihood regression techniques.
-Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-As such, I assumed a normal error distribution, and fitted a least squares regression.
-To prevent heteroskedasticity, I used the \emph{per capita} fecundity as the response variable, as in the following model:
+The Lotka--Volterra model is not linear in the parameters.
+With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.
+With the rows grouped, however, this becomes impossible since each species still has an independent growth rate.
+As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
+%The models were fitted to the data using maximum likelihood regression techniques.
+%Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
+I assumed a normal error distribution of the response variable. and 
+to prevent heteroskedasticity and improve normality, I transformed total fecundity to \emph{per capita} fecundity, which corresponds to the following model:
 \[
@@
 .\]
-
-The Lotka--Volterra model is not linear in the parameters.
-With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters, by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$.
-With the rows grouped, however, this becomes impossible, for each species still has its own growth rate.
-As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
+% DBS: CRPB to alter equation above consist with changes to previous equations.
 
@@
 
-To assess the parsimony of each model, all \num{\Sexpr{numbers::bell(6)^2}} possible models were fitted.
+To assess the parsimony of the different species groupings, I exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
 As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
@@
 As such, I calculated the AIC for each model.
+% DBS: Is it possible that the dataset is small enough that we should be using AICc instead?
 
-AIC values can be compared to determine which is the most parsimonious model, but cannot directly be interpreted to find the significance of the difference in parsimony.
-As such, I converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
-These give the probability, for each model, that it is the best among the models assessed.
+AIC values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
+As such, I also converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
+These give the probability that each model is the best among the models assessed.
 All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.
+% DBS: I find the last sentence above to be worded a bit cryptically.
 
@@
 \subsection{Phylogeny}
+% DBS: For now, I would cut out the bit about phylogeny since it's relatively weak without a properly calibrated tree.
+If you want to do a post hoc test, I would go with one that looks at body size and co-classification matrices.
+On the other hand, my gut tells me that the paper stands on its own merits without a post hoc test, and this is an easy thing to guide reviewers toward commenting on/requesting that you also know how to address.
+So it might be a useful strategic omission.
 
@@
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
+% DBS: I think the last sentence above needs a bit of elaboration here OR the usefulness of this "test" should be explained in the Methods in the section that discusses how we examined aspects of parsimony.
 
@@
 These results are shown in \cref{fig:coclassification}.
+% DBS: Much of the paragraph above is probably more appropriate at Methods text whereas in the Results we should discuss the patterns that emerge from the co-classification matrices.
 
@@
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
+% DBS: As I have noted before, I'd like to know what the null expectation is for this before claiming confidence of being co-classified or not being co-classified.
+Firstly, I think that the random expectation is much lower than one might otherwise suspect.
+(For three species, it is already 2/5.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.
 
@@
 Overall, more coclassification occurred in the row groupings than in the column groupings.
+% DBS: In the network modularity literature, there is a nice measure of mutual information between two partitions.
+I wonder if we could exploit that here to give a quantitative measure of similarity between the two.
+Or we could just convert the two matrices to distance matrices and run a Procrustes to measure their similarity?
 

### 2021-12-22 src/data.hpp
Include stddef.h when necessary.
I'm not sure why I could compile this without stddef; size_t should require it.
My compiler must have automatically defined size_t.
This should allow this to compile on a compiler without such automatic definition.

@@ -1,6 +1,7 @@
 #ifndef DATA_HPP
 #define DATA_HPP
 
+#include <stddef.h>
 #include <assert.h>
 #include <vector>
 #include <Eigen/Core>

### 2022-02-21 article.rnw
adding one more by-hand calculation about null co-classification
adding a note regarding an idea for another figure
adding some comments to the discussion
Add Daniel as an author.
In doing so, remove him from the acknowledgements.
Fix a mangled sentence break.

@@
 \title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
-\author{Christopher R. P. Brown}
+\author{Christopher R.\ P.\ Brown}
+\author{Daniel B.\ Stouffer}
 \affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
 \date{}
-
-% DBS: We should have a conversation regarding authorship.
-To me, it makes perfect sense thus far that you are the sole author.
-Depending on how revisions go and what anyone else or I do or do not contribute, it may be appropriate for this to change.
-In many such instances, I often think that the lead author (i.e., you) will have the best feeling for this relative to the criteria set out in the Vancouver guidelines for authorship.
 
@@
 %Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-I assumed a normal error distribution of the response variable. and 
-to prevent heteroskedasticity and improve normality, I transformed total fecundity to \emph{per capita} fecundity, which corresponds to the following model:
+I assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, I transformed total fecundity to \emph{per capita} fecundity, which corresponds to the following model:
 \[
@@
 Firstly, I think that the random expectation is much lower than one might otherwise suspect.
-(For three species, it is already 2/5.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.
+(For three species, it is already 2/5; for four species, it is 5/15.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.
 
@@
 
+% DBS: I think a good figure would be to show the ungrouped estimated alpha matrix in one panel and the alpha matrix averaged across all partitions in a second panel, with lines drawn in the second to reflect the "optimal" partitioning of the co-classification matrices.
+
 \section{Discussion}
 
+% DBS: I would start this paragraph with a restatement of the overall premise.
 The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped, but not confidently so.
 Which grouping might give the most parsimonious model also could not be determined with any confidence.
+% DBS: The two preceding sentences are very glass half empty. I'm also not sure that the results are really so equivocal. What makes you feel this way?
 The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+% DBS: In my mind, I would steal the preceding sentence and spin it potentially spin it into its own paragraph later since it speaks strongly to a mixed-membership approach which could be sold as a "future direction".
 
+% DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
 This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
@@
 Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
+% DBS: Prolix warning! ;)
 
 Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
+% DBS: Personally, I try to make links to previous studies more self contained.
+Since the Allesina paper and its use of AIC was brought up earlier, it strikes me as repetitive to lean on it alone again here.
 Alas, the brute force method I employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
@@
 
+% DBS: The paragraph below is a very good example of text that could easily be simplified for clarity without losing important content.
 In light of the failure to produce clear groups, perhaps the most curious aspect of the results is the disagreement between the likely coclassifications of species in the groupings of rows and of columns.
 This is perhaps not surprising in hindsight, for there is no necessity that species respond to competition in the same manner that they cause it, especially in competition for certain resources such as space (the limiting resource presumed in these data) or light.
+% DBS: Some definite refs missing here.
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
@@
 
-\section*{Acknowledgements}
-
-I thank Daniel B. Stouffer for advice throughout the study, and particularly for making me aware of Akaike weights and suggesting the use of coclassification matrices.
-
 \FloatBarrier

### 2022-02-21 article.rnw
Flag as an incomplete sentence as a TODO.

@@
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}.
-XXX why this could be a problem XXX
+%TODO: XXX why this could be a problem XXX.
 Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

### 2022-02-21 article.rnw
Add a missing semantic newline.
Break some preamble code in the report into more statements.
Declare the list of species names as its own variable, for clarity.
Reorder the species in the coclassifcation matrix figures, to show patterns more clearly.

@@
 	source("r/brute-post-process.R")
-	brute_data <- BruteData$new(
-		"output/brute.data",
-		c(
+
+	species_names <- c(
 		"D. birchii",
@@
 	)
-	)
+	species_output_order <- c(4,3,1,2,6,5)
+
+	brute_data <- BruteData$new("output/brute.data", species_names)
 
@@
 			weighted_coclassification_kable(
-				brute_data$weighted_col_coclassification_matrix,
+				brute_data$weighted_col_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
@@
 			weighted_coclassification_kable(
-				brute_data$weighted_row_coclassification_matrix,
+				brute_data$weighted_row_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"

### 2022-02-22 article.rnw
Add a missing space.
Fix a mix-up of the row and column groupings in the text of the results.

@@
 In contrast, both of the other most closely related pairs were coclassified with very low probabilities in both the row and column groupings.
-Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D.
-sulfurigaster}of the Drosophila subgenus and \emph{D.
-simulans} of the Sophophora subgenus, while the column groupings frequently coclassified both \emph{D.
+Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the column groupings frequently coclassified \emph{D.
+sulfurigaster} of the Drosophila subgenus and \emph{D.
+simulans} of the Sophophora subgenus, while the row groupings frequently coclassified both \emph{D.
 pallidifrons} and \emph{D.

### 2022-02-22 article.rnw
Fix the response variable to be population growth, instead of offspring population size.
Fix this in both the code and the report,
including updating the results text to account for changes in the results.

--- 2022-02-21 article.rnw
@@
 A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
-The number of adult pairs of each species emerging from these eggs---i.e.\ the size of the next generation---was the response variable.
-% DBS: CRPB to fix this response variable when he fixes the model formula to reflect number of offspring.
+The number of adult pairs of each species emerging from these eggs was counted---this was the size of the next generation.
 
@@
 
-As the response variable was fecundity, I used a discrete-time version of the Lotka--Volterra competition model given by:
+The data provided the change population size from one generation to the next, so I used a discrete-time version of the Lotka--Volterra competition model given by:
 \[
-	N_{i,t+1} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
+	N_{i,t+1} - N_{i,t} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
 ,\]
-% DBS: CRPB to update the equation above after consideration of experimental response variable.
-where $N_{i,t}$ is the population of species $i$ at time $t$, $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ on species $i$.
-$N_{i,t+1}$ is the size of the population in the following time-step, i.e.\ the number of surviving offspring, the fecundity, of the previous generation, and therefore is equal to the experimentally measured response variable.
+where $N_{i,t}$ is the population of species $i$ at time $t$ (the size of the parent generation), $N_{i,t+1}$ is the population at time $t+1$ (the size of the offspring generation), $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ on species $i$.
 The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.
@@
 %Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-I assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, I transformed total fecundity to \emph{per capita} fecundity, which corresponds to the following model:
+I assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, I transformed total population growth to \emph{per capita} population growth, which corresponds to the following model:
 \[
-	\frac{N_{i,t+1}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
+	\frac{N_{i,t+1} - N_{i,t}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
 .\]
-% DBS: CRPB to alter equation above consist with changes to previous equations.
 
@@
 
-In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{60}{\percent}.
+In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
@@
 
-A high likelihood of coclassification in the row groupings was typically transitive: e.g.\ \emph{D.
+A relatively high likelihood of coclassification in the row groupings was typically transitive: e.g.\ \emph{D.
 birchii}, \emph{D.
@@
 More intransitivity was observed in the column groupings: \emph{D.
-simulans} had a relatively high probability of being coclassified with \emph{D.
+pallidifrons} had a relatively high probability of being coclassified with \emph{D.
 sulfurigaster}, and \emph{D.
 sulfurigaster} had a substantial probability of being coclassified with \emph{D.
-pallidifrons}, but \emph{D.
-simulans} had a much lower probability of being coclassified with \emph{D.
-pallidifrons}.
+simulans}, but \emph{D.
+pallidifrons} had a much lower probability of being coclassified with \emph{D.
+simulans}.
 
@@
 In contrast, both of the other most closely related pairs were coclassified with very low probabilities in both the row and column groupings.
-Furthermore, both row and column groupings gave high probabilities of coclassification to pairs of species split across the two subgenera in the study---the row groupings frequently coclassified \emph{D.
-sulfurigaster}of the Drosophila subgenus and \emph{D.
-simulans} of the Sophophora subgenus, while the column groupings frequently coclassified both \emph{D.
-pallidifrons} and \emph{D.
-sulfurigaster} of the Drosophila subgenus with \emph{D.
-birchii} of the Sophophora subgenus.
 

### 2022-02-22 article.rnw
Correct "qualitative" to "quantitative".

@@
 This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
-It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a qualitative competitive context.
+It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
 Perhaps species simply do not group to the same extent in a competitive context.

### 2022-02-22 r/brute-post-process.R
Add a brute-force post-processing function for getting an unweighted average coclassification.
This is the null under the assumption that each partition occurs with equal probability.

@@ -23,6 +23,9 @@ BruteData <- R6::R6Class("BruteData",
 	inherit = Data,
 	
 	active = list(
+		unweighted_average_coclassification_matrix = function() {
+			return(private$annotate_matrix(private$get_average_coclassification_matrix(self$row_groupings)))
+		},
 		weighted_row_coclassification_matrix = function() {
 			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$row_groupings, self$statistics$aic_weight)))
 		},

### 2022-02-22 r/post-process.R
Add post-processing functions to get a fully grouped or fully separated coclassification matrix.
These are alternative null coclassification matrices.

@@ -133,6 +133,13 @@ Data <- R6::R6Class("Data",
 		fully_separated_statistics = function() {
 			grouping <- 1:self$num_species
 			return(private$get_statistics_row(grouping, grouping))
+		},
+		
+		fully_grouped_coclassification_matrix = function() {
+			return(matrix(1, self$num_species, self$num_species))
+		},
+		fully_separated_coclassification_matrix = function() {
+			return(diag(self$num_species))
 		}
 	)
 )

### 2022-02-22 article.rnw
Put all invocations of `source` in the R code of article.rnw in the same place.

@@
 	source("r/brute-post-process.R")
+	source("r/coclassification-table.R")
 
@@
 	brute_data <- BruteData$new("output/brute.data", species_names)
-
-	source("r/coclassification-table.R")
 @

### 2022-02-22 article.rnw
Precalculate the coclassification matrices in article.rnw.
Calculating these is the slowest part of compilations.
We don't want to recalculate them if we use them again.
They're only being used once currently, but that will soon change.

@@
 	brute_data <- BruteData$new("output/brute.data", species_names)
+
+	#Precalculate the coclassification matrices, as these are active bindings and the slowest part of compilation.
+	weighted_col_coclassification_matrix <- brute_data$weighted_col_coclassification_matrix
+	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix
 @
@@
 			weighted_coclassification_kable(
-				brute_data$weighted_col_coclassification_matrix[species_output_order,species_output_order],
+				weighted_col_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
@@
 			weighted_coclassification_kable(
-				brute_data$weighted_row_coclassification_matrix[species_output_order,species_output_order],
+				weighted_row_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"

### 2022-02-22 r/mantel-test.R
Add an R module for doing Mantel tests.

@@ -1,0 +1,29 @@
+#ape's implementation of the Mantel test doesn't give the correlation; it gies an unnormalised test statistic.
+#vegan's implementation doesn't give a p value; it gives a significance value with no control over the tail of the test.
+#So here I've rolled my own implementation.
+
+permute_matrix <- function(m) {
+	s <- sample(1:nrow(m))
+	return(m[s,s])
+}
+
+mantel_cor <- function(m1, m2) {
+	#Grab the upper triangles of both, and get the correlation between them.
+	return(cor(m1[upper.tri(m1)], m2[upper.tri(m2)]))
+}
+
+mantel_p <- function(m1, m2, nperm = 999, alternative = c("two.sided", "less", "greater")) {
+	alternative <- match.arg(alternative, c("two.sided", "less", "greater"))
+	obs_cor <- mantel_cor(m1, m2)
+	perm_cors <- replicate(nperm, mantel_cor(m1, permute_matrix(m2)))
+	
+	num_less <- sum(perm_cors <= obs_cor)
+	num_greater <- sum(perm_cors >= obs_cor)
+	num_counted <- switch(alternative,
+		two.sided = 2*min(num_less, num_greater),
+		less = num_less,
+		greater = num_greater
+	)
+	p <- (num_counted+1)/(nperm+1)
+	return(min(1, p))
+}

### 2022-03-07 r/procrustes-test.R
Add an R module for doing Procrustes tests.

@@ -1,0 +1,28 @@
+#A Procrustes test based upon two distance matrices.
+#Assuming the matrices are n by n, the distances are first converted to n points in n-1 dimensions.
+#This requires that the matrices be metric and Euclidean, so an additional function to check for that is included.
+#Finally, a Procrustes test is performed.
+
+#TODO: This performs a Procrustes test *with* scaling.
+#The coclassification matrices have meaningful distances, bounded between 0 and 1.
+#So we may want an unscaled Procrustes test.
+
+distance_matrix_is_euclidean <- function(m) {
+	return(ade4::is.euclid(as.dist(m)))
+}
+
+dist_to_coords <- function(m) {
+	return(cmdscale(as.dist(m), nrow(m)-1))
+}
+
+procrustes_test <- function(m1, m2) {
+	return(vegan::protest(dist_to_coords(m1), dist_to_coords(m2)))
+}
+
+procrustes_ss <- function(m1, m2) {
+	return(procrustes_test(m1, m2)$ss)
+}
+
+procrustes_p <- function(m1, m2) {
+	return(procrustes_test(m1, m2)$signif)
+}

### 2022-03-07 article.rnw
Add an R module for doing Mantel tests.
Use the species data file to get the species names in article.rnw.

@@
 	source("r/brute-post-process.R")
+	source("r/mantel-test.R")
 	source("r/coclassification-table.R")
 
-	species_names <- c(
-		"D. birchii",
-		"D. pallidifrons",
-		"D. pandora",
-		"D. pseudoananassae",
-		"D. simulans",
-		"D. sulfurigaster"
-	)
+	species_dat <- read.csv("data/species.csv")
 	species_output_order <- c(4,3,1,2,6,5)
 
-	brute_data <- BruteData$new("output/brute.data", species_names)
+	brute_data <- BruteData$new("output/brute.data", species_dat$name)
 

### 2022-03-14 r/dist-matrix.R
Add an R module for building distance matrices.

@@ -1,0 +1,18 @@
+#A set of helper functions for building distance matrices, for comparison with the coclassification matrices.
+
+build_dist_matrix <- function(species_names, data, dist_func) {
+	#Builds and annotates a distance matrix between species.
+	#Requires a vector of species names, and a vector of data about the species.
+	#dist_func must take two elements of the data vector, and return a distance.
+	#All elements, even the diagonal, will be filled with dist_func, so it should return 0 if given the same data twice.
+	#As usual for a distance function, it should be symmetric.
+	
+	m <- sapply(data, function(col_data){
+		sapply(data, function(row_data){
+			dist_func(col_data, row_data)
+		})
+	})
+	rownames(m) <- species_names
+	colnames(m) <- species_names
+	return(m)
+}

### 2022-03-14 article.rnw
Precompute the body-weight-based distance matrix in article.rnw.

@@
 	source("r/mantel-test.R")
+	source("r/dist-matrix.R")
 	source("r/coclassification-table.R")
@@
 	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix
+
+	#Precalculate distances matrices as well.
+	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
 @

### 2022-03-14 article.rnw
Precompute the row and column coclassification matrices as distance matrices in article.rnw.

@@
 	#Precalculate distances matrices as well.
+	col_distance_matrix <- 1 - weighted_col_coclassification_matrix
+	row_distance_matrix <- 1 - weighted_row_coclassification_matrix
 	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})

### 2022-03-19 article.rnw
Correct the comparator in an inequality.
The sentence previously stated that *over* 100 parameters
were required for a model of 10 species.
08b69117c28ed648a444812afb75dcaaeb6d4db4 changed the wording to
"*the interactions in* a model of 10 species",
so that the inequality should state *at least* 100 parameters required.

@@
 Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
-Hence the number of parameters scales quadratically with the number of species; over \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
+Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
 Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.

### 2022-03-20 article.rnw
Correct spelling.

@@
 This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
-Even the simplest models with no environmental dependence require one parameter to characterize the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
+Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
 Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.

### 2022-03-20 article.rnw
Complete the final setntence of the second paragraph of the introduction.
08b69117c28ed648a444812afb75dcaaeb6d4db4 left it with a couple of blanks to fill.

@@
 However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
-To bridge this gap between XXX and YYY, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
+To bridge this gap between the size of real communities and our ability to parameterise them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
 

### 2022-03-20 article.rnw
Remove an unnecessary sentence.
I don't think using the word "regularising" is helping much.
Apart from this sentence to explain what it is,
which doesn't mesh well with the paragraph it begins,
the word is only used in the title.
I think we're best off rewording the title and avoiding the word "regularising".

@@
 %Title Page
-\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
+\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable} %TODO: Remove the word "regularising" from the title.
 \author{Christopher R.\ P.\ Brown}
@@
 
-In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}.
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}.

### 2022-03-20 article.rnw
Add a missing reference.

@@
 
-%Several methods have been applied to regularise species interaction models, each with their own limitations.
-%For example, it is often assumed that most pairs of species don't interact, setting many of the parameters to zero \parencite{mutshinda2009drives,ovaskainen2017species}.
-%TODO: Find a citation for why this assumption doesn't hold.
-
-One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}.
+One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
 %TODO: XXX why this could be a problem XXX.

### 2022-03-20 article.rnw
Simplify the sentence explaining phylogeny-based grouping.
The mention of Darwin added nothing in particular.

@@
 In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
-The argument for grouping based on phylogeny is based on the principle (originally hypothesised by Darwin himself \cite{XXX}) that closely related species will be similar in (what we now know as) ecological niche, and thereby will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
-% DBS: the preceding sentence could be simplified a fair bit
+The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.

### 2022-03-20 article.rnw
Reword a sentence for ease of reading.

@@
 As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
-In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful fashion with less data than required for a fully pairwise parameterisation.
+In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful way using less data than required for a fully pairwise parameterisation.
 

### 2022-03-20 article.rnw
Add a paragraph to the introduction about grouping rows and columns independently.

@@
 
+Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how spcies respond to others \parencite{XXX}.
+There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
+As such, the best groupings of species may be different for each of the effects and responses.
+
 I propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
@@
 Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
-% DBS: I feel like the last sentences of this paragraph, from "In this study,..." onward should be rephrased to be more user friendly and without introducing new concepts (e.g., rows vs columns).
-If that info is important for the introduction, it ought to appear before the "This is what we do here" paragraph.
 

### 2022-03-20 article.rnw
Fix a missed semantic newline.
Remove the comparison with phylogeny from the article.
The comaprison was based on a qualitative, not quantitative, phylogeny.
As such it was weak, and non-rigorous.

@@
 \usepackage{colortbl}
-
-\import{latex/}{forest-phylogeny}
 
@@
 I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
-Finally, I compare the resultant groupings with species phylogeny, to provide further investigation of the suitability of \emph{a priori} phylogenetic grouping.
 
@@
 
-\subsection{Phylogeny}
-% DBS: For now, I would cut out the bit about phylogeny since it's relatively weak without a properly calibrated tree.
-If you want to do a post hoc test, I would go with one that looks at body size and co-classification matrices.
-On the other hand, my gut tells me that the paper stands on its own merits without a post hoc test, and this is an easy thing to guide reviewers toward commenting on/requesting that you also know how to address.
-So it might be a useful strategic omission.
-
-I determined the phylogenetic relationships between the six study species by examination of the literature, in order to compare these to the groupings generated by the models.
-No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
-Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.
-
-\Textcite{terry2021natural} gave the subgroups of the genus to which each study species belongs.
-\Textcite{lewis2005phylogeny} gave the relationship between three of these subgroups (melanogaster, ananassae, and montium), all of the subgenus Sophophora, while \textcite{izumitani2016phylogeography} described the fourth subgroup (nasuta) as belonging to the distinct Drosophila subgenus.
-From this can be constructed the necessary relationships, which are depicted in \cref{fig:phylogeny}.
-
-\begin{figure}
-	\centering
-	\begin{forest} phylogeny
-		[
-			[
-				[
-					[\emph{D. simulans}]
-					[\emph{D. birchii}]
-				]
-				[
-					[\emph{D. pandora}]
-					[\emph{D. pseudoananassae}]
-				]
-			]
-			[
-				[
-					[\emph{D. pallidifrons}]
-					[\emph{D. sulfurigaster}]
-				]
-			]
-		]
-	\end{forest}
-	%TODO: Mark subgroups and subgenera on the diagram.
-
-	\caption{%
-		The phylogenetic relationships between the six \emph{Drosophila} species in the study.
-		The relationships depicted are purely qualitative; no implication of phylogenetic distance is made.
-	}
-	\label{fig:phylogeny}
-\end{figure}
-
 %TODO: Use Terry et al. table S1 for additional classification information. The two species that coclassify in both columns and rows are substantially larger.
@@
 
-A high likelihood of coclassification was associated with phylogeny in one instance, but by no means consistently.
-The phylogeny divided the six species into three pairs of most closely related species (\cref{fig:phylogeny}).
-The pair of \emph{D.
-pallidifrons} and \emph{D.
-sulfurigaster}, which both belonged to a different subgenus than the other four species, were also the only pair of species to be coclassified with relatively high probability in both the row and column groupings.
-In contrast, both of the other most closely related pairs were coclassified with very low probabilities in both the row and column groupings.
-
 \pgfplotsset{%
@@
 
-I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species' phylogenetic relationships.
-Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
-A study system with species spanning multiple functional groups, however, might have shown clearer groupings.
-While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
-In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based on light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
-Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
+%TODO: Discuss the potential to study a system with functional groups without brining up phylogeny.
+%I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species' phylogenetic relationships.
+%Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
+%A study system with species spanning multiple functional groups, however, might have shown clearer groupings.
+%While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
+%In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based on light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
+%Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
 % DBS: Prolix warning! ;)
@@
 All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely related set of species.
-However, the results suggest a number of pieces of advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.
+However, the results suggest some advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.
 Firstly, there may be no single best grouping, but perhaps multiple rather distinct groupings which each perform similarly.
-Secondly, phylogeny does not appear to provide appropriate groupings.
-Lastly, one should not implicitly assume that species are grouped in the same way with regard to their effects upon other species and their response to them; distinct groupings of the two might well be considered.
+Furthermore, one should not implicitly assume that species are grouped in the same way with regard to their effects upon other species and their response to them; distinct groupings of the two might well be considered.
 

### 2022-03-20 article.rnw
Remove unnecessary mentions of excluded treatments from the methods.
They have no direct bearing on our model, and most of the details
are already in Terry et al.

@@
 The two-species densities were, giving the densities of each of the two species, (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial, each replicated three times per pair of species.
-
-% DBS: We should probably remove all of the following except the bit about a single founding pair since it's the only thing with direct bearing on how this model gets fit.
-For reference, it's not hard to add an Allee effect to a LV model if we wanted to add another set of parameters, though I understand why we probably don't!
-The experiment also included a number of other vials that were excluded from the analysis for various reasons.
-The original authors' study was on parasitism, so the experiments also included a parasitised treatment.
-That is irrelevant to this study, so was excluded.
 Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
-Lastly, an additional set of vials were raised in colder temperatures, but were excluded from this study and the original authors' as the resulting emergence was too low to analyse.
 

### 2022-03-20 article.rnw
Correct a \textcite to a \parencite.
The sentence was refactored around the citation in 08b69117c28ed648a444812afb75dcaaeb6d4db4
such that a textcite was no longer appropriate.

@@
 The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \textcite{hart2018quantify, XXX}.
+This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify, XXX}.
 

### 2022-03-20 article.rnw
Add a comma for ease of reading.
Fix a double space between two words.
Remove a non-essential sentence.

@@
 With $1$ group, every species is placed in the same group, such that all are equal in their competitive effects or responses, reminiscent of the neutral model.
-Intermediate numbers of groups give more freedom in the groupings, such that there are many possible groupings for any intermediate number of groups. % DBS: Is this sentence essential?
 The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
@@
 With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.
-With the rows grouped, however, this becomes impossible since each species still has an independent growth rate.
+With the rows grouped, however, this becomes impossible, since each species still has an independent growth rate.
 As such, the models were fitted by the Gauss--Newton method for non-linear least squares.

### 2022-03-20 article.rnw
Remove a redundant part of a sentence.
It's in the formal mathematical definition, but it's not really relevant here.

@@
 Each model fit was performed with one grouping of the interaction matrix's rows and a second, independent grouping of the matrix's columns.
-A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group, and such that every group contains at least one species.
+A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group.
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.

### 2022-03-20 article.rnw
Rearrange the methods section of species groupings.
Try to introduce concepts in an order that builds up the idea more readily.
In particular, the idea of the row and column groupings needs careful introduction.

@@
 
-The set of competition coefficients in the Lotka--Volterra model can be arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
-This interpretation was used in the grouping of species, as it was rows or columns of this matrix that were grouped.
-% DBS: Similar to my comment above, I'm not sure the rows vs column groupings is sufficiently introduced to this point.
-So I think we need more than a single sentence explaining this idea.
-Since it appears below, we can reiterate the meaning in terms of equivalence of competitive responses and equivalence of competitive effects.
+In order to reduce the number of free parameters in the model, we grouped species together, and constrained the appropriate competition coefficients to be equal for species within the same group.
 
-Grouping was performed by constraining appropriate competition coefficients to be equal, reducing the number of free parameters in the model.
-Each model fit was performed with one grouping of the interaction matrix's rows and a second, independent grouping of the matrix's columns.
 A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group.
@@
 With $n$ groups, the grouping places each species into its own group, such that all species interact in a unique fashion.
-With $1$ group, every species is placed in the same group, such that all are equal in their competitive effects or responses, reminiscent of the neutral model.
-The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
-With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
+With $1$ group, every species is placed in the same group, such that all are equal in their interactions, reminiscent of the neutral model.
 
-Species in the same column grouping were constrained to have the same competitive effect upon all other species, while species in the same row grouping were constrained to have the same competitive response to all other species.
-Formally, if species $a$ and $b$ were in the same column grouping, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row grouping, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$.
+We did not assume that species should be grouped the same in their competitive effects as in their competitive responses.
+As such, each model was defined by two groupings: a grouping of species constraining equivalence in their competitive effects, and a second, independent grouping of species constraining equivalence in their competitive responses.
+
+The set of competition coefficients in the Lotka--Volterra model can be arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
+As such, if two species are in the same group regarding their competitive responses, then two rows of the interaction matrix are constrained to be equal.
+Similarly, if two species are in the same group regarding their competitive effects, then two columns of the interaction matrix are constrained to be equal.
+This allows us to refer simply to the ``row grouping'' and the ``column grouping''.
+Formally, if species $a$ and $b$ were in the same column group, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row group, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$.
 As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
@@
 
-% DBS: I think my comments at the top of the previous section really boil down to simply reorganizing the pieces in the different paragraphs so that they more clearly build on each other linearly.
+The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
+With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
 

### 2022-03-20 article.rnw
Correct spelling.

@@
 		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the full grouped model, where every pair of species shares a single interaction coefficient.
+		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
 	}

### 2022-03-20 article.rnw
Remove an unnecessary sentence.
Change "I" to "we" to reflect that this is now a two author paper.

@@
 To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogeny or functional groups, and species within a group are assumed to behave identically.
-Herein, I assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to fecundity data from six competing species of \emph{Drosophila} in laboratory conditions.
-I find evidence that grouping can benefit the parsimony of species interaction models, but that there is no single optimal grouping.
+Herein, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to fecundity data from six competing species of \emph{Drosophila} in laboratory conditions.
+We find evidence that grouping can benefit the parsimony of species interaction models, but that there is no single optimal grouping.
 Further, those groupings that did prove beneficial could not be predicted from information available \emph{a priori}, calling the method of \emph{a priori} species grouping into question.
-Lastly, I find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.
+Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.
 
@@
 
-I propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
+We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
 % DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks.
 I can point to some very good references along those lines.
-In this study, I investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
-I fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
-I group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
+In this study, we investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
+We fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
+We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
 
@@
 
-The data I used in this study were drawn from the work of \textcite{terry2021natural}.
+The data we used in this study were drawn from the work of \textcite{terry2021natural}.
 The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
@@
 
-I shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
+We shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
 
@@
 
-The data provided the change population size from one generation to the next, so I used a discrete-time version of the Lotka--Volterra competition model given by:
+The data provided the change population size from one generation to the next, so we used a discrete-time version of the Lotka--Volterra competition model given by:
 \[
@@
 %Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-I assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, I transformed total population growth to \emph{per capita} population growth, which corresponds to the following model:
+We assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, we transformed total population growth to \emph{per capita} population growth, which corresponds to the following model:
 \[
@@
 
-To assess the parsimony of the different species groupings, I exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
-As a measure of parsimony, I selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
+To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
+As a measure of parsimony, we selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
 Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
-As such, I calculated the AIC for each model.
+As such, we calculated the AIC for each model.
 % DBS: Is it possible that the dataset is small enough that we should be using AICc instead?
@@
 AIC values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
-As such, I also converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
+As such, we also converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
 These give the probability that each model is the best among the models assessed.
-All tests were based upon the relationship between the groupings used in a model and the Akaike weight of the model.
-% DBS: I find the last sentence above to be worded a bit cryptically.
 
@@
 The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
-As such, I assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
+As such, we assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
 These results are shown in \cref{fig:coclassification}.
@@
 %In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based on light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
-%Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.
+%Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework we present here to a set of species spanning multiple functional groups.
 % DBS: Prolix warning! ;)
@@
 Since the Allesina paper and its use of AIC was brought up earlier, it strikes me as repetitive to lean on it alone again here.
-Alas, the brute force method I employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
+Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

### 2022-03-20 article.rnw
Explain in the methods the statistics and tests calculated from the Akaike weights.
That is, all the calculations performed before creating the coclassification matrices.

@@
 
+From the Akaike weights, we calculated two important statistics.
+Firstly, the total Akaike weight of models with a lower AIC than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
+Secondly, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
+To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a random equally-sized subset of the models.
+%This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
+%TODO: Is this test superseded by the Mantel test of row vs column coclassification?
+%TODO: Should this test simply be a t-test on the raw AIC values? I think not, as we're interested in the best, rather than the mean.
+
 %TODO: Explain the coclassification matrices and the tests.

### 2022-03-20 article.rnw
Elaborate upon the meaning of the result of the Monte Carlo permutation test on the Akaike weights.
Add a section to the methods on the coclassification matrices and associated tests.

@@
 
-%TODO: Explain the coclassification matrices and the tests.
+\subsubsection{Coclassification matrices}
 
-%TODO: Use Terry et al. table S1 for additional classification information. The two species that coclassify in both columns and rows are substantially larger.
+To summarise the results, the Akaike weights were used to generate coclassification matrices, one for the row groupings and one for the column groupings.
+Each cell of a coclassification matrix represents the coclassification of two species, and contains the total Akaike weight of models that place those two species in the same group.
+As such, each cell represents the probability that the most parsimonious model is one that coclassifies those two species.
+
+There are a number of possible ``null'' expectations for these matrices.
+A neutral model approach would expect all species to be the same: every cell would be $1$.
+If each species were expected to be unique, every off-diagonal cell would be $0$.
+Alternatively, if every possible grouping were considered to be equally likely, every off-diagonal cell would be $\frac{B_{n-1}}{B_n}$: \probnum{\Sexpr{numbers::bell(5)/numbers::bell(6)}} for six species.
+Unfortunately, without a null distribution, it was impossible to test the empirical coclassification matrices against a null expectation.
+
+However, we could test the coclassification matrices against one another.
+By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could test the assumption that it is appropriate to use the same grouping for both.
+We did this using a Mantel test, as appropriate for similarity matrices.
+
+We could also test the coclassification matrices for correlation with an expected dissimilarity matrix.
+We calculated one such dissimilarity matrix based on a species trait: body size (as mean wet mass of female adults, obtained from \cite{terry2021natural}).
+The trait difference matrix was calculated as absolute difference between trait values, while the coclassification matrices were converted to dissimilarity matrices by subtracting from $1$.
+We performed a Mantel test for correlation between the trait distance matrix and each of the two coclassification dissimilarity matrices.
 
@@
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
-% DBS: I think the last sentence above needs a bit of elaboration here OR the usefulness of this "test" should be explained in the Methods in the section that discusses how we examined aspects of parsimony.
+This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
 

### 2022-03-20 article.rnw
Remove some text from the results that is now better addressed in the methods.
Namely, the explanation of the coclassification matrices.

@@
 
+The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
 The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
@@
 
-The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
-As such, we assessed the appropriate groupings by taking the total probability that whichever was the best model grouped a given pair of species together (i.e.\ coclassified the pair of species).
-These results are shown in \cref{fig:coclassification}.
-% DBS: Much of the paragraph above is probably more appropriate at Methods text whereas in the Results we should discuss the patterns that emerge from the co-classification matrices.
-
+Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
 In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.

### 2022-03-20 article.rnw
Remove a note about null coclassification expectation that is now addressed in the methods.
Add the Mantel tests to the results.

@@
 \newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
+\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}
+
+\newcommand\mantelstat{\ensuremath{r_{\text{M}}}}
 
@@
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
-% DBS: As I have noted before, I'd like to know what the null expectation is for this before claiming confidence of being co-classified or not being co-classified.
-Firstly, I think that the random expectation is much lower than one might otherwise suspect.
-(For three species, it is already 2/5; for four species, it is 5/15.) Second, the conventional "ecological" null is actually that the probability is 0, in which case it doesn't take much co-classification probability to see the glass as half full and argue that grouping is a much more parsimonious approach than the contrary.
 
@@
 Overall, more coclassification occurred in the row groupings than in the column groupings.
-% DBS: In the network modularity literature, there is a nice measure of mutual information between two partitions.
-I wonder if we could exploit that here to give a quantitative measure of similarity between the two.
-Or we could just convert the two matrices to distance matrices and run a Procrustes to measure their similarity?
+A Mantel test of the coclassification matrix for the rows against that for the columns shows that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
 
@@
 simulans}.
+
+Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
 

### 2022-03-20 article.rnw
Add a possible TODO to the introduction.
Add a sentence to reiterate the overall premise at the beginning of the discussion.
Make the first paragraph of the discussion less pessimistic.

@@
 We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
+%TODO: Mention the comparison to traits (body size)?
 
@@
 
-% DBS: I would start this paragraph with a restatement of the overall premise.
-The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped, but not confidently so.
-Which grouping might give the most parsimonious model also could not be determined with any confidence.
-% DBS: The two preceding sentences are very glass half empty. I'm also not sure that the results are really so equivocal. What makes you feel this way?
+We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
+Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
+Which grouping would give the most parsimonious model, however, could not be determined with confidence.
 The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.

### 2022-03-21 article.rnw
Change the inspecific subjecct "this" to "this result".

@@
 % DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
-This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
+This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.

### 2022-03-21 article.rnw
Rewrite the part of the discussion around phylogeny, so it stands with the phylogenetic results removed.
Remove the commented out part about phylogeny, as that's now done with.

@@
 
-%TODO: Discuss the potential to study a system with functional groups without brining up phylogeny.
-%I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species' phylogenetic relationships.
-%Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
-%A study system with species spanning multiple functional groups, however, might have shown clearer groupings.
-%While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
-%In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based on light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonomically (with both groupings defined \emph{a priori}).
-%Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework we present here to a set of species spanning multiple functional groups.
-% DBS: Prolix warning! ;)
-
-Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
-% DBS: Personally, I try to make links to previous studies more self contained.
-Since the Allesina paper and its use of AIC was brought up earlier, it strikes me as repetitive to lean on it alone again here.
+All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
+A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
+Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
 Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.

### 2022-03-21 article.rnw
Move the part about intransitivity in the discussion to its own paragraph.
Use this to suggest future approaches: Bayesian or mixed membership.

@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-% DBS: In my mind, I would steal the preceding sentence and spin it potentially spin it into its own paragraph later since it speaks strongly to a mixed-membership approach which could be sold as a "future direction".
 
@@
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
+
+The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+This could suggest a Bayesian approach, in which the outcome is not a definitive grouping, but a distribution of valid groupings.
+Alternatively, it may suggest a mixed membership approach in which a species can be a partial part of more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
 

### 2022-03-21 article.rnw
Collapse the first two paragraphs of the discussion into one.
They tie together too tightly to be separate paragraphs.
Change a TODO to merely a possible TODO.
Simplify an overly wordy paragraph.

@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-
-% DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
 This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
@@
 
-% DBS: The paragraph below is a very good example of text that could easily be simplified for clarity without losing important content.
-In light of the failure to produce clear groups, perhaps the most curious aspect of the results is the disagreement between the likely coclassifications of species in the groupings of rows and of columns.
-This is perhaps not surprising in hindsight, for there is no necessity that species respond to competition in the same manner that they cause it, especially in competition for certain resources such as space (the limiting resource presumed in these data) or light.
-% DBS: Some definite refs missing here.
+While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
+That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
+This should not be surprising, for it is known that different traits govern species competitive effects than their responses \parencite{goldberg1991competitive}.
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
 My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
-%TODO: Discuss the fact that species were coclassified more in the rows than in the columns.
+%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
 

### 2022-03-21 article.rnw
Change "my" to "our" to reflect that this is now a two author paper.
Point out a potential problem with the many-zeroes simplification, to justify the grouping approach.

@@
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-%TODO: XXX why this could be a problem XXX.
-Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{wootton2016many}, and setting these to zero may lose important information.
+Another approach assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
 
@@
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
-My results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
+Our results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
 %TODO: Discuss the fact that species were coclassified more in the rows than in the columns?

### 2022-03-21 article.rnw
Correct spelling.

@@
 
-Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how spcies respond to others \parencite{XXX}.
+Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.

### 2022-03-21 src/mlsolver.cpp
Add MaximumLikelihoodSolver::getAICc().

@@ -109,6 +109,17 @@ double MaximumLikelihoodSolver::getAIC() {
 	return aic;
 }
 
+double MaximumLikelihoodSolver::getAICc() {
+	Parameters parameters = getSolution();
+	double n = data.getNumObservations();
+	double p = parameters.getNumParameters();
+	
+	double aic = getAIC();
+	double aicc = aic + (double)(2 * p * p + 2 * p) / (n - p - 1);
+	
+	return aicc;
+}
+
 double MaximumLikelihoodSolver::getR2() {
 	//Returns R^2, the coefficient of determination.
 	

### 2022-03-21 src/mlsolver.hpp

@@ -59,6 +59,7 @@ class MaximumLikelihoodSolver : public Solver {
 		Eigen::VectorXd getSolutionResiduals();
 		double getDeviance();
 		double getAIC();
+		double getAICc();
 		double getR2();
 };
 

### 2022-03-21 src/brute.cpp
Add AICc to the output of the C++ program.

@@ -10,6 +10,7 @@ int main(int argc, char **argv) {
 	OutputColumn<Grouping> outputRowGroupings("row_group");
 	OutputColumn<Grouping> outputColGroupings("col_group");
 	OutputColumn<double> outputAICs("aic");
+	OutputColumn<double> outputAICcs("aicc");
 	OutputColumn<double> outputR2s("R2");
 	OutputColumn<Parameters> outputParameters("parameters");
 	
@@ -18,12 +19,13 @@ int main(int argc, char **argv) {
 			outputRowGroupings.insert(solver.getGrouping(ROW));
 			outputColGroupings.insert(solver.getGrouping(COL));
 			outputAICs.insert(solver.getAIC());
+			outputAICcs.insert(solver.getAICc());
 			outputR2s.insert(solver.getR2());
 			outputParameters.insert(solver.getSolution());
 		} while(solver.updateGrouping(ROW, &Grouping::advance));
 	} while(solver.updateGrouping(COL, &Grouping::advance));
 	
-	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters, outputAICs, outputR2s);
+	outputTable(input.getOutputFile(), outputRowGroupings, outputColGroupings, outputParameters, outputAICs, outputAICcs, outputR2s);
 	
 	return 0;
 }

### 2022-03-21 r/post-process.R
Adapt the post-process module to also convert AICc values to Akaike weights.

@@ -43,6 +43,7 @@ Data <- R6::R6Class("Data",
 			
 			#Add additional columns of statistics.
 			if(!is.null(self$statistics$aic)) private$add_aic_weights()
+			if(!is.null(self$statistics$aicc)) private$add_aicc_weights()
 		}
 	),
 	
@@ -59,6 +60,10 @@ Data <- R6::R6Class("Data",
 		
 		add_aic_weights = function() {
 			self$statistics$aic_weight <- information_criterion_weights(self$statistics$aic)
+		},
+		
+		add_aicc_weights = function() {
+			self$statistics$aicc_weight <- information_criterion_weights(self$statistics$aicc)
 		},
 		
 		match_grouping = function(desired_grouping, grouping_table) {

### 2022-03-21 r/brute-post-process.R
Adapt the brute-post-process module to choose between AIC and AICc on initialisation.

@@ -22,26 +22,35 @@ prob_perm_test <- function(selected_probs, all_probs, num_iter = 1000) {
 BruteData <- R6::R6Class("BruteData",
 	inherit = Data,
 	
+	public = list(
+		weight_column = NULL, #The name of the column to use for weights.
+		
+		initialize = function(data_file_name, species_names, weight_column = c("aic_weight", "aicc_weight")) {
+			super$initialize(data_file_name, species_names)
+			self$weight_column <- match.arg(weight_column)
+		}
+	),
+	
 	active = list(
 		unweighted_average_coclassification_matrix = function() {
 			return(private$annotate_matrix(private$get_average_coclassification_matrix(self$row_groupings)))
 		},
 		weighted_row_coclassification_matrix = function() {
-			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$row_groupings, self$statistics$aic_weight)))
+			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$row_groupings, self$statistics[[self$weight_column]])))
 		},
 		weighted_col_coclassification_matrix = function() {
-			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$col_groupings, self$statistics$aic_weight)))
+			return(private$annotate_matrix(private$get_weighted_coclassification_matrix(self$col_groupings, self$statistics[[self$weight_column]])))
 		},
 		
 		equivalently_grouped_weight = function() {
-			return(sum(self$equivalently_grouped_statistics$aic_weight))
+			return(sum(self$equivalently_grouped_statistics[[self$weight_column]]))
 		},
 		equivalently_grouped_expected_weight = function() {
 			return(nrow(self$equivalently_grouped_statistics) / nrow(self$statistics))
 		},
 		equivalently_grouped_weight_p = function() {
 			#p value of a permutation test
-			return(prob_perm_test(self$equivalently_grouped_statistics$aic_weight, self$statistics$aic_weight))
+			return(prob_perm_test(self$equivalently_grouped_statistics[[self$weight_column]], self$statistics[[self$weight_column]]))
 		}
 	)
 )

### 2022-03-21 article.rnw
Remove phylogeny as a keyword, now that we are no longer discussing it.
Adapt article.rnw to switch between AIC and AICc on a single variable change.

@@
 
-	brute_data <- BruteData$new("output/brute.data", species_dat$name)
+	ic <- "aic" #The information criterion to use, e.g. "aic" or "aicc"
+	ic_weight <- sprintf("%s_weight", ic)
+
+	brute_data <- BruteData$new("output/brute.data", species_dat$name, ic_weight)
 
@@
 
-\keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony; phylogeny}
+\keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony}
 
@@
 The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
-The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$statistics$aic)}}.
-The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}.
+The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
+The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
 \Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
@@
 	<<echo=FALSE>>=
-		hist(brute_data$statistics$aic,
+		hist(brute_data$statistics[[ic]],
 			main="",
@@
 		)
-		abline(v = brute_data$fully_separated_statistics$aic, lwd=2, lty="dashed", col="green")
-		abline(v = brute_data$fully_grouped_statistics$aic, lwd=2, lty="dashed", col="red")
+		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
+		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dashed", col="red")
 	@
@@
 		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
-		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics$aic}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics$aic}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
+		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
+		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
 	}
@@
 
-The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics$aic_weight)}} that it was the best.
-The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
+The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
+The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
 
-Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
+Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
@@
 We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
-Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
+Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}) than leaving them ungrouped.
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.

### 2022-03-21 article.rnw
Remove an extraneous comma.

@@
 Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
-In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
+In all, no pair of species can confidently be said to be coclassified in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

### 2022-03-21 article.rnw
Automate the highest probability of coclassification in the results.

@@
 Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
-In all, no pair of species can confidently be said to be coclassified in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
+In all, no pair of species can confidently be said to be coclassified in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(brute_data$num_species), weighted_row_coclassification_matrix - diag(brute_data$num_species))*100}}{\percent}.
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

### 2022-03-21 article.rnw
Change \aicnum to \icnum to reflect that it may now be a different information criterion.

@@
 \newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
-\newcommand\aicnum[1]{\num{#1}}
+\newcommand\icnum[1]{\num{#1}} %For information criteria.
 \newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
@@
 The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
-The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
-The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
+The AIC values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
+The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
 \Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
@@
 		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
-		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
+		The green line shows the AIC value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
+		The red line shows the AIC value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
 	}
@@
 
-Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
+Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).

### 2022-03-21 article.rnw
Change the fig:aic label to fig:ic.
To reflect that it may use other information criteria.
Correct "AIC weights" to "Akaike weights".
This will be especially if they are calculated from AICc instead of AIC.

@@
 The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
-\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.
+\Cref{fig:ic} shows the distribution of AIC values from the models, with some models of interest marked.
 
@@
 	}
-	\label{fig:aic}
+	\label{fig:ic}
 \end{figure}
@@
 	\caption{%
-		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
-		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
+		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by Akaike weights.
+		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
 		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).

### 2022-03-21 article.rnw
Replace "AIC" in article.rnw with a macro that gives the appropriate information criterion.

@@
 	ic_weight <- sprintf("%s_weight", ic)
+	ic_name <- list(aic="AIC", aicc="AICc")[ic]
 
@@
 @
+
+\newcommand\ic{\Sexpr{ic_name}}
 
@@
 Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
-As such, we calculated the AIC for each model.
+As such, we calculated the {\ic} for each model.
 % DBS: Is it possible that the dataset is small enough that we should be using AICc instead?
 
-AIC values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
-As such, we also converted the set of AIC values to Akaike weights \parencite{wagenmakers2004aic}.
+{\ic} values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
+As such, we also converted the set of {\ic} values to Akaike weights \parencite{wagenmakers2004aic}.
 These give the probability that each model is the best among the models assessed.
@@
 From the Akaike weights, we calculated two important statistics.
-Firstly, the total Akaike weight of models with a lower AIC than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
+Firstly, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
 Secondly, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
@@
 The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
-The AIC values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
-The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
-\Cref{fig:ic} shows the distribution of AIC values from the models, with some models of interest marked.
+The {\ic} values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
+The ungrouped model gave an {\ic} value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
+\Cref{fig:ic} shows the distribution of {\ic} values from the models, with some models of interest marked.
 
@@
 			main="",
-			xlab="AIC",
+			xlab=ic_name,
 			xaxs='i',
@@
 	\caption{%
-		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
-		The green line shows the AIC value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the AIC value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
+		A histogram of the {\ic} values of species interaction models with all possible groupings of interaction coefficients.
+		The green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
+		The red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
 	}
@@
 
-The ``best'' model, as indicated by AIC, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
+The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
 The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
 
-Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
+Considering only models in which the rows and columns were grouped using the same grouping, the {\ic} values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).

### 2022-03-21 article.rnw
Correct a comment in article.rnw to reflect the use of a generic information criterion.
Add and use num_species to article.rnw.
This saves having to use brute_data$num_species every time.

@@
 	species_output_order <- c(4,3,1,2,6,5)
+
+	num_species <- nrow(species_dat)
 
@@
 %TODO: Is this test superseded by the Mantel test of row vs column coclassification?
-%TODO: Should this test simply be a t-test on the raw AIC values? I think not, as we're interested in the best, rather than the mean.
+%TODO: Should this test simply be a t-test on the raw information criterion values? I think not, as we're interested in the best, rather than the mean.
 
@@
 Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
-In all, no pair of species can confidently be said to be coclassified in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(brute_data$num_species), weighted_row_coclassification_matrix - diag(brute_data$num_species))*100}}{\percent}.
+In all, no pair of species can confidently be said to be coclassified in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent}.
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

### 2022-03-21 article.rnw
Add a num_obs variable to article.rnw.
Switch to using AICc instead of AIC.

@@
 	num_species <- nrow(species_dat)
+	num_obs <- nrow(read.table("output/design-matrix.data"))
 
-	ic <- "aic" #The information criterion to use, e.g. "aic" or "aicc"
+	ic <- "aicc" #The information criterion to use, e.g. "aic" or "aicc"
 	ic_weight <- sprintf("%s_weight", ic)
@@
 Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
+Some of the models had a relatively high number of parameters compared to the number of observations (\num{\Sexpr{num_obs}} observations; up to \num{\Sexpr{num_species + num_species^2}} parameters), so we used AICc to correct for this.
 As such, we calculated the {\ic} for each model.
-% DBS: Is it possible that the dataset is small enough that we should be using AICc instead?
 

### 2022-03-30 r/grouped-matrix.R
Add the grouped-matrix R module, for printing grouped alpha matrices.

@@ -1,0 +1,4 @@
+#A function for printing a grouped alpha matrix as a table using knitr.
+#Expects the species names, the row grouping, the column grouping, and the alpha matrix.
+#The groupings are given as a vector, [number of species] in length, with the number of the group each species belongs to.
+#The matrix is defined in terms of the groups, and hence is [number of row groups] by [number of column groups].

### 2022-03-30 r/grouped-matrix.R
Add a helper function for the grouped matrix module to check if a grouping is in a suitable order.

@@ -2,3 +2,16 @@
 #Expects the species names, the row grouping, the column grouping, and the alpha matrix.
 #The groupings are given as a vector, [number of species] in length, with the number of the group each species belongs to.
 #The matrix is defined in terms of the groups, and hence is [number of row groups] by [number of column groups].
+
+#First, we need to determine an ordering of the species such that all species that are grouped together are adjacent in all groupings.
+#In the absence of an elegant method, I'll do this by an exhaustive search of orderings.
+#An ordering is given as a vector of integers: a permutation of the original order.
+#Using R's subsetting, species can be reordered according to an ordering using species_names[ordering].
+#First, a helper function, to check if a grouping is in consecutive blocks.
+is_consecutive_blocks <- function(grouping) {
+	for(group in unique(grouping)) {
+		indices <- (1:length(grouping))[grouping == group]
+		if(!all((grouping == group)[min(indices):max(indices)])) return(FALSE)
+	}
+	return(TRUE)
+}

### 2022-03-30 r/grouped-matrix.R
Rewrite is_consecutive_blocks to be faster and hopefully clearer.
The code for the previous version was obtuse, and quite slow.
This code is longer, but faster, and hopefully less obtuse in how it works.

@@ -9,9 +9,14 @@
 #Using R's subsetting, species can be reordered according to an ordering using species_names[ordering].
 #First, a helper function, to check if a grouping is in consecutive blocks.
 is_consecutive_blocks <- function(grouping) {
-	for(group in unique(grouping)) {
-		indices <- (1:length(grouping))[grouping == group]
-		if(!all((grouping == group)[min(indices):max(indices)])) return(FALSE)
+	current_group <- grouping[1]
+	completed_groups <- c()
+	for(g in grouping[-1]) {
+		if(g != current_group) {
+			if(g %in% completed_groups) return(FALSE)
+			completed_groups <- c(completed_groups, current_group)
+			current_group <- g
+		}
 	}
 	return(TRUE)
 }

### 2022-03-31 r/grouped-matrix.R
Add a helper function for the grouped matrix module to generate all orderings.

@@ -20,3 +20,14 @@ is_consecutive_blocks <- function(grouping) {
 	}
 	return(TRUE)
 }
+#Second, another helper function to get a list of all orderings.
+#In C++, to make use of std::next_permutation().
+Rcpp::cppFunction("List get_all_orderings(int n) {
+	List all_orderings = List::create();
+	std::vector<int> ordering(n);
+	for(int i = 0; i < n; i++) ordering[i] = i+1;
+	do {
+		all_orderings.push_back(NumericVector::import(ordering.begin(), ordering.end()));
+	} while(std::next_permutation(ordering.begin(), ordering.end()));
+	return all_orderings;
+}")

### 2022-03-31 article.rnw
Remove some potential TODOs regarding the permutation test for equivalently grouped rows and columns.
After discussion with Daniel, we've decided that the current test works fine.
There's no need to change it.
But it's useful, so it shouldn't be removed either.
Fix an incorrect subsetting that was causing an error in the histogram.
I was subsetting a list with [], not [[]].
dbs edits to and comments on the manuscript

@@
 \usepackage{setspace} \doublespacing
-\usepackage[nomarkers,tablesfirst,notablist]{endfloat}
+\usepackage[nomarkers,tablesfirst,notablist,nofiglist]{endfloat}
 \addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.
@@
 %Title Page
+% DBS: What about "Simplifying Lotka--Volterra interaction matrices by species grouping", with or without the bit after the colon (and where I lean slightly in favor of the "with" option)
 \title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable} %TODO: Remove the word "regularising" from the title.
@@
 	ic_weight <- sprintf("%s_weight", ic)
-	ic_name <- list(aic="AIC", aicc="AICc")[ic]
+	ic_name <- list(aic="AIC", aicc="AICc")[[ic]]
 
@@
 
-% DBS: I'll leave the abstract free of comments until the main text is closer to the final version.
-
 \section*{Abstract}
 
-Dynamic models of ecological communities require many parameters, making them expensive to fit.
-To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogeny or functional groups, and species within a group are assumed to behave identically.
-Herein, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to fecundity data from six competing species of \emph{Drosophila} in laboratory conditions.
-We find evidence that grouping can benefit the parsimony of species interaction models, but that there is no single optimal grouping.
-Further, those groupings that did prove beneficial could not be predicted from information available \emph{a priori}, calling the method of \emph{a priori} species grouping into question.
-Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating an assumption often made implicitly when defining species groupings.
+Dynamic models of ecological communities require many parameters, making them expensive to fit to experimental or observational data.
+To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogenetic or functional groups, and species within a group are assumed to behave identically.
+Here, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to experimental data from six species of \emph{Drosophila} competing in laboratory conditions.
+We find evidence that grouping can improve the parsimony of species interaction models, but we also observe that there is no single optimal grouping.
+Further, those groupings that did prove beneficial could not be easily predicted from available species attributes \emph{a priori}, calling into question the prevailing method of \emph{a priori} species grouping.
+Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating a key assumption often made implicitly when defining species groupings.
+% DBS: add some sort of concluding sentence a la where to from here
 
+% DBS: Once we have a title, make sure that we remove all words from the keywords that appear there.
 \keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony}
@@
 Models have long been used in community ecology \parencite{lotka1925elements}.
-They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing}, or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
+They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
 The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{XXX}.
@@
 Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
+% DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
 Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
 Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
-This is expensive, and requires a lot of effort.
+This is understandably expensive and requires substantial effort.
 As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
 However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
-To bridge this gap between the size of real communities and our ability to parameterise them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
+To bridge this gap between the size of real communities and our ability to parameterise models for them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
 
@@
 However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{wootton2016many}, and setting these to zero may lose important information.
-Another approach assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
+Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
 
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
+% please add a reference to http://dx.doi.org/10.1086/713082 to the above
 The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
@@
 
-Additionally, studies that use grouping to simplify models of species interactions have always made one untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
+To the best of our knowledge, studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
+% DBS: Maybe it's worth adding a concrete example here for the more empirical reader/reviewer.
 As such, the best groupings of species may be different for each of the effects and responses.
@@
 I can point to some very good references along those lines.
-In this study, we investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
-We fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
-We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
+In this study, we investigate the usefulness and correctness of such an approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
+We fit the Lotka--Volterra model to find the groupings that give the most parsimonious model.
+While doing so, we group species independently with regard to their effects upon other species and their responses to other species, to find whether the data-informed groupings differ between these two cases.
 %TODO: Mention the comparison to traits (body size)?
+% DBS: If we leave in the traits, then we should mention them at least briefly.
 
@@
 
-We shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
+%We shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
+% DBS: I don't think we need the above because we say the same thing in line 172 below.
 
@@
 A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
-The number of adult pairs of each species emerging from these eggs was counted---this was the size of the next generation.
+The number of adult pairs of each species emerging from these eggs was counted.
+%---this was the size of the next generation.
+% DBS: Do we need the bit I've commented out above? Plus, it isn't the size of the next generation it's the number of new adults...
 
 Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
-The single-species densities were 3, 9, or 12 pairs per vial, each replicated six times per species.
-The two-species densities were, giving the densities of each of the two species, (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial, each replicated three times per pair of species.
+The single-species densities were 3, 9, or 12 pairs per vial, and each of these was replicated six times per species.
+The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
 Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
-
+ %
 Further details of the experimental methodology can be found in \textcite{terry2021natural}.
@@
 
-The data provided the change population size from one generation to the next, so we used a discrete-time version of the Lotka--Volterra competition model given by:
-\[
-	N_{i,t+1} - N_{i,t} = N_{i,t} r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
-,\]
-where $N_{i,t}$ is the population of species $i$ at time $t$ (the size of the parent generation), $N_{i,t+1}$ is the population at time $t+1$ (the size of the offspring generation), $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the \emph{per capita} competitive effect of species $j$ on species $i$.
+The data provided the change in population size from one generation to the next, so we used a discrete-time version of the Lotka--Volterra competition model given by:
+\begin{equation}
+	N_{i,t+1} - N_{i,t} = N_{i,t} \, r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right) \,,
+	\label{LVmodel}
+\end{equation}
+where $N_{i,t}$ is the population of species $i$ at time $t$ (the size of the parent generation), $N_{i,t+1}$ is the population at time $t+1$ (the size of the offspring generation), $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the per capita effect of species $j$ on species $i$.
 The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.
+
+% DBS: Let's add something that very briefly outlines how many parameters this model has.
+Then, below, we can provide formulae for the number of parameters given the number of row and column groups.
+Even though people can work this out themselves, it is probably useful to make it explicit so that we don't have to depend on them actually mustering up the energy to do so.
 
@@
 \subsubsection{Species grouping}
+
+% DBS: I still feel like the bits and pieces of the section below are not in a well-flowing order.
 
@@
 
-The Lotka--Volterra model is not linear in the parameters.
+The Lotka--Volterra competition model in Eq.~(\ref{LVmodel}) is not linear in the parameters.
 With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.
-With the rows grouped, however, this becomes impossible, since each species still has an independent growth rate.
-As such, the models were fitted by the Gauss--Newton method for non-linear least squares.
+With the rows grouped, however, this becomes impossible since each species still has an independent growth rate.
+As such, we instead fit the models with the Gauss--Newton method for non-linear least squares and assumed a normal error distribution of the response variable.
 %The models were fitted to the data using maximum likelihood regression techniques.
 %Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
-We assumed a normal error distribution of the response variable and to prevent heteroskedasticity and improve normality, we transformed total population growth to \emph{per capita} population growth, which corresponds to the following model:
-\[
-	\frac{N_{i,t+1} - N_{i,t}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right)
-.\]
+To prevent heteroskedasticity and improve normality, we transformed total population growth to per capita population growth, which corresponds to the following model:
+\begin{equation}
+	\frac{N_{i,t+1} - N_{i,t}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right) \,.
+\end{equation}
 
@@
 
-To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models.
-As a measure of parsimony, we selected AIC over BIC on the basis that we want to find the best model for making ecological predictions, rather than seeking the ``true'' model \parencite{aho2014model}.
-Further, AIC is more conservative in promoting grouping, as BIC penalises number of parameters more for any reasonably sized data set.
-Some of the models had a relatively high number of parameters compared to the number of observations (\num{\Sexpr{num_obs}} observations; up to \num{\Sexpr{num_species + num_species^2}} parameters), so we used AICc to correct for this.
-As such, we calculated the {\ic} for each model.
-
-{\ic} values can be compared to determine which model is the most parsimonious, but cannot directly be interpreted to find the significance of the difference in parsimony.
+To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models and computed the resulting {\ic} for those fits.
+As a measure of parsimony, we selected AICc over BIC on the basis that we want to find the best model for making ecological predictions rather than seeking the ``true'' model \parencite{aho2014model}.
+Furthermore, AICc is more conservative in promoting grouping as BIC imposes a greater penalty for the number of parameters for any reasonably sized data set.
+Some of the models had a relatively high number of parameters compared to the number of observations (\num{\Sexpr{num_obs}} observations compared to up to \num{\Sexpr{num_species + num_species^2}} parameters), so we used AICc to correct for this ``small sample size'' effect.
+{\ic} values can be compared to determine which model is the most parsimonious, but they cannot directly be interpreted to find the significance of the difference in parsimony.
 As such, we also converted the set of {\ic} values to Akaike weights \parencite{wagenmakers2004aic}.
@@
 
-From the Akaike weights, we calculated two important statistics.
-Firstly, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
-Secondly, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
-To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a random equally-sized subset of the models.
+Using these Akaike weights, we calculated two important statistics.
+First, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the fully ungrouped model.
+Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
+To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
 %This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
-%TODO: Is this test superseded by the Mantel test of row vs column coclassification?
-%TODO: Should this test simply be a t-test on the raw information criterion values? I think not, as we're interested in the best, rather than the mean.
 
@@
 
-To summarise the results, the Akaike weights were used to generate coclassification matrices, one for the row groupings and one for the column groupings.
-Each cell of a coclassification matrix represents the coclassification of two species, and contains the total Akaike weight of models that place those two species in the same group.
+To summarise the results, we also used the Akaike weights to generate two coclassification matrices, one for the row groupings and one for the column groupings.
+Each cell of a coclassification matrix represents the coclassification of a pair of species, and contains the total Akaike weight of models that place those two species in the same group.
 As such, each cell represents the probability that the most parsimonious model is one that coclassifies those two species.
+For reference, note that the diagonal of a coclassification matrix is tautologically equal to $1$.
 
-There are a number of possible ``null'' expectations for these matrices.
-A neutral model approach would expect all species to be the same: every cell would be $1$.
-If each species were expected to be unique, every off-diagonal cell would be $0$.
+There are a number of possible ``null'' expectations for the off-diagonal elements these matrices.
+A neutral model approach would expect all species to be in the same group: every off-diagonal cell would therefore be $1$.
+If each species were expected to be unique, every off-diagonal cell would instead be $0$.
 Alternatively, if every possible grouping were considered to be equally likely, every off-diagonal cell would be $\frac{B_{n-1}}{B_n}$: \probnum{\Sexpr{numbers::bell(5)/numbers::bell(6)}} for six species.
-Unfortunately, without a null distribution, it was impossible to test the empirical coclassification matrices against a null expectation.
+Unfortunately, without a null \emph{distribution} of coclassification matrices, it was impossible to test the data-informed coclassification matrices against a null expectation.
 
-However, we could test the coclassification matrices against one another.
-By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could test the assumption that it is appropriate to use the same grouping for both.
+However, we could test the row-grouping and column-grouping coclassification matrices against one another.
+By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could perform a different test regarding the assumption that it is appropriate to use the same grouping for both.
 We did this using a Mantel test, as appropriate for similarity matrices.
-
+ %
 We could also test the coclassification matrices for correlation with an expected dissimilarity matrix.
 We calculated one such dissimilarity matrix based on a species trait: body size (as mean wet mass of female adults, obtained from \cite{terry2021natural}).
-The trait difference matrix was calculated as absolute difference between trait values, while the coclassification matrices were converted to dissimilarity matrices by subtracting from $1$.
-We performed a Mantel test for correlation between the trait distance matrix and each of the two coclassification dissimilarity matrices.
+The trait difference matrix was calculated as absolute difference between trait values, while the coclassification matrices were converted to dissimilarity matrices by subtracting them from $1$.
+We then performed Mantel tests for correlation between the trait distance matrix and each of the two coclassification dissimilarity matrices.
 
 \section{Results}
+
+% DBS: Should we add a figure that shows the fit of observed vs predicted? Are we forgetting how much that might resonate with readers and jumping ahead too quickly?
+
+% DBS: Semi-random thought: should we also add the "all alphas = 0" model to the mix?
 
@@
 The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
-The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
+Despite it being just over $7$ {\ic} units from the most parsimonious model, the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
 
 Considering only models in which the rows and columns were grouped using the same grouping, the {\ic} values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
-The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
+The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; this was more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
 This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
@@
 Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
-In all, no pair of species can confidently be said to be coclassified in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent}.
+% DBS: In general, I am more in favor of just putting something like a pointer to a figure "(Fig.~1)" at the end of the sentence below than an explicit statement of what appears in a figure.
+Some journals also frown on devoting words to explanations of what appears in figures since that is technically what figure captions are for.
+Overall, no pair of species can confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent}.
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
@@
 
-A relatively high likelihood of coclassification in the row groupings was typically transitive: e.g.\ \emph{D.
+A relatively high likelihood of coclassification in the row groupings was typically transitive: for example, \emph{D.
 birchii}, \emph{D.
@@
 Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
+
+% DBS: Most journals frown upon or do not allow overly verbose subtitles on figures. So I've cut them down to be a bit more concise.
+% DBS: But the fact that the labels say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
+We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects.
+As long as we're consistent, I'm fine either way.
+But we need to remember we're writing the paper for the audience and not for ourselves.
+;)
 
@@
 		@
-		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
+		\caption{Coclassification of competitive effects}
 		\label{fig:coclassification-cols}
@@
 		@
-		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
+		\caption{Coclassification of competitive responses}
 		\label{fig:coclassification-rows}
@@
 
+% DBS: Within the caption, the reference to a subfigure should just be (a) and (b), not Figure 2a and fig. 2b.
+
 % DBS: I think a good figure would be to show the ungrouped estimated alpha matrix in one panel and the alpha matrix averaged across all partitions in a second panel, with lines drawn in the second to reflect the "optimal" partitioning of the co-classification matrices.
@@
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
-Perhaps species simply do not group to the same extent in a competitive context.
-The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
-Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
-Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.
+% DBS: We're probably doing a disservice to the "groups in ecological communities" literature by only citing the Allesina paper above.
 
+One possible explanation is that species simply do not group to the same extent in a competitive context.
+That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
+Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
+In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
 All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
@@
 Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
+%DBS: Add in the number of models for both of these to emphasize the point.
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
 
+% DBS: I think we should swap the order of the following two paragraphs.
+
 The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-This could suggest a Bayesian approach, in which the outcome is not a definitive grouping, but a distribution of valid groupings.
-Alternatively, it may suggest a mixed membership approach in which a species can be a partial part of more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
+A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
+This could suggest a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
+Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
 
@@
 
+% DBS: Never shoot yourself in the foot in your concluding paragraph! The reviewers will already be primed to do this for you, so I always think it's better to take a glass half full perspective.
+% DBS: Also, there is no hard and fast rule to say we need a "sum it all up" concluding paragraph.
+Each of the statements below is pretty much already stated above but with more depth.
+I think we could actually do away with it and lose very little.
 All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely related set of species.

### 2022-03-31 article.rnw
orphaned edits
adding reminders in a few places where I think we should add more references

@@
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{wootton2016many}, and setting these to zero may lose important information.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{XXX, wootton2016many}, and setting these to zero may lose important information.
 Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
@@
 % please add a reference to http://dx.doi.org/10.1086/713082 to the above
-The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
+The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
-On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
+On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX, bret2008plant}.
 While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
@@
 In this study, we investigate the usefulness and correctness of such an approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
-We fit the Lotka--Volterra model to find the groupings that give the most parsimonious model.
+We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model.
 While doing so, we group species independently with regard to their effects upon other species and their responses to other species, to find whether the data-informed groupings differ between these two cases.
@@
 	\caption{%
-		A histogram of the {\ic} values of species interaction models with all possible groupings of interaction coefficients.
+		Histogram of the {\ic} values of Lotka--Volterra model fit with all possible groupings of interaction coefficients.
 		The green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
+This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{XXX, blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{XXX, godoy2014phylogenetic}.
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.

### 2022-03-31 r/grouped-matrix.R
Define a wrapper function around is_consecutive_blocks that reorders a grouping using an ordering.

@@ -20,7 +20,11 @@ is_consecutive_blocks <- function(grouping) {
 	}
 	return(TRUE)
 }
-#Second, another helper function to get a list of all orderings.
+#Second, a wrapper around is_consecutive_blocks that takes the base ordering and a grouping.
+forms_consecutive_blocks <- function(grouping, ordering) {
+	is_consecutive_blocks(grouping[ordering])
+}
+#Third, another helper function to get a list of all orderings.
 #In C++, to make use of std::next_permutation().
 Rcpp::cppFunction("List get_all_orderings(int n) {
 	List all_orderings = List::create();

### 2022-04-11 r/input-data.R
Add an input-data R module, to handle the raw data that was fed to the C++ program.

@@ -1,0 +1,22 @@
+#An R6 object to read, store and handle the raw data that was fed into the C++ program.
+#Requires the three data files that were provided to the C++ object:
+#the focal vector, the response vector, and the design matrix.
+
+InputData <- R6::R6Class("InputData",
+	public = list(
+		focal_vector = NULL,
+		response_vector = NULL,
+		design_matrix = NULL,
+		num_species = NULL,
+		num_obs = NULL,
+		
+		initialize = function(focal_vector_file_name, response_vector_file_name, design_matrix_file_name) {
+			self$focal_vector <- read.table(focal_vector_file_name)[[1]]
+			self$response_vector <- read.table(response_vector_file_name)[[1]]
+			self$design_matrix <- as.matrix(read.table(design_matrix_file_name))
+			
+			self$num_species <- ncol(self$design_matrix)
+			self$num_obs <- nrow(self$design_matrix)
+		}
+	)
+)

### 2022-04-11 article.rnw
Use the input-data module to read the input data in the rnw file.

--- 2022-03-21 article.rnw
@@
 <<include=FALSE>>=
+	source("r/input-data.R")
 	source("r/post-process.R")
@@
 
+	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data")
+
 	num_species <- nrow(species_dat)
@@
 %This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
-%TODO: Is this test superseded by the Mantel test of row vs column coclassification?
-%TODO: Should this test simply be a t-test on the raw information criterion values? I think not, as we're interested in the best, rather than the mean.
 

### 2022-04-11 src/input.cpp
Fix the description of the reponse variable in the usage spiel for the C++ program.
It did not account for the change to the meaning of the response variable
in a4a686f7416a2e9fd2a3de31addab8d3e4604b6f.

@@ -23,7 +23,7 @@ static void printUsage(int argc, const char **argv) {
 		
 		"\t-p\n"
 		"\t\tResponse variables are per capita growth/fecundity.\n"
-		"\t\tOtherwise, the response is assumed to be a measure of the total size of the next generation.\n"
+		"\t\tOtherwise, the response is assumed to be a measure of the total change in population size from one generation to the next.\n"
 		,
 		argv[0]
 	);

### 2022-04-11 article.rnw
Refactor the rnw file to get num_species and num_obs from the InputData object.
Add an `is_per_capita` variable to the InputData object.

@@
 
-	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data")
+	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data", is_per_capita=TRUE)
 
-	num_species <- nrow(species_dat)
-	num_obs <- nrow(read.table("output/design-matrix.data"))
+	num_species <- input_data$num_species
+	num_obs <- input_data$num_obs
 

### 2022-04-11 r/input-data.R

@@ -7,13 +7,15 @@ InputData <- R6::R6Class("InputData",
 		focal_vector = NULL,
 		response_vector = NULL,
 		design_matrix = NULL,
+		is_per_capita = NULL,
 		num_species = NULL,
 		num_obs = NULL,
 		
-		initialize = function(focal_vector_file_name, response_vector_file_name, design_matrix_file_name) {
+		initialize = function(focal_vector_file_name, response_vector_file_name, design_matrix_file_name, is_per_capita=FALSE) {
 			self$focal_vector <- read.table(focal_vector_file_name)[[1]]
 			self$response_vector <- read.table(response_vector_file_name)[[1]]
 			self$design_matrix <- as.matrix(read.table(design_matrix_file_name))
+			self$is_per_capita <- is_per_capita
 			
 			self$num_species <- ncol(self$design_matrix)
 			self$num_obs <- nrow(self$design_matrix)

### 2022-04-11 r/parameters.R
Add a parameters R module, to handle the parameters for a model instance.

@@ -1,0 +1,13 @@
+#An R6 object to store all the parameters for an instance of the model.
+
+Parameters <- R6::R6Class("Parameters",
+	public = list(
+		growth_rates = NULL,
+		alpha_values = NULL,
+		
+		initialize = function(growth_rates, alpha_values) {
+			self$growth_rates <- growth_rates
+			self$alpha_values <- alpha_values
+		}
+	)
+)

### 2022-04-11 article.rnw
Alter the post-process Data object so that it stores parameters using Parameters objects.

@@
 <<include=FALSE>>=
+	source("r/parameters.R")
 	source("r/input-data.R")

### 2022-04-11 r/post-process.R

@@ -38,7 +38,7 @@ Data <- R6::R6Class("Data",
 			names(self$row_groupings) <- species_names
 			names(self$col_groupings) <- species_names
 			self$parameters <- data_table[,grep("parameters", names(data_table))]
-			names(self$parameters) <- gsub("parameters_", "", names(self$parameters)) #Strip "parameters_" from the column names.
+			private$objectify_parameters()
 			self$statistics <- data_table[,grep("_[0-9]*$|parameters", names(data_table), invert=TRUE)]
 			
 			#Add additional columns of statistics.
@@ -56,6 +56,27 @@ Data <- R6::R6Class("Data",
 			) {
 				stop("Data table has the wrong number of species.")
 			}
+		},
+		
+		objectify_parameters = function() {
+			#Turns self$parameters from a data frame of raw parameter values to a vector of R6 Parameters objects.
+			
+			growth_rates_df <- self$parameters[,grep("parameters_r_", names(self$parameters))]
+			alpha_values_df <- self$parameters[,grep("parameters_alpha_", names(self$parameters))]
+			
+			self$parameters <- sapply(1:nrow(self$parameters), function(i) {
+				growth_rates <- as.vector(as.matrix(growth_rates_df[i,]))
+				row_grouping <- as.vector(as.matrix(self$row_groupings[i,]))
+				col_grouping <- as.vector(as.matrix(self$col_groupings[i,]))
+				group_alpha_values <- matrix(
+					as.vector(as.matrix(alpha_values_df[i,])),
+					nrow = self$num_species,
+					byrow = TRUE
+				)
+				alpha_values <- group_alpha_values[row_grouping,col_grouping]
+				
+				return(Parameters$new(growth_rates, alpha_values))
+			})
 		},
 		
 		add_aic_weights = function() {

### 2022-04-11 src/parameters.hpp
Add a missing word to a C++ comment.

@@ -46,7 +46,7 @@ class Parameters {
 		double moveModel(GroupingType groupingType, MoveType moveType, const GroupingMove &groupingMove, RandomVariableFunc getRandomVariable, RandomVariableDensityFunc getRandomVariableDensity);
 		
 		//TODO: If we were to use a non-symmetric jumping density, this would need to return a component of the acceptance ratio.
-		//But it would also need to a bit differently in other ways.
+		//But it would also need to work a bit differently in other ways.
 		void moveParameters(RandomVariableFunc getGrowthRateJump, RandomVariableFunc getCompetitionCoefficientJump);
 };
 

### 2022-04-12 r/input-data.R
Add a get_fitted_values method to InputData.

@@ -19,6 +19,22 @@ InputData <- R6::R6Class("InputData",
 			
 			self$num_species <- ncol(self$design_matrix)
 			self$num_obs <- nrow(self$design_matrix)
+		},
+		
+		get_fitted_values = function(parameters) {
+			focal_growth_rate <- parameters$growth_rates[self$focal_vector]
+			focal_density <- mapply(
+				function(obs,focal){self$design_matrix[obs,focal]},
+				1:num_obs, self$focal_vector
+			)
+			alpha_values_on_focal <- parameters$alpha_values[self$focal_vector,]
+			
+			intrinsic_growth <- focal_growth_rate
+			if(!self$is_per_capita) intrinsic_growth <- intrinsic_growth * focal_density
+			total_competition <- rowSums(alpha_values_on_focal * self$design_matrix)
+			fitted_values <- intrinsic_growth * (1 - total_competition)
+			
+			return(fitted_values)
 		}
 	)
 )

### 2022-04-12 r/input-data.R
Fix an indexing error in the InputData class.
It's reading data designed for a C++ program, so it needs
to add 1 to indices to make them 1 indexed for R.

@@ -12,7 +12,7 @@ InputData <- R6::R6Class("InputData",
 		num_obs = NULL,
 		
 		initialize = function(focal_vector_file_name, response_vector_file_name, design_matrix_file_name, is_per_capita=FALSE) {
-			self$focal_vector <- read.table(focal_vector_file_name)[[1]]
+			self$focal_vector <- read.table(focal_vector_file_name)[[1]] + 1 #Add one to make it 1-indexed, as R prefers.
 			self$response_vector <- read.table(response_vector_file_name)[[1]]
 			self$design_matrix <- as.matrix(read.table(design_matrix_file_name))
 			self$is_per_capita <- is_per_capita

### 2022-05-02 r/grouped-matrix.R
Adjust grouped_alpha_matrix() to add dividing lines.

@@ -67,7 +67,8 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat)
 	
 	#Configuration options.
 	decimal_places <- 3
-	use_dashed_lines <- TRUE
+	use_dashed_lines_inner <- TRUE
+	use_dashed_lines_outer <- FALSE
 	dashed_line_spec <- "1pt/1pt" #Dash/gap.
 	header_angle <- 30
 	
@@ -76,6 +77,19 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat)
 		sprintf(">{\\centering\\arraybackslash}p{\\dimexpr %d %s\\relax}", num_cols, length_macro)
 	}
 	length_macro <- "\\colwidth"
+	divider <- function(use_dashed_lines) {
+		ifelse(use_dashed_lines, sprintf(";{%s}",dashed_line_spec), "|")
+	}
+	cline <- function(use_dashed_lines) {
+		ifelse(use_dashed_lines,
+			function(col1, col2){sprintf("\\cdashline{%d-%d}[%s]", col1, col2, dashed_line_spec)},
+			function(col1, col2){sprintf("\\cline{%d-%d}", col1, col2)}
+		)
+	}
+	outer_divider <- divider(use_dashed_lines_outer)
+	inner_divider <- divider(use_dashed_lines_inner)
+	outer_cline <- cline(use_dashed_lines_outer)
+	inner_cline <- cline(use_dashed_lines_inner)
 	
 	#Determine the width of the widest cell entry.
 	#Following the decimal point will always be decimal_places characters.
@@ -128,11 +142,18 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat)
 	
 	#A helper function to get the content of a particular group.
 	#Wrapped in \multicolumn and \multirow to make it the right size for that group.
-	get_expanded_group_content <- function(row_index, col_index) {
+	#Also adds vertical rules.
+	#Adding the vertical dividers is interfered with by multirow, so we need some empty \multicolumns.
+	#is_empty_content produces such.
+	get_expanded_group_content <- function(row_index, col_index, is_first_group, is_last_group, is_empty_content) {
 		num_rows <- sum(row_grouping == row_grouping[row_index])
 		num_cols <- sum(col_grouping == col_grouping[col_index])
-		#TODO: Add vertical rules.
[…]

### 2022-05-02 r/grouped-matrix.R
Adjust the dashed lines in grouped_alpha_matrix() to avoid a visual bug.
They looked odd when the documetnt was zoomed out.

@@ -69,7 +69,7 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat)
 	decimal_places <- 3
 	use_dashed_lines_inner <- TRUE
 	use_dashed_lines_outer <- FALSE
-	dashed_line_spec <- "1pt/1pt" #Dash/gap.
+	dashed_line_spec <- "3pt/3pt" #Dash/gap.
 	header_angle <- 30
 	
 	#Define some helper functions/variables.

### 2022-05-02 r/coclassification-table.R
Correct spelling.

@@ -66,7 +66,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 	}
 	
 	#LaTeX doesn't like us using \pgfplotscolormapaccess mid-table.
-	#So we will use it beforehand, define colours, then acces them.
+	#So we will use it beforehand, define colours, then access them.
 	#This requires us to generate a unique colour name for each cell.
 	#We will make it verbose to reduce the risk of a clash.
 	get_colour_name <- function(row, col) {

### 2022-05-02 r/coclassification-table.R
Add more options to weighted_coclassification_kable().
To adjust array stretch, inclusion of names,
and inclusion of the colourbar.

@@ -16,10 +16,9 @@ strip_booktabs_rules <- function(tab) {
 		sub("\\\\bottomrule", "", .)
 }
 
-weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray", digits=3) {
+weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray", digits=3, array_stretch=1.5, has_colourbar=TRUE, has_names=TRUE) {
 	#colourmap is the name of a pgfplots colourmap.
 	
-	array_stretch <- 1.5
 	header_angle <- 30
 	
 	#\dimexpr can't work with floating point multipliers, so we need rationals.
@@ -58,11 +57,15 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 	sep="\n")
 	
 	format_num <- function(num) {
-		if(round(num,digits=digits) == 1) {
-			return(paste0("1.",paste0(rep("0",digits-1),collapse="")))
+		if(digits == 0) {
+			return(sprintf("%.0f", num)) #Gives just 0 or 1, no decimal places.
+		} else {
+			if(round(num,digits=digits) == 1) {
+				return(paste0("1.",paste0(rep("0",digits-1),collapse="")))
+			}
+			sprintf(paste0("%.",digits,"f"), num) %>%
+				sub("0.", ".", ., fixed=TRUE) #Strip the leading 0.
 		}
-		sprintf(paste0("%.",digits,"f"), num) %>%
-			sub("0.", ".", ., fixed=TRUE) #Strip the leading 0.
 	}
 	
 	#LaTeX doesn't like us using \pgfplotscolormapaccess mid-table.
@@ -96,16 +99,21 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 		})
 	})
 	
-	#\rotatebox makes things wider, so we enclose in a fixed width \makebox.
-	colnames(string_mat) <- paste0("\\makebox[1em][l]{\\rotatebox{",header_angle,"}{\\emph{",colnames(mat),"}}}")
-	#We don't set row names for mat, because we want the species labels on the right instead of the left.
-	#We cbind instead.
-	string_mat <- cbind(string_mat, matrix(
-		paste0("\\emph{",rownames(mat),"}"),
-	ncol=1))
+	if(has_names) {
[…]

### 2022-05-02 r/coclassification-table.R
Add minimal_coclassification_kable().
It just pre-sets some options to weighted_coclassification_kable().

@@ -141,3 +141,8 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 	cat(colour_definitions)
 	cat(outer_tab)
 }
+
+#A shortcut for a minimal version.
+minimal_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray") {
+	weighted_coclassification_kable(mat, colourmap, diagonal_colour, digits=0, array_stretch=0.8, has_colourbar=FALSE, has_names=FALSE)
+}

### 2022-05-02 article.rnw
Add the grouped matrix module, and required LaTeX packages, to article.rnw.

--- 2022-04-11 article.rnw
@@
 
-%Images
+%Images & tables
 \usepackage{subcaption}
@@
 \usepackage{colortbl}
+\usepackage{multirow}
+\usepackage{arydshln}
 
@@
 	source("r/coclassification-table.R")
+	source("r/grouped-matrix.R")
 

### 2022-05-03 r/post-process.R
Remove an unnecessary call to as.matrix().
It's being called on something that's already a matrix.

@@ -132,9 +132,9 @@ Data <- R6::R6Class("Data",
 		get_coclassification_matrix = function(grouping_table, index) {
 			#Returns a binary matrix of whether two species are grouped together in a given row of a grouping table.
 			grouping <- as.vector(as.matrix(grouping_table[index,]))
-			mat <- as.matrix(sapply(grouping, function(group) {
+			mat <- sapply(grouping, function(group) {
 				return(grouping == group)
-			}))
+			})
 			return(mat)
 		},
 		

### 2022-05-03 r/post-process.R
Refactor the post-process module with an as_coclassification_matrix() function.

@@ -14,6 +14,14 @@ information_criterion_weights <- function(information_criterion) {
 	return(weights)
 }
 
+as_coclassification_matrix <- function(grouping) {
+	#Converts a grouping to a binary coclassification matrix.
+	mat <- sapply(grouping, function(group) {
+		return(grouping == group)
+	})
+	return(mat)
+}
+
 Data <- R6::R6Class("Data",
 	public = list(
 		num_species = NULL,
@@ -132,10 +140,7 @@ Data <- R6::R6Class("Data",
 		get_coclassification_matrix = function(grouping_table, index) {
 			#Returns a binary matrix of whether two species are grouped together in a given row of a grouping table.
 			grouping <- as.vector(as.matrix(grouping_table[index,]))
-			mat <- sapply(grouping, function(group) {
-				return(grouping == group)
-			})
-			return(mat)
+			return(as_coclassification_matrix(grouping))
 		},
 		
 		get_weighted_coclassification_matrix = function(grouping_table, weights) {

### 2022-05-03 r/grouped-matrix.R
Fix an ordering bug in grouped_alpha_matrix().
Introduced in b3719e242f7cd7aba619ac13b3623553a6735e63.
Prior to that refactor, the matrix was defined in terms of the groups,
so reordering the species didn't matter.
That refactor made it defined in terms of the species,
so it needs reordering as the species are reordered.

@@ -64,6 +64,7 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat)
 	species_names <- species_names[ordering]
 	row_grouping <- row_grouping[ordering]
 	col_grouping <- col_grouping[ordering]
+	mat <- mat[ordering,ordering]
 	
 	#Configuration options.
 	decimal_places <- 3

### 2022-05-03 r/grouped-matrix.R
Add an option to grouped_alpha_matrix() to assume the species are already ordered.

@@ -56,15 +56,22 @@ get_integer_part_width <- function(x) {
 }
 
 #Finally, the function to actually print the grouped matrix.
-grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat) {
+grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat, is_ordered=TRUE) {
 	num_species <- length(species_names)
 	
-	#Reorder the species to place grouped species adjacent.
-	ordering <- get_ordering(list(row_grouping, col_grouping))
-	species_names <- species_names[ordering]
-	row_grouping <- row_grouping[ordering]
-	col_grouping <- col_grouping[ordering]
-	mat <- mat[ordering,ordering]
+	if(is_ordered) {
+		#Assert that the ordering is correct.
+		if(!forms_consecutive_blocks(row_grouping, 1:num_species) || !forms_consecutive_blocks(col_grouping, 1:num_species)) {
+			stop("Given ordering does not make all groups consecutive")
+		}
+	} else {
+		#Reorder the species to place grouped species adjacent.
+		ordering <- get_ordering(list(row_grouping, col_grouping))
+		species_names <- species_names[ordering]
+		row_grouping <- row_grouping[ordering]
+		col_grouping <- col_grouping[ordering]
+		mat <- mat[ordering,ordering]
+	}
 	
 	#Configuration options.
 	decimal_places <- 3

### 2022-05-03 r/coclassification-table.R
Ensure matrices passed to weighted_coclassification_kable() are numeric, not Boolean.

@@ -21,6 +21,8 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 	
 	header_angle <- 30
 	
+	mat <- matrix(as.numeric(mat), nrow=nrow(mat)) #Ensure the matrix is numeric, not Boolean.
+	
 	#\dimexpr can't work with floating point multipliers, so we need rationals.
 	as_rational_string <- function(x) {
 		as.character(gmp::as.bigq(x))

### 2022-05-09 r/coclassification-table.R
Change the default array stretch for a minimal coclassification table.

@@ -146,5 +146,5 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 
 #A shortcut for a minimal version.
 minimal_coclassification_kable <- function(mat, colourmap="hot", diagonal_colour="lightgray") {
-	weighted_coclassification_kable(mat, colourmap, diagonal_colour, digits=0, array_stretch=0.8, has_colourbar=FALSE, has_names=FALSE)
+	weighted_coclassification_kable(mat, colourmap, diagonal_colour, digits=0, array_stretch=1, has_colourbar=FALSE, has_names=FALSE)
 }

### 2022-05-09 r/grouped-matrix.R
Allow customising array stretch in grouped_alpha_matrix().

@@ -56,7 +56,7 @@ get_integer_part_width <- function(x) {
 }
 
 #Finally, the function to actually print the grouped matrix.
-grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat, is_ordered=TRUE) {
+grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat, is_ordered=TRUE, array_stretch=1.5) {
 	num_species <- length(species_names)
 	
 	if(is_ordered) {
@@ -112,8 +112,12 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat,
 	length_definition <- sprintf("\\ifdefined%s\\relax\\else\\newlength{%s}\\fi\n\\settowidth{%s}{$%s$}\n", length_macro, length_macro, length_macro, widest_number)
 	
 	#The beginning and end of the table.
-	begin <- paste(c("\\begin{tabular}{", rep(alignment(1), num_species), "l}"), collapse="")
-	end <- "\\end{tabular}"
+	begin <- paste(c(
+		"\\begingroup",
+		"\\renewcommand*\\arraystretch{", array_stretch, "}",
+		"\\begin{tabular}{", rep(alignment(1), num_species), "l}"
+	), collapse="")
+	end <- "\\end{tabular}\\endgroup"
 	
 	#The row with the species names as column headers.
 	get_species_column_label <- function(index) {

### 2022-05-09 article.rnw
Move the colour definitions within the rnw file.
This means the same colours can be used for coclassification matrices
throughout the document, when new coclassisification matrices are added.
Add a figure showing the alpha values of the "best" model.

@@
 \newcommand\keywords[1]{\emph{Key words: #1}}
+
+\pgfplotsset{%
+	colormap={coclassification}{color=(white) color=(red)}
+}
+\colorlet{coclassification diagonal}{black!20}
 
@@
 The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
+\Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
 The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
@@
 This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
+
+\begin{figure}
+	\centering
+
+	<<echo=FALSE>>=
+		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
+		best_row_grouping <- brute_data$get_row_grouping(best_model_index)
+		best_col_grouping <- brute_data$get_col_grouping(best_model_index)
+		best_alpha_matrix <- brute_data$parameters[[best_model_index]]$alpha_values
+
+		ordering <- get_ordering(list(best_row_grouping, best_col_grouping))
+		best_species_names <- brute_data$species_names[ordering]
+		best_row_grouping <- best_row_grouping[ordering]
+		best_col_grouping <- best_col_grouping[ordering]
+		best_alpha_matrix <- best_alpha_matrix[ordering,ordering]
+
+		best_row_coclassification <- as_coclassification_matrix(best_row_grouping)
+		best_col_coclassification <- as_coclassification_matrix(best_col_grouping)
+	@
+
+	\begin{subfigure}{\textwidth}
+		\centering
+		<<echo=FALSE>>=
+			grouped_alpha_matrix(
+				best_species_names,
+				best_row_grouping,
+				best_col_grouping,
+				best_alpha_matrix
+			)
+		@
+		\caption{The grouped alpha matrix.}
+		\label{fig:best-alpha-matrix}
+	\end{subfigure}
+
+	\bigskip
+
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		<<echo=FALSE>>=
+			minimal_coclassification_kable(
+				best_col_coclassification,
+				colourmap="coclassification", diagonal_colour="coclassification diagonal"
+			)
+		@
+		\caption{The coclassification matrix of rows.}
+		\label{fig:best-coclassification-cols}
+	\end{subfigure}
+	%
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		<<echo=FALSE>>=
+			minimal_coclassification_kable(
+				best_row_coclassification,
+				colourmap="coclassification", diagonal_colour="coclassification diagonal"
+			)
+		@
+		\caption{The coclassification matrix of columns.}
+		\label{fig:best-coclassification-rows}
+	\end{subfigure}
+
+	\caption{%
+		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
+		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
+		\Cref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
+		\Cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
+		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
+		Species have been reordered that species which are grouped together appear adjacent.
+		The ordering is the same in \cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} as shown in \cref{fig:best-alpha-matrix}.
+	}
+	\label{fig:best-model}
+\end{figure}
 
@@
 
-\pgfplotsset{%
-	colormap={coclassification}{color=(white) color=(red)}
-}
-\colorlet{coclassification diagonal}{black!20}
 \begin{figure}

### 2022-05-10 article.rnw

@@
 Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
+% DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
 Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
 Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
-This is expensive, and requires a lot of effort.
+This is understandably expensive and requires substantial effort.
 As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
 However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
-To bridge this gap between the size of real communities and our ability to parameterise them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
+To bridge this gap between the size of real communities and our ability to parameterise models for them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
 
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{wootton2016many}, and setting these to zero may lose important information.
-Another approach assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{XXX, wootton2016many}, and setting these to zero may lose important information.
+Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
 
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional groupings \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
-The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic}.
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
+% please add a reference to http://dx.doi.org/10.1086/713082 to the above
+The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
-On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant}.
+On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX, bret2008plant}.
 While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
@@
 I can point to some very good references along those lines.
-In this study, we investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
-We fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
-We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
+In this study, we investigate the usefulness and correctness of such an approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
+We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model.
+While doing so, we group species independently with regard to their effects upon other species and their responses to other species, to find whether the data-informed groupings differ between these two cases.
 %TODO: Mention the comparison to traits (body size)?
+% DBS: If we leave in the traits, then we should mention them at least briefly.
 
@@
 
-From the Akaike weights, we calculated two important statistics.
-Firstly, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
-Secondly, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
-To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a random equally-sized subset of the models.
+Using these Akaike weights, we calculated two important statistics.
+First, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the fully ungrouped model.
+Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
+To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
 %This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
@@
 \Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
-The total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
+Despite it being just over $7$ {\ic} units from the most parsimonious model, the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
 
 Considering only models in which the rows and columns were grouped using the same grouping, the {\ic} values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
-The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
+The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; this was more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
 This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
@@
 
+% DBS: Most journals frown upon or do not allow overly verbose subtitles on figures. So I've cut them down to be a bit more concise.
+% DBS: But the fact that the labels say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
+We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects.
+As long as we're consistent, I'm fine either way.
+But we need to remember we're writing the paper for the audience and not for ourselves.
+;)
 \begin{figure}
@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
+This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{XXX, blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{XXX, godoy2014phylogenetic}.
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
-Perhaps species simply do not group to the same extent in a competitive context.
-The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
-Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
-Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.
+% DBS: We're probably doing a disservice to the "groups in ecological communities" literature by only citing the Allesina paper above.
 
+One possible explanation is that species simply do not group to the same extent in a competitive context.
+That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
+Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
+In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
 All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.

### 2022-05-16 article.rnw
Add a missing semantic newline.
Change "regularising" to "simplifying" in the title.
"Regularising" is a word that needs explanation, but an explanation
does not fit neatly anywhere in the paper.
Fix the format of subreferences within figure captions.
(a) rather than "fig. 1a".
Unfortunately, this has necessitated a change from \cref to \subref.

@@
 \usepackage{arydshln}
+
+\captionsetup{subrefformat=parens} %Changes only \subref, not \ref.
+\let\Subref\subref
+%TODO: Make \cref figure out if it should be a subref, and use cref throughout.
 
@@
 %Title Page
-% DBS: What about "Simplifying Lotka--Volterra interaction matrices by species grouping", with or without the bit after the colon (and where I lean slightly in favor of the "with" option)
-\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable} %TODO: Remove the word "regularising" from the title.
+\title{Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
 \author{Christopher R.\ P.\ Brown}
@@
 		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
-		\Cref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
-		\Cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
+		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
+		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
 		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
 		Species have been reordered that species which are grouped together appear adjacent.
-		The ordering is the same in \cref{fig:best-coclassification-cols} and \cref{fig:best-coclassification-rows} as shown in \cref{fig:best-alpha-matrix}.
+		The ordering is the same in \subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} as shown in \subref{fig:best-alpha-matrix}.
 	}
@@
 		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
-		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
+		\Subref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \subref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
 	}
@@
 \end{figure}
-
-% DBS: Within the caption, the reference to a subfigure should just be (a) and (b), not Figure 2a and fig. 2b.
 

### 2022-05-16 article.rnw
Fix the rounding for AICc values in the manuscript.
For some reason, the precision to print them to wasn't specified.
Fix a hard-coded number in the results, and reword the sentence around it.
The sentence said "just over 7", so it had to be reworded if the
number wasn't going to be hard-coded.

@@
 \newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
-\newcommand\icnum[1]{\num{#1}} %For information criteria.
+\newcommand\icnum[1]{\num[round-mode=places,round-precision=2]{#1}} %For information criteria.
 \newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
@@
 \Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
-Despite it being just over $7$ {\ic} units from the most parsimonious model, the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
+The ungrouped model had an {\ic} just \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]] - min(brute_data$statistics[[ic]])}} units from the most parsimonious model, but the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
 

### 2022-05-17 article.rnw
Add a reference with another example of a priori species grouping.

@@
 
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling}.
-% please add a reference to http://dx.doi.org/10.1086/713082 to the above
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
 The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.

### 2022-05-17 article.rnw
Mention the comparison of groupings to species traits in the introduction.
Set echo=FALSE as a global default for knitr chunks in the article.

@@
 <<include=FALSE>>=
+	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
 	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
@@
 In this study, we investigate the usefulness and correctness of such an approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
-We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model.
+We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model, and compare these groupings to similarity based upon a species trait (body size).
 While doing so, we group species independently with regard to their effects upon other species and their responses to other species, to find whether the data-informed groupings differ between these two cases.
-%TODO: Mention the comparison to traits (body size)?
-% DBS: If we leave in the traits, then we should mention them at least briefly.
 
@@
 \begin{figure}
-	<<echo=FALSE>>=
+	<<>>=
 		hist(brute_data$statistics[[ic]],
@@
 
-	<<echo=FALSE>>=
+	<<>>=
 		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
@@
 		\centering
-		<<echo=FALSE>>=
+		<<>>=
 			grouped_alpha_matrix(
@@
 		\centering
-		<<echo=FALSE>>=
+		<<>>=
 			minimal_coclassification_kable(
@@
 		\centering
-		<<echo=FALSE>>=
+		<<>>=
 			weighted_coclassification_kable(

### 2022-05-17 article.rnw
Remove a sentence (about reading Terry for methods) that DBS commented out.
Remove a clause from the methods that DBS commented out.
Remove a break between two paragraphs.
The second "paragraph" was a single sentence, which is poor practice.
Add a sentence explaining how many parameters the ungrouped model has.
Rearrange the methods section on species groupings.

@@
 
-%We shall not repeat the entire experimental methodology here---refer to \textcite{terry2021natural} for that---but provide a summary of the pertinent points.
-% DBS: I don't think we need the above because we say the same thing in line 172 below.
-
 \subsubsection{Summary of the experimental methodology}
@@
 The number of adult pairs of each species emerging from these eggs was counted.
-%---this was the size of the next generation.
-% DBS: Do we need the bit I've commented out above? Plus, it isn't the size of the next generation it's the number of new adults...
 
@@
 Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
- %
 Further details of the experimental methodology can be found in \textcite{terry2021natural}.
@@
 The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.
-
-% DBS: Let's add something that very briefly outlines how many parameters this model has.
-Then, below, we can provide formulae for the number of parameters given the number of row and column groups.
-Even though people can work this out themselves, it is probably useful to make it explicit so that we don't have to depend on them actually mustering up the energy to do so.
+With $n$ species, this model has $n+n^2$ parameters: $n$ growth rates and $n^2$ competition coefficients.
 
@@
 
-% DBS: I still feel like the bits and pieces of the section below are not in a well-flowing order.
+In order to reduce the number of free parameters in the model, we grouped species together, and constrained the appropriate competition coefficients to be equal for species within the same group.
+In our grouping, we avoided the common assumption that species which are similar in their responses to competition would automatically be similar in their competition effects.
+As such, we had two groupings; one grouping of the competitive responses, and one of the competitive effects.
 
-In order to reduce the number of free parameters in the model, we grouped species together, and constrained the appropriate competition coefficients to be equal for species within the same group.
+The set of competition coefficients in the Lotka--Volterra model can be arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
+As such, if two species are assumed to have the same response to competition, then two rows of the interaction matrix are constrained to be equal.
+Similarly, if two species are assumed to have the same competitive effect, then two columns of the interaction matrix are constrained to be equal.
+This allows us to refer simply to the ``row grouping'' and the ``column grouping''.
+Formally, if species $a$ and $b$ were in the same row group, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$, and if $a$ and $b$ were in the same column group, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$.
+As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
+The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
 
-A grouping, known as a partition in mathematics, divides the species into groups such that each species belongs to one and only one group.
+Groupings are known formally as ``partitions'' in mathematics.
+A grouping divides the species into groups such that each species belongs to one and only one group.
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.
@@
 With $1$ group, every species is placed in the same group, such that all are equal in their interactions, reminiscent of the neutral model.
-
-We did not assume that species should be grouped the same in their competitive effects as in their competitive responses.
-As such, each model was defined by two groupings: a grouping of species constraining equivalence in their competitive effects, and a second, independent grouping of species constraining equivalence in their competitive responses.
-
-The set of competition coefficients in the Lotka--Volterra model can be arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
-As such, if two species are in the same group regarding their competitive responses, then two rows of the interaction matrix are constrained to be equal.
-Similarly, if two species are in the same group regarding their competitive effects, then two columns of the interaction matrix are constrained to be equal.
-This allows us to refer simply to the ``row grouping'' and the ``column grouping''.
-Formally, if species $a$ and $b$ were in the same column group, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$, and if $a$ and $b$ were in the same row group, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$.
-As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
-The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
-
 The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.

### 2022-05-19 article.rnw
Rearrange the methods section on species groupings again.

@@
 In order to reduce the number of free parameters in the model, we grouped species together, and constrained the appropriate competition coefficients to be equal for species within the same group.
-In our grouping, we avoided the common assumption that species which are similar in their responses to competition would automatically be similar in their competition effects.
-As such, we had two groupings; one grouping of the competitive responses, and one of the competitive effects.
+Within the model defined above, each species is effectively in its own group, such that all pairs of species interact in a unique fashion.
+At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently, reminiscent of the neutral model.
+Given $n$ species, there may be any integer number of groups from $1$ to $n$.
+Groupings are known formally as partitions in mathematics, and the total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
 
-The set of competition coefficients in the Lotka--Volterra model can be arranged in an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
+It is commonly assumed that species which are similar in their responses to competition would automatically be similar in their competition effects.
+However, competitive responses may be governed by a different set of traits than compeititive effects, so this assumption does not necessarily hold.
+We avoided this assumption by allowing species which were similar in one regard to be dissimilar in the other, and vice versa.
+As such, each model was defined by two groupings of species: one grouping of the competitive responses, and one of the competitive effects.
+
+To better understand the meaning of species grouping of competition coefficients, it is useful to recognize that this component of the Lotka--Volterra model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
 As such, if two species are assumed to have the same response to competition, then two rows of the interaction matrix are constrained to be equal.
 Similarly, if two species are assumed to have the same competitive effect, then two columns of the interaction matrix are constrained to be equal.
-This allows us to refer simply to the ``row grouping'' and the ``column grouping''.
+This allows us to refer below to the grouping of the competitive responses as the ``row grouping'' and the grouping of the competitive effects as the ``column grouping''.
 Formally, if species $a$ and $b$ were in the same row group, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$, and if $a$ and $b$ were in the same column group, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$.
-As such, the total number of free competition coefficients in the model was equal to the number of row groups multiplied by the number of column groups.
+
+With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
 The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
-
-Groupings are known formally as ``partitions'' in mathematics.
-A grouping divides the species into groups such that each species belongs to one and only one group.
-Given $n$ species, there may be any integer number of groups from $1$ to $n$.
-With $n$ groups, the grouping places each species into its own group, such that all species interact in a unique fashion.
-With $1$ group, every species is placed in the same group, such that all are equal in their interactions, reminiscent of the neutral model.
-The total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
-With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
+The total number of parameters in the model is reduced to $n$ growth rates, and a number of competition coefficients equal to the number of row groups multiplied by the number of column groups.
 

### 2022-05-22 article.rnw
Change "neutral" to "ecologically equivalent" per McPeek 2019.

@@
 Within the model defined above, each species is effectively in its own group, such that all pairs of species interact in a unique fashion.
-At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently, reminiscent of the neutral model.
+At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently; they are ecologically equivalent in the sense of \textcite{mcpeek2019disentangling}.
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.

### 2022-05-22 article.rnw
Swap the order of two paragraphs in the discussion.
Remove the concluding paragraph of the discussion.

@@
 
-% DBS: I think we should swap the order of the following two paragraphs.
-
-The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
-This could suggest a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
-Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
-
 While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
@@
 
-% DBS: Never shoot yourself in the foot in your concluding paragraph! The reviewers will already be primed to do this for you, so I always think it's better to take a glass half full perspective.
-% DBS: Also, there is no hard and fast rule to say we need a "sum it all up" concluding paragraph.
-Each of the statements below is pretty much already stated above but with more depth.
-I think we could actually do away with it and lose very little.
-All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely related set of species.
-However, the results suggest some advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.
-Firstly, there may be no single best grouping, but perhaps multiple rather distinct groupings which each perform similarly.
-Furthermore, one should not implicitly assume that species are grouped in the same way with regard to their effects upon other species and their response to them; distinct groupings of the two might well be considered.
+The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
+This could suggest a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
+Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
 

### 2022-05-22 article.rnw
Remove an unnecessary sentence, moving the figure reference into the sentence after.

@@
 
-Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
-% DBS: In general, I am more in favor of just putting something like a pointer to a figure "(Fig.~1)" at the end of the sentence below than an explicit statement of what appears in a figure.
-Some journals also frown on devoting words to explanations of what appears in figures since that is technically what figure captions are for.
-Overall, no pair of species can confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent}.
+Overall, no pair of species can confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent} (\cref{fig:coclassification}).
 Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

### 2022-05-22 article.rnw
Move the word "however" from the middle to the beginning of a sentence.
Remove some commented out sentences.
Add a concluding "what to do going forward" sentence to the abstract.

@@
 Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating a key assumption often made implicitly when defining species groupings.
-% DBS: add some sort of concluding sentence a la where to from here
+This suggests the need for a different, more data-ifnormed, approach to grouping in species interaction models.
 
@@
 As such, we instead fit the models with the Gauss--Newton method for non-linear least squares and assumed a normal error distribution of the response variable.
-%The models were fitted to the data using maximum likelihood regression techniques.
-%Fitting it using precisely a Lotka--Volterra model prevented the use of a link function, rendering most generalised regression techniques infeasible.
 To prevent heteroskedasticity and improve normality, we transformed total population growth to per capita population growth, which corresponds to the following model:
@@
 To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
-%This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
 
@@
 Overall, no pair of species can confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent} (\cref{fig:coclassification}).
-Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
+However, some pairs of species were far more likely to be coclassified than others, suggesting some structure to the best groupings.
 

### 2022-05-22 article.rnw
Add a sentence justifying the difference in traits determining competitive effect and response.
Correct spelling.

@@
 Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating a key assumption often made implicitly when defining species groupings.
-This suggests the need for a different, more data-ifnormed, approach to grouping in species interaction models.
+This suggests the need for a different, more data-informed, approach to grouping in species interaction models.
 
@@
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
-% DBS: Maybe it's worth adding a concrete example here for the more empirical reader/reviewer.
+For resource competition in particular, competitive effect is determined by how the organism affects local resource availability, while competitive response is determined by the organism is inhibited by depleted resources \parencite{violle2009competition}.
 As such, the best groupings of species may be different for each of the effects and responses.

### 2022-05-22 article.rnw
Remove a commented out paragraph break.
Correct spelling.

@@
 It is commonly assumed that species which are similar in their responses to competition would automatically be similar in their competition effects.
-However, competitive responses may be governed by a different set of traits than compeititive effects, so this assumption does not necessarily hold.
+However, competitive responses may be governed by a different set of traits than competitive effects, so this assumption does not necessarily hold.
 We avoided this assumption by allowing species which were similar in one regard to be dissimilar in the other, and vice versa.
@@
 
-To better understand the meaning of species grouping of competition coefficients, it is useful to recognize that this component of the Lotka--Volterra model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
+To better understand the meaning of species grouping of competition coefficients, it is useful to recognise that this component of the Lotka--Volterra model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
 As such, if two species are assumed to have the same response to competition, then two rows of the interaction matrix are constrained to be equal.
@@
 We did this using a Mantel test, as appropriate for similarity matrices.
- %
 We could also test the coclassification matrices for correlation with an expected dissimilarity matrix.
@@
 Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
-%DBS: Add in the number of models for both of these to emphasize the point.
+%DBS: Add in the number of models for both of these to emphasise the point.
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

### 2022-05-22 article.rnw
Use \cref for an equation reference.
Standardise the format of equation labels to that used for figures.
Add a sentence regarding the success of data-informed grouping in networks.

@@
 We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
-% DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks.
-I can point to some very good references along those lines.
-In this study, we investigate the usefulness and correctness of such an approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
+Data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional, newman2006modularity, girvan2002community}.
+In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
 We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model, and compare these groupings to similarity based upon a species trait (body size).
@@
 	N_{i,t+1} - N_{i,t} = N_{i,t} \, r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right) \,,
-	\label{LVmodel}
+	\label{eq:lv-model}
 \end{equation}
@@
 
-The Lotka--Volterra competition model in Eq.~(\ref{LVmodel}) is not linear in the parameters.
+The Lotka--Volterra competition model in \cref{eq:lv-model} is not linear in the parameters.
 With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.

### 2022-05-22 article.rnw
Add a missing semantic newline.
Add a missing word.

@@
 A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
-This could suggest a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
+This could suggest that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
 Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.

### 2022-05-22 article.rnw
Remove a completed TODO.
Add missing references for the first paragraph of the introduction.

@@
 They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
-The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{XXX}.
+The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{gilman2010framework, sutherst2007including}.
 
@@
 		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
-		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}). %TODO: Debug this.
+		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
 		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.

### 2022-05-22 article.rnw
Add an additional reference for the minimum number of parameters in a species interaction model.

@@
 This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
-Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, XXX}.
+Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, rocha2005lotka}.
 % DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?

### 2022-05-22 article.rnw
Add an additional reference regarding species interaction models usually being small.

@@
 This is understandably expensive and requires substantial effort.
-As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species, XXX}.
+As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species,maynard2020predicting}.
 However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.

### 2022-05-22 article.rnw
Add additional references regarding the importance of weak interactions to stability.

@@
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{XXX, wootton2016many}, and setting these to zero may lose important information.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}, and setting these to zero may lose important information.
 Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

### 2022-05-23 article.rnw
Standardise to not using spaces after commas in \cite commands.
I was being inconsistent on this.

@@
 They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
-The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{gilman2010framework, sutherst2007including}.
+The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{gilman2010framework,sutherst2007including}.
 
@@
 This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
-Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing, rocha2005lotka}.
+Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing,rocha2005lotka}.
 % DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
@@
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
-On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX, bret2008plant}.
+On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX,bret2008plant}.
 While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
@@
 We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
-Data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional, newman2006modularity, girvan2002community}.
+Data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
 In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
@@
 The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify, XXX}.
+This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify,XXX}.
 
@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{XXX, blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{XXX, godoy2014phylogenetic}.
+This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{XXX,blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{XXX,godoy2014phylogenetic}.
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.

### 2022-05-23 article.rnw
Add a missing word.

@@
 
-To the best of our knowledge, studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
+To the best of our knowledge, all studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.

### 2022-05-23 article.rnw
Add additional references for the argument behind grouping based on phylogeny.

@@
 In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
-The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{XXX,godoy2014phylogenetic}.
+The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic,webb2002phylogenies,darwin1859origin}.
+%Darwin Chapter 3 "Struggle for Life Most Severe Between Individuals and Varieties of the Same Species".
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.

### 2022-05-23 article.rnw
Add an additional reference regarding the inadequacy of functional groups.
Remove a citation placeholder that's nigh-impossible to fill.
To the best of our knowledge, all studies that group species have grouped
them the same in their competitive effects and responses. This is
nigh-impossible to provide a citation for, as proving it by citation
is an attempt to prove a negative. One cannot simply cite a bunch of studies
that have made this assumption, but I cannot find a paper that even
identifies that the assumptions is typically made.

@@
 However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
-On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{XXX,bret2008plant}.
+On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant,funk2017revisiting}.
 While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
@@
 
-To the best of our knowledge, all studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others \parencite{XXX}.
+To the best of our knowledge, all studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others.
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.

### 2022-05-23 article.rnw
Add additional references regarding the use of response surface designs.

@@
 The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify,XXX}.
+This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify,zhang2019common,cameron2019size}.
 

### 2022-05-23 article.rnw
Add additional references regarding the use of grouping in existing studies.

@@
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{XXX,blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{XXX,godoy2014phylogenetic}.
+This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds,kirwan2009diversity,boulangeat2012improving}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic,wilcox2018evolutionary}.
 It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.

### 2022-05-23 article.rnw
Rewrite a couple of sentences in the discussion to include more references.
Some of the content of a sentence that ended one paragraph has been
moved to the first sentence of the folllowing paragraph.

@@
 This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds,kirwan2009diversity,boulangeat2012improving}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic,wilcox2018evolutionary}.
-It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
-% DBS: We're probably doing a disservice to the "groups in ecological communities" literature by only citing the Allesina paper above.
+It also contrasts with previous studies that have succeeded in finding clear groups in other ecological contexts, such as in food webs \parencite{krause2003compartments,allesina2009food} and pollination networks \parencite{olesen2007modularity}.
 
-One possible explanation is that species simply do not group to the same extent in a competitive context.
+One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
 That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.

### 2022-05-23 article.rnw
Add some numbers to emphasise the atrocious algorithmic complexity of the method.

@@
 Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
-Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species.
-%DBS: Add in the number of models for both of these to emphasise the point.
+Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

### 2022-05-23 article.rnw
Remove an unnecessary sentence in the discussion.
Add a missing referenceregarding the multivariate nature of niche.

@@
 That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
-Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
 In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
@@
 The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{XXX}.
+A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
 This could suggest that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.

### 2022-05-23 article.rnw
Change "in the sense of" to "sensu".
To make it clear the technical meaning is meant.

@@
 Within the model defined above, each species is effectively in its own group, such that all pairs of species interact in a unique fashion.
-At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently; they are ecologically equivalent in the sense of \textcite{mcpeek2019disentangling}.
+At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently; they are ecologically equivalent \emph{sensu} \textcite{mcpeek2019disentangling}.
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.

### 2022-05-23 r/coclassification-table.R
Fix a bug in weighted_coclassification_kable() that broke it with has_names=TRUE.
The method of casting the matrix to numeric was losing the names.

@@ -21,7 +21,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 	
 	header_angle <- 30
 	
-	mat <- matrix(as.numeric(mat), nrow=nrow(mat)) #Ensure the matrix is numeric, not Boolean.
+	class(mat) <- "numeric" #Ensure the matrix is numeric, not Boolean.
 	
 	#\dimexpr can't work with floating point multipliers, so we need rationals.
 	as_rational_string <- function(x) {

### 2022-06-02 article.rnw
Correct the tense of a sentence.
DBS edits and final comments

@@
 
-Dynamic models of ecological communities require many parameters, making them expensive to fit to experimental or observational data.
+Most dynamic models of ecological communities require many parameters, making them expensive to fit to experimental or observational data.
 To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogenetic or functional groups, and species within a group are assumed to behave identically.
-Here, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori}, from the parsimony of a Lotka--Volterra model fit to experimental data from six species of \emph{Drosophila} competing in laboratory conditions.
+Here, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori} based on the fit of the Lotka--Volterra competition model to experimental data from six species of \emph{Drosophila} competing in laboratory conditions.
 We find evidence that grouping can improve the parsimony of species interaction models, but we also observe that there is no single optimal grouping.
-Further, those groupings that did prove beneficial could not be easily predicted from available species attributes \emph{a priori}, calling into question the prevailing method of \emph{a priori} species grouping.
+Further, those groupings that did prove beneficial could not have been easily predicted from available species attributes, calling into question the prevailing method of \emph{a priori} species grouping.
 Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating a key assumption often made implicitly when defining species groupings.
-This suggests the need for a different, more data-informed, approach to grouping in species interaction models.
+Our study suggests the need for a different, more data-informed, approach to grouping in species interaction models.
 
 % DBS: Once we have a title, make sure that we remove all words from the keywords that appear there.
-\keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony}
+\keywords{competition; ecological equivalence; grouping; model fitting; parsimony; \emph{Drosophila}}
 
@@
 Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing,rocha2005lotka}.
-% DBS: Hmm. Should the above two or rephrased to embrace the directionality of what's going on?
 Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
@@
 One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}, and setting these to zero may lose important information.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}, and setting any individual parameter to zero risks losing important information.
 Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
 
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional (i.e., trait) similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
 The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic,webb2002phylogenies,darwin1859origin}.
@@
 There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
-For resource competition in particular, competitive effect is determined by how the organism affects local resource availability, while competitive response is determined by the organism is inhibited by depleted resources \parencite{violle2009competition}.
+For resource competition in particular, competitive effects are determined by how the organism affects local resource availability while competitive responses are determined by how the organism is inhibited by depleted resources \parencite{violle2009competition}.
 As such, the best groupings of species may be different for each of the effects and responses.
@@
 We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
-Data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
+Such data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
 In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
-We fit a Lotka--Volterra model to these data to find the groupings that give the most parsimonious model, and compare these groupings to similarity based upon a species trait (body size).
-While doing so, we group species independently with regard to their effects upon other species and their responses to other species, to find whether the data-informed groupings differ between these two cases.
+We fit a Lotka--Volterra competition model to these data to find the groupings that give the most parsimonious model, and we then compare these groupings to similarity based upon a species trait (body size).
+While doing so, we group species independently with regard to their effects upon other species and their responses to other species to find whether the data-informed groupings differ between these two cases.
 
@@
 
-The data we used in this study were drawn from the work of \textcite{terry2021natural}.
-The data consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-This experimental design corresponds to a response--surface experimental design commonly used to parameterise a species interaction model \parencite{hart2018quantify,zhang2019common,cameron2019size}.
+The data used in this study were drawn from the work of \textcite{terry2021natural}.
+They consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
+This experimental design corresponds to a response--surface experimental design commonly used to parameterise species interactions in population dynamics models \parencite{hart2018quantify,zhang2019common,cameron2019size}.
 
@@
 
+% DBS: Wait, the response is pairs? So can we have non-integer responses?
+
 Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
@@
 \begin{equation}
-	N_{i,t+1} - N_{i,t} = N_{i,t} \, r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right) \,,
+	N_{i,t+1} - N_{i,t} = N_{i,t} \, r_i \left(1 - \sum_j^n \alpha_{ij} N_{j,t}\right) \,,
 	\label{eq:lv-model}
@@
 where $N_{i,t}$ is the population of species $i$ at time $t$ (the size of the parent generation), $N_{i,t+1}$ is the population at time $t+1$ (the size of the offspring generation), $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the per capita effect of species $j$ on species $i$.
-The competition coefficients were not constrained to be positive, allowing for the possibility of mutualistic effects between some species.
+When fitting the data to the model, the competition coefficients were not constrained to be positive; this allows for the possibility of mutualistic effects between some species.
 With $n$ species, this model has $n+n^2$ parameters: $n$ growth rates and $n^2$ competition coefficients.
+
+% DBS: A tardy thought, if we don't constrain alphas I believe many people would say we should claim that we are fitting the generalised Lotka--Volterra model and *not* a Lotka--Volterra competition model.
 
@@
 Given $n$ species, there may be any integer number of groups from $1$ to $n$.
-Groupings are known formally as partitions in mathematics, and the total number of groupings for $n$ species is given by the Bell numbers, denoted $B_n$ \parencite{bell1934exponential}.
+Groupings are known formally as partitions in mathematics, and the total number of ways to group $n$ species is given by the Bell number, denoted $B_n$ \parencite{bell1934exponential}.
 
 It is commonly assumed that species which are similar in their responses to competition would automatically be similar in their competition effects.
-However, competitive responses may be governed by a different set of traits than competitive effects, so this assumption does not necessarily hold.
-We avoided this assumption by allowing species which were similar in one regard to be dissimilar in the other, and vice versa.
-As such, each model was defined by two groupings of species: one grouping of the competitive responses, and one of the competitive effects.
+However, competitive responses may be governed by a different set of traits than competitive effects, so this assumption may not always hold.
+We therefore relaxed this assumption by allowing species which were similar in one regard to be dissimilar in the other, and vice versa.
+As such, each grouped model was defined by two groupings of species: one grouping of the competitive responses and one of the competitive effects.
 
-To better understand the meaning of species grouping of competition coefficients, it is useful to recognise that this component of the Lotka--Volterra model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
-As such, if two species are assumed to have the same response to competition, then two rows of the interaction matrix are constrained to be equal.
-Similarly, if two species are assumed to have the same competitive effect, then two columns of the interaction matrix are constrained to be equal.
+To better understand the meaning of species grouping of competition coefficients, it is useful to recognise that this component of the Lotka--Volterra competition model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
+If two species are assumed to have the same responses to competition, then two rows of the interaction matrix are constrained to be equal.
+Similarly, if two species are assumed to have the same competitive effects, then two columns of the interaction matrix are constrained to be equal.
 This allows us to refer below to the grouping of the competitive responses as the ``row grouping'' and the grouping of the competitive effects as the ``column grouping''.
@@
 First, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the fully ungrouped model.
-Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
+Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the models grouping species equivalently in their competitive effects and competitive responses were more parsimonious than all other models.
 To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
@@
 However, we could test the row-grouping and column-grouping coclassification matrices against one another.
-By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could perform a different test regarding the assumption that it is appropriate to use the same grouping for both.
+By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could perform a second test of the assumption that it is appropriate to use the same grouping for both.
 We did this using a Mantel test, as appropriate for similarity matrices.
@@
 We calculated one such dissimilarity matrix based on a species trait: body size (as mean wet mass of female adults, obtained from \cite{terry2021natural}).
-The trait difference matrix was calculated as absolute difference between trait values, while the coclassification matrices were converted to dissimilarity matrices by subtracting them from $1$.
-We then performed Mantel tests for correlation between the trait distance matrix and each of the two coclassification dissimilarity matrices.
+The trait difference matrix was calculated as absolute difference between trait values while the coclassification matrices were converted to dissimilarity matrices by subtracting them from $1$.
+We then performed Mantel tests for correlation between the trait distance matrix and each of the row-grouping and column-grouping coclassification dissimilarity matrices.
 
@@
 
-% DBS: Semi-random thought: should we also add the "all alphas = 0" model to the mix?
+% DBS: We need to add a reference to the partial residual plots in the supps.
 
@@
 \begin{figure}
+	\centering
+	\begin{subfigure}{0.65\textwidth}
 	<<>>=
@@
 			xaxs='i',
-			yaxs='i'
+			yaxs='i',
+			ylim=c(0,6000)
 		)
-		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
+		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dotted", col="green")
 		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dashed", col="red")
 	@
+	\end{subfigure}
 
 	\caption{%
-		Histogram of the {\ic} values of Lotka--Volterra model fit with all possible groupings of interaction coefficients.
-		The green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
-		The red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
+		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
+		The dotted green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
+		The dashed red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
 	}
@@
 \end{figure}
+% DBS: Reconsider green and red to be more colour-blind friendly. I've already changed it so that the lines are different types.
 
@@
 The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; this was more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
-This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
+This indicates that the most parsimonious model was not especially likely to be one that grouped the rows and columns equivalently.
 
@@
 		@
-		\caption{The grouped alpha matrix.}
+		\caption{Grouped alpha matrix}
 		\label{fig:best-alpha-matrix}
@@
 		@
-		\caption{The coclassification matrix of rows.}
+		\caption{Coclassification matrix of rows}
 		\label{fig:best-coclassification-cols}
@@
 		@
-		\caption{The coclassification matrix of columns.}
+		\caption{Coclassification matrix of columns}
 		\label{fig:best-coclassification-rows}
@@
 		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
-		This represents the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
-		\Subref{fig:best-alpha-matrix} shows the competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions, per the groupings.
-		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} show the coclassification matrices derived from the groupings of the columns and rows respectively.
-		These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
-		Species have been reordered that species which are grouped together appear adjacent.
-		The ordering is the same in \subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} as shown in \subref{fig:best-alpha-matrix}.
+		Where results are for the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
+		\Subref{fig:best-alpha-matrix} We show the inferred matrix of competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions (per the identified groupings).
+		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} We show the coclassification matrices derived from the groupings of the columns and rows, respectively.
+		%These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
+		Species have been reordered so that species that were grouped together appear adjacent, and the ordering is the same in all of \subref{fig:best-alpha-matrix}, \subref{fig:best-coclassification-cols}, and \subref{fig:best-coclassification-rows}.
 	}
@@
 
+% DBS: I cut out a sentence above in the caption because we say this in the text elsewhere and it's a bit unusual to refer to a later figure in the caption of an earlier one.
+
 \subsection{Coclassification of species}
 
-Overall, no pair of species can confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent} (\cref{fig:coclassification}).
+Overall, no pair of species could confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent} (\cref{fig:coclassification}).
 However, some pairs of species were far more likely to be coclassified than others, suggesting some structure to the best groupings.
 
-The structure of the coclassifications was very different in the row groups than in the column groups.
-Most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
+The structure of the coclassification matrices was very different in the row groups than in the column groups.
+That is, most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
 Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
 Overall, more coclassification occurred in the row groupings than in the column groupings.
-A Mantel test of the coclassification matrix for the rows against that for the columns shows that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
+A Mantel test of the coclassification matrix for the rows against that for the columns showed that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
 
@@
 
-% DBS: Most journals frown upon or do not allow overly verbose subtitles on figures. So I've cut them down to be a bit more concise.
 % DBS: But the fact that the labels say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
@@
 ;)
+
+% DBS: Adding a new note here. Shouldn't we pick one version that gets used in Fig 2 and in Fig 3 to refer to the two coclassification matrices?
+
 \begin{figure}
@@
 		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
-		\Subref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \subref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
+		\Subref{fig:coclassification-cols} We show the grouping of species' competitive effects upon other species (columns of the interaction matrix).
+\subref{fig:coclassification-rows} We show the grouping of species' responses to competition (rows of the interaction matrix).
 	}
@@
 
-% DBS: I think a good figure would be to show the ungrouped estimated alpha matrix in one panel and the alpha matrix averaged across all partitions in a second panel, with lines drawn in the second to reflect the "optimal" partitioning of the co-classification matrices.
-
 \section{Discussion}
@@
 We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
-Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}) than leaving them ungrouped.
+Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}) than was leaving them ungrouped.
 Which grouping would give the most parsimonious model, however, could not be determined with confidence.
 This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds,kirwan2009diversity,boulangeat2012improving}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic,wilcox2018evolutionary}.
-It also contrasts with previous studies that have succeeded in finding clear groups in other ecological contexts, such as in food webs \parencite{krause2003compartments,allesina2009food} and pollination networks \parencite{olesen2007modularity}.
+It also contrasts with previous studies that have succeeded in finding clear groups in other ecological contexts, such as in food webs \parencite{krause2003compartments,allesina2009food} or plant--pollinator networks \parencite{olesen2007modularity}.
 
-One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
-That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
+One possible explanation for our results is that species simply do not group to the same extent in a quantitative competitive context as in a binary interaction networks.
+That said, the results also suggest that this is unlikely as grouping was useful for increasing parsimony.
 In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
 All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
-A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
+A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown less equivocal groupings.
 Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
-Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
+Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing an application of this approach to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
 As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
 
-While the results could not definitely show the best grouping, it was clear that the appropriate grouping differed for the rows and columns.
+While the results could not definitely identify a single best grouping, it was clear that the model-supported groupings differed for the rows and columns.
 That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
-This should not be surprising, for it is known that different traits govern species competitive effects than their responses \parencite{goldberg1991competitive}.
+In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1991competitive}.
+% DBS: I think it would be good to find another reference here.
+Maybe this one?
+https://onlinelibrary.wiley.com/doi/10.1111/j.1365-2486.2008.01557.x
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
-Our results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.
+Our results recommend more explicit questioning, and even testing, of this assumption when building future species interaction models.
 %TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
 
+% DBS: Can we replace "in some instances" below with something a bit more explicit? Do we mean "for some sets of species"?
 The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
 A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
-This could suggest that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
+% DBS: Should we consider replacing "ecological niches" above with "competitive niches"?
+This could indicate that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
 Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.

### 2022-06-02 article.rnw
a few more minor tweaks

@@
 
-One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}, and setting any individual parameter to zero risks losing important information.
-Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
+One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives, weiss2021disentangling}.
+However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}.
+Setting any individual parameter to zero thus risks losing important information; moreover, we often do not know with confidence which parameters are likely to be zeros and which are not.
+Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species}.
 
@@
 
-% DBS: We need to add a reference to the partial residual plots in the supps.
+% DBS: As per my comment immediately above, we need to add a reference to the partial residual plots in the supps.
 

### 2022-06-03 article.rnw
shuffled one more sentence
Interchange the dashing and dotting of the lines on the histogram.
The dotted green line was hard to read (a combination of the pale green
and the small dots). Both green dashes and red dots are easy enough to see.

@@
 		)
-		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dotted", col="green")
-		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dashed", col="red")
+		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
+		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="red")
 	@
@@
 		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
-		The dotted green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
-		The dashed red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
+		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
+		The dotted red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
 	}
@@
 A Mantel test of the coclassification matrix for the rows against that for the columns showed that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
+Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
 
@@
 
-Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
-
-% DBS: But the fact that the labels say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
+% DBS: But the fact that the labels in figure 3 say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
 We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects.

### 2022-06-03 article.rnw
Change values from being in breeding pairs to individuals.
Specify that initial densities are given in breeding pairs.
That sentence uses the word "pair" three times to refer to two different things:
breeding pairs, or pairs of species. Specifying that the first use is
breeding pairs should help lessen confusion.

@@
 A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
-The number of adult pairs of each species emerging from these eggs was counted.
-
-% DBS: Wait, the response is pairs? So can we have non-integer responses?
+The number of adults of each species emerging from these eggs was counted.
 
@@
 The single-species densities were 3, 9, or 12 pairs per vial, and each of these was replicated six times per species.
-The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
+The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) breeding pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
 Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.

### 2022-06-13 src/rjsolver.cpp
Correct spelling.

@@ -236,7 +236,7 @@ Eigen::VectorXd ReversibleJumpSolver::getResiduals() {
 
 double ReversibleJumpSolver::getLikelihoodRatio(Eigen::VectorXd sourceResiduals, Eigen::VectorXd destResiduals, double sourceErrorVariance, double destErrorVariance) {
 	//Having a getLikelihood() function and calling it for source and destination
-	//just results in it returning 0 twice, as it multiplies several hundred small numbers together, and gts too small.
+	//just results in it returning 0 twice, as it multiplies several hundred small numbers together, and gets too small.
 	//So we must calculate the likelihood ratio, getting the ratio as we go.
 	double likelihoodRatio = 1.0;
 	for(size_t i = 0; i < (size_t)sourceResiduals.size(); i++) {

### 2022-06-13 article.rnw
Change the lines in the histogram to be more colourblind-friendly.
Green and purple instead of green and red.

@@
 		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
-		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="red")
+		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
 	@
@@
 		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
-		The dotted red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
+		The dotted purple line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
 	}
@@
 \end{figure}
-% DBS: Reconsider green and red to be more colour-blind friendly. I've already changed it so that the lines are different types.
 

### 2022-06-13 article.rnw
Remove a commented-out sentence.
Clarify "in some instances" to "for some sets of species".

@@
 		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} We show the coclassification matrices derived from the groupings of the columns and rows, respectively.
-		%These coclassification matrices are averaged for all models, weighted by Akaike weights, to produce \cref{fig:coclassification}.
 		Species have been reordered so that species that were grouped together appear adjacent, and the ordering is the same in all of \subref{fig:best-alpha-matrix}, \subref{fig:best-coclassification-cols}, and \subref{fig:best-coclassification-rows}.
@@
 \end{figure}
-
-% DBS: I cut out a sentence above in the caption because we say this in the text elsewhere and it's a bit unusual to refer to a later figure in the caption of an earlier one.
 
@@
 
-% DBS: Can we replace "in some instances" below with something a bit more explicit? Do we mean "for some sets of species"?
-The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
+The intransitivity of coclassification for some sets of species even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
 A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.

### 2022-06-13 article.rnw
Replace "ecological niches" with "competitive niches".

@@
 The intransitivity of coclassification for some sets of species even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-A single trait like body size might therefore not be able to capture the multivariate nature of species' ecological niches \parencite{blonder2018hypervolume}.
-% DBS: Should we consider replacing "ecological niches" above with "competitive niches"?
+A single trait like body size might therefore not be able to capture the multivariate nature of species' competitive niches \parencite{blonder2018hypervolume}.
 This could indicate that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.

### 2022-06-14 article.rnw
Add another reference regarding how different traits govern responses than effects.
I haven't used the reference Daniel suggested, as that wasn't dealing with
*competitive* effect and response, but with response to environmental change
and effect on ecosystem processes. However, it did direct me to the
reference I used.

@@
 That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
-In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1991competitive}.
-% DBS: I think it would be good to find another reference here.
-Maybe this one?
-https://onlinelibrary.wiley.com/doi/10.1111/j.1365-2486.2008.01557.x
+In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1990components, goldberg1991competitive}.
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.

### 2022-07-01 r/grouped-matrix.R
Reimplement get_all_orderings() in native R, not Rcpp.
Rcpp functions can't be saved to an rda file.

@@ -25,17 +25,48 @@ is_consecutive_blocks <- function(grouping) {
 forms_consecutive_blocks <- function(grouping, ordering) {
 	is_consecutive_blocks(grouping[ordering])
 }
-#Third, another helper function to get a list of all orderings.
-#In C++, to make use of std::next_permutation().
-Rcpp::cppFunction("List get_all_orderings(int n) {
-	List all_orderings = List::create();
-	std::vector<int> ordering(n);
-	for(int i = 0; i < n; i++) ordering[i] = i+1;
-	do {
-		all_orderings.push_back(NumericVector::import(ordering.begin(), ordering.end()));
-	} while(std::next_permutation(ordering.begin(), ordering.end()));
-	return all_orderings;
-}")
+#Next, we need another helper function to get a list of all orderings.
+#Ordinarily, I would do this in C++, to make use of std::next_permutation().
+#However, you can't conveniently save an Rcpp function to an rda file.
+#So, third, I implement next_permutation in R.
+next_permutation <- function(perm) {
+	#Using the linear-time implementation described here: https://wordaligned.org/articles/next-permutation
+	#First, check that the vector is long enough to have permutations.
+	if(length(perm) < 2) return(perm)
+	#Second, find the longest monotonically decreasing tail.
+	head_of_tail <- NA
+	for(i in (length(perm)-1):1) {
+		if(perm[i+1] > perm[i]) {
+			head_of_tail <- i+1
+			break
+		}
+	}
+	#If head_of_tail is NA, the entire permutation is monotonically decreasing, just reverse it.
+	if(is.na(head_of_tail)) {
+		return(perm[length(perm):1])
+	}
+	#Else, swap the end of the head with the the last element of the tail that is greater than it.
+	temp <- perm[head_of_tail-1]
+	for(i in length(perm):head_of_tail) {
+		if(perm[i] > temp) {
+			perm[head_of_tail-1] <- perm[i]
+			perm[i] <- temp
+			break
+		}
+	}
+	#Reverse the tail.
+	perm[head_of_tail:length(perm)] <- perm[length(perm):head_of_tail]
+	return(perm)
+}
+#Fourth, another helper function to get a list of all orderings.
+get_all_orderings <- function(n) {
+	all_orderings <- vector("list", factorial(n))
+	all_orderings[[1]] <- 1:n
+	for(i in 2:length(all_orderings)) {
+		all_orderings[[i]] <- next_permutation(all_orderings[[i-1]])
+	}
+	return(all_orderings)
+}
[…]

### 2022-07-01 article.rnw
Fix an error in the subcaptiosn of the best alpha matrix figure.
I had the captions of the row and column coclassification matrices interchanged.
Standardise the subcaptions of coclassification matrix figures.
In one figure it was rows/columns; in the other it was effects/responses.
Now both are effects/responses, with rows/columns in brackets where necessary.
Move the heavy analysis currently in the rnw file into a separate R script which saves an rda.
This speeds up compilation, by not requiring all the analysis to be rerun
every time the wording of the article changes.
It also allows the sa

@@
 <<include=FALSE>>=
-	source("r/parameters.R")
-	source("r/input-data.R")
-	source("r/post-process.R")
-	source("r/brute-post-process.R")
-	source("r/mantel-test.R")
-	source("r/dist-matrix.R")
-	source("r/coclassification-table.R")
-	source("r/grouped-matrix.R")
-
-	species_dat <- read.csv("data/species.csv")
-	species_output_order <- c(4,3,1,2,6,5)
-
-	input_data <- InputData$new("output/focal-vector.data", "output/response-vector.data", "output/design-matrix.data", is_per_capita=TRUE)
-
-	num_species <- input_data$num_species
-	num_obs <- input_data$num_obs
-
-	ic <- "aicc" #The information criterion to use, e.g. "aic" or "aicc"
-	ic_weight <- sprintf("%s_weight", ic)
-	ic_name <- list(aic="AIC", aicc="AICc")[[ic]]
-
-	brute_data <- BruteData$new("output/brute.data", species_dat$name, ic_weight)
-
-	#Precalculate the coclassification matrices, as these are active bindings and the slowest part of compilation.
-	weighted_col_coclassification_matrix <- brute_data$weighted_col_coclassification_matrix
-	weighted_row_coclassification_matrix <- brute_data$weighted_row_coclassification_matrix
-
-	#Precalculate distances matrices as well.
-	col_distance_matrix <- 1 - weighted_col_coclassification_matrix
-	row_distance_matrix <- 1 - weighted_row_coclassification_matrix
-	body_weight_distance_matrix <- build_dist_matrix(species_dat$name, species_dat$body_weight, function(w1,w2){abs(w1-w2)})
+	library(magrittr)
+	load("output/article-data.rda")
 @
@@
 		@
-		\caption{Coclassification matrix of rows}
+		\caption{Coclassification of competitive effects\\(columns)}
 		\label{fig:best-coclassification-cols}
@@
 		@
-		\caption{Coclassification matrix of columns}
+		\caption{Coclassification of competitive responses\\(rows)}
 		\label{fig:best-coclassification-rows}
@@
 ;)
-
-% DBS: Adding a new note here. Shouldn't we pick one version that gets used in Fig 2 and in Fig 3 to refer to the two coclassification matrices?
 

### 2022-07-26 article.rnw
Extract the article preamble into a separate file.
Much of the preamble will be duplicated for the supplementary,
so this prevents code duplication.

@@
 \documentclass[12pt,titlepage]{article}
-\usepackage{amsmath}
-\usepackage{siunitx}
-\usepackage{import}
-\usepackage{authblk}
 
-%Images & tables
-\usepackage{subcaption}
-\usepackage{pgfplots}
-\usepackage{colortbl}
-\usepackage{multirow}
-\usepackage{arydshln}
-
-\captionsetup{subrefformat=parens} %Changes only \subref, not \ref.
-\let\Subref\subref
-%TODO: Make \cref figure out if it should be a subref, and use cref throughout.
-
-%Journal font & paper requirements
-\usepackage{newtxtext} %Times New Roman
-\usepackage[letterpaper,margin=1in]{geometry}
-
-%Preprint
-\usepackage{lineno} \linenumbers
-\usepackage{setspace} \doublespacing
-\usepackage[nomarkers,tablesfirst,notablist,nofiglist]{endfloat}
-\addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.
-
-%Ensure title page is numbered, as journal style requires it.
-%Using https://tex.stackexchange.com/a/172005, adapted not to bother with two column stuff.
-\makeatletter
-\renewenvironment{titlepage}{\thispagestyle{plain}}{\newpage}
-\makeatother
-
-%Referencing
-\import{reference-styles/}{ecology.tex}
-\addbibresource{bibliography/references.bib}
-\addbibresource{references.bib}
-\usepackage{placeins} %Provides \FloatBarrier
-
-\usepackage{hyperref}
-\usepackage{cleveref}
-
-%Title Page
-\title{Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
-\author{Christopher R.\ P.\ Brown}
-\author{Daniel B.\ Stouffer}
-\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
-\date{}
-
-<<include=FALSE>>=
-	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
-	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
-	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
+<<preamble,child="preamble.rnw">>=
 @
-
-<<include=FALSE>>=
-	library(magrittr)
-	load("output/article-data.rda")
-@
-
-\newcommand\ic{\Sexpr{ic_name}}
-
-\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
-\newcommand\icnum[1]{\num[round-mode=places,round-precision=2]{#1}} %For information criteria.
-\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
-\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}
-
-\newcommand\mantelstat{\ensuremath{r_{\text{M}}}}
-
-\newcommand\keywords[1]{\emph{Key words: #1}}
-
-\pgfplotsset{%
-	colormap={coclassification}{color=(white) color=(red)}
-}
-\colorlet{coclassification diagonal}{black!20}
 

### 2022-07-26 preamble.rnw
Extract the article preamble into a separate file.
Much of the preamble will be duplicated for the supplementary,
so this prevents code duplication.

\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{import}
\usepackage{authblk}

%Images & tables
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{arydshln}

\captionsetup{subrefformat=parens} %Changes only \subref, not \ref.
\let\Subref\subref
%TODO: Make \cref figure out if it should be a subref, and use cref throughout.

%Journal font & paper requirements
\usepackage{newtxtext} %Times New Roman
\usepackage[letterpaper,margin=1in]{geometry}

%Preprint
\usepackage{lineno} \linenumbers
\usepackage{setspace} \doublespacing
\usepackage[nomarkers,tablesfirst,notablist,nofiglist]{endfloat}
\addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.

%Ensure title page is numbered, as journal style requires it.
%Using https://tex.stackexchange.com/a/172005, adapted not to bother with two column stuff.
\makeatletter
\renewenvironment{titlepage}{\thispagestyle{plain}}{\newpage}
\makeatother

%Referencing
\import{reference-styles/}{ecology.tex}
\addbibresource{bibliography/references.bib}
\addbibresource{references.bib}
\usepackage{placeins} %Provides \FloatBarrier

\usepackage{hyperref}
\usepackage{cleveref}

%Title Page
\title{Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{Christopher R.\ P.\ Brown}
\author{Daniel B.\ Stouffer}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

<<include=FALSE>>=
	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
@

<<include=FALSE>>=
	library(magrittr)
	load("output/article-data.rda")
@

\newcommand\ic{\Sexpr{ic_name}}

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\icnum[1]{\num[round-mode=places,round-precision=2]{#1}} %For information criteria.
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

\newcommand\mantelstat{\ensuremath{r_{\text{M}}}}

\newcommand\keywords[1]{\emph{Key words: #1}}

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}

### 2022-07-26 supp.rnw
Add the as-yet-empty supplementary.

--- 2022-07-26 article.rnw
@@
 
-\section*{Abstract}
-
-Most dynamic models of ecological communities require many parameters, making them expensive to fit to experimental or observational data.
-To reduce the number of parameters, species are often divided into groups \emph{a priori}, using phylogenetic or functional groups, and species within a group are assumed to behave identically.
-Here, we assess the validity of such grouping by deriving the optimal groupings \emph{a posteriori} based on the fit of the Lotka--Volterra competition model to experimental data from six species of \emph{Drosophila} competing in laboratory conditions.
-We find evidence that grouping can improve the parsimony of species interaction models, but we also observe that there is no single optimal grouping.
-Further, those groupings that did prove beneficial could not have been easily predicted from available species attributes, calling into question the prevailing method of \emph{a priori} species grouping.
-Lastly, we find that species did not group equivalently in their competitive effect and in their response to competition, invalidating a key assumption often made implicitly when defining species groupings.
-Our study suggests the need for a different, more data-informed, approach to grouping in species interaction models.
-
-% DBS: Once we have a title, make sure that we remove all words from the keywords that appear there.
-\keywords{competition; ecological equivalence; grouping; model fitting; parsimony; \emph{Drosophila}}
-
-\section{Introduction}
-
-Models have long been used in community ecology \parencite{lotka1925elements}.
-They allow us to make predictions about things we cannot directly observe, be it the response of a community to novel pressures \parencite{novak2016characterizing} or the stability of an entirely novel assemblage \parencite{maynard2020predicting}.
-The ability to make these predictions is becoming increasingly important as global change accelerates, introducing alien species and applying climatic or other anthropogenic pressures to communities worldwide \parencite{gilman2010framework,sutherst2007including}.
-
-Making practical use of a model requires experimentally or observationally determining the values of each of the model's parameters.
-This poses a particular problem for models that include species interactions due to the sheer number of parameters that must be determined.
-Even the simplest models with no environmental dependence require one parameter to characterise the interaction of each pair of species \parencite{novak2016characterizing,rocha2005lotka}.
-Hence the number of parameters scales quadratically with the number of species; at least \num{100} parameters are required for the interactions in a community of ``just'' \num{10} species.
-Determining these parameters experimentally requires at least one experiment per parameter, and preferably more \parencite{hart2018quantify}.
-This is understandably expensive and requires substantial effort.
-As such, model-based predictions of real communities are typically restricted to a small number of focal species \parencite{ovaskainen2017species,maynard2020predicting}.
-However, real communities can contain hundreds of species \parencite{cornell1999unsaturation}, or even thousands for microbial communities assessed by genetic metabarcoding \parencite{warton2015variables}.
-To bridge this gap between the size of real communities and our ability to parameterise models for them, we need an ecologically-defensible way to reduce the number of parameters that predictive models require.
-
-One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives, weiss2021disentangling}.
-However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}.
-Setting any individual parameter to zero thus risks losing important information; moreover, we often do not know with confidence which parameters are likely to be zeros and which are not.
-Another approach assumes that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species}.
-
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional (i.e., trait) similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
-The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic,webb2002phylogenies,darwin1859origin}.
-%Darwin Chapter 3 "Struggle for Life Most Severe Between Individuals and Varieties of the Same Species".
-However, empirical tests of this principle have found remarkably little support for it \parencite{godoy2014phylogenetic,cahill2008does,mayfield2010opposing}.
-On the other hand, functional groupings have also proven to be poor predictors of species interactions \parencite{bret2008plant,funk2017revisiting}.
-While attempts have been made to define functional groupings that are more useful in a modelling context \parencite{boulangeat2012improving}, these rely upon measurements of biotic interactions to define such groups.
-As such, integrating these into species interaction models leaves us with a circular argument: a functional group is a group of species that interact with others in a similar way, and we therefore assume that all the species in a functional group interact with others in a similar way.
-In all, we are left with the question of how best to group species in community models, and whether we can do so in a meaningful way using less data than required for a fully pairwise parameterisation.
-
-To the best of our knowledge, all studies that use grouping to simplify models of species interactions have also made one additional, untested assumption: that the same grouping is equally valid for how species affect others as for how species respond to others.
-There is good reason to question this assumption, as it is known that different traits can govern species' competitive effects than govern their responses to competition \parencite{goldberg1991competitive}.
-For resource competition in particular, competitive effects are determined by how the organism affects local resource availability while competitive responses are determined by how the organism is inhibited by depleted resources \parencite{violle2009competition}.
-As such, the best groupings of species may be different for each of the effects and responses.
-
-We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
-Such data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
-In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
-We fit a Lotka--Volterra competition model to these data to find the groupings that give the most parsimonious model, and we then compare these groupings to similarity based upon a species trait (body size).
-While doing so, we group species independently with regard to their effects upon other species and their responses to other species to find whether the data-informed groupings differ between these two cases.
-
-\section{Methods}
-
-\subsection{Data}
-
-The data used in this study were drawn from the work of \textcite{terry2021natural}.
-They consist of fecundity measurements---number of surviving offspring---for six species of \emph{Drosophila}, grown in single-species or two-species communities with varying densities of each species.
-This experimental design corresponds to a response--surface experimental design commonly used to parameterise species interactions in population dynamics models \parencite{hart2018quantify,zhang2019common,cameron2019size}.
-
-\subsubsection{Summary of the experimental methodology}
-
-The experiment used six species of \emph{Drosophila} from an Australian rainforest community: \emph{D.
-birchii}, \emph{D.
-pallidifrons}, \emph{D.
-pandora}, \emph{D.
-pseudoananassae}, \emph{D.
-simulans}, and \emph{D.
-sulfurigaster}.
-The experiment took place in vials with a limited amount of medium for egg-laying and larval development; competition was for space on this medium.
-A fixed number of adult pairs of one or two species were added to each vial and allowed to mate and lay eggs.
-The number of adults of each species emerging from these eggs was counted.
-
-Experiments occurred for every single-species and two-species combination of the six species, at a variety of densities.
-The single-species densities were 3, 9, or 12 pairs per vial, and each of these was replicated six times per species.
-The two-species densities were (3,3), (3,6), (3,9), (3,12), (6,3), (9,3), or (12,3) breeding pairs per vial (where the paired values give the densities of each of the two species), and each of these was replicated three times per pair of species.
-Vials with a single founding pair were excluded from this study and the original authors' due to an Allee effect that the Lotka--Volterra model cannot accommodate.
-Further details of the experimental methodology can be found in \textcite{terry2021natural}.
-
-\subsection{Model}
-
-The data provided the change in population size from one generation to the next, so we used a discrete-time version of the Lotka--Volterra competition model given by:
-\begin{equation}
-	N_{i,t+1} - N_{i,t} = N_{i,t} \, r_i \left(1 - \sum_j^n \alpha_{ij} N_{j,t}\right) \,,
-	\label{eq:lv-model}
-\end{equation}
-where $N_{i,t}$ is the population of species $i$ at time $t$ (the size of the parent generation), $N_{i,t+1}$ is the population at time $t+1$ (the size of the offspring generation), $r_i$ is the intrinsic growth rate of species $i$, and $\alpha_{ij}$ is the per capita effect of species $j$ on species $i$.
-When fitting the data to the model, the competition coefficients were not constrained to be positive; this allows for the possibility of mutualistic effects between some species.
-With $n$ species, this model has $n+n^2$ parameters: $n$ growth rates and $n^2$ competition coefficients.
-
-% DBS: A tardy thought, if we don't constrain alphas I believe many people would say we should claim that we are fitting the generalised Lotka--Volterra model and *not* a Lotka--Volterra competition model.
-
-% DBS: We might want to be prepared for reviewers asking us to change from a linear LV model.
-
-\subsubsection{Species grouping}
-
-In order to reduce the number of free parameters in the model, we grouped species together, and constrained the appropriate competition coefficients to be equal for species within the same group.
-Within the model defined above, each species is effectively in its own group, such that all pairs of species interact in a unique fashion.
-At the other extreme, all species could be placed in the same group, such that all pairs of species interact equivalently; they are ecologically equivalent \emph{sensu} \textcite{mcpeek2019disentangling}.
-Given $n$ species, there may be any integer number of groups from $1$ to $n$.
-Groupings are known formally as partitions in mathematics, and the total number of ways to group $n$ species is given by the Bell number, denoted $B_n$ \parencite{bell1934exponential}.
-
-It is commonly assumed that species which are similar in their responses to competition would automatically be similar in their competition effects.
-However, competitive responses may be governed by a different set of traits than competitive effects, so this assumption may not always hold.
-We therefore relaxed this assumption by allowing species which were similar in one regard to be dissimilar in the other, and vice versa.
-As such, each grouped model was defined by two groupings of species: one grouping of the competitive responses and one of the competitive effects.
-
-To better understand the meaning of species grouping of competition coefficients, it is useful to recognise that this component of the Lotka--Volterra competition model can be represented as an interaction matrix \parencite{novak2016characterizing}, where a row contains all the competitive effects on a single species and a column contains all the competitive effects of a single species.
-If two species are assumed to have the same responses to competition, then two rows of the interaction matrix are constrained to be equal.
-Similarly, if two species are assumed to have the same competitive effects, then two columns of the interaction matrix are constrained to be equal.
-This allows us to refer below to the grouping of the competitive responses as the ``row grouping'' and the grouping of the competitive effects as the ``column grouping''.
-Formally, if species $a$ and $b$ were in the same row group, $\alpha_{aj}\equiv\alpha_{bj} \, \forall j$, and if $a$ and $b$ were in the same column group, $\alpha_{ia}\equiv\alpha_{ib} \, \forall i$.
-
-With six species and independently selected row and column groupings, the total number of possible models is ${\left(B_6\right)}^2 = \num{\Sexpr{numbers::bell(6)^2}}$.
-The species' intrinsic growth rates, $r_i$, were not affected by grouping; each species always had its own growth rate fitted independently of other species.
-The total number of parameters in the model is reduced to $n$ growth rates, and a number of competition coefficients equal to the number of row groups multiplied by the number of column groups.
-
-\subsubsection{Model fitting}
-
-The Lotka--Volterra competition model in \cref{eq:lv-model} is not linear in the parameters.
-With the rows of the interaction matrix ungrouped, the regression could be reparameterised to be linear in the parameters by treating $r_i \alpha_{ij}$ as a single regression parameter for each $i,j$ pair.
-With the rows grouped, however, this becomes impossible since each species still has an independent growth rate.
-As such, we instead fit the models with the Gauss--Newton method for non-linear least squares and assumed a normal error distribution of the response variable.
-To prevent heteroskedasticity and improve normality, we transformed total population growth to per capita population growth, which corresponds to the following model:
-\begin{equation}
-	\frac{N_{i,t+1} - N_{i,t}}{N_{i,t}} = r_i \left(1 - \sum_j \alpha_{ij} N_{j,t}\right) \,.
-\end{equation}
-
-\subsubsection{Assessing parsimony}
-
-To assess the parsimony of the different species groupings, we exhaustively fit all \num{\Sexpr{numbers::bell(6)^2}} possible models and computed the resulting {\ic} for those fits.
-As a measure of parsimony, we selected AICc over BIC on the basis that we want to find the best model for making ecological predictions rather than seeking the ``true'' model \parencite{aho2014model}.
-Furthermore, AICc is more conservative in promoting grouping as BIC imposes a greater penalty for the number of parameters for any reasonably sized data set.
-Some of the models had a relatively high number of parameters compared to the number of observations (\num{\Sexpr{num_obs}} observations compared to up to \num{\Sexpr{num_species + num_species^2}} parameters), so we used AICc to correct for this ``small sample size'' effect.
-{\ic} values can be compared to determine which model is the most parsimonious, but they cannot directly be interpreted to find the significance of the difference in parsimony.
-As such, we also converted the set of {\ic} values to Akaike weights \parencite{wagenmakers2004aic}.
-These give the probability that each model is the best among the models assessed.
-
-Using these Akaike weights, we calculated two important statistics.
-First, the total Akaike weight of models with a lower {\ic} than the entirely ungrouped model; this is the probability that some model is more parsimonious than the fully ungrouped model.
-Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the models grouping species equivalently in their competitive effects and competitive responses were more parsimonious than all other models.
-To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
-
-\subsubsection{Coclassification matrices}
-
-To summarise the results, we also used the Akaike weights to generate two coclassification matrices, one for the row groupings and one for the column groupings.
-Each cell of a coclassification matrix represents the coclassification of a pair of species, and contains the total Akaike weight of models that place those two species in the same group.
-As such, each cell represents the probability that the most parsimonious model is one that coclassifies those two species.
-For reference, note that the diagonal of a coclassification matrix is tautologically equal to $1$.
-
-There are a number of possible ``null'' expectations for the off-diagonal elements these matrices.
-A neutral model approach would expect all species to be in the same group: every off-diagonal cell would therefore be $1$.
-If each species were expected to be unique, every off-diagonal cell would instead be $0$.
-Alternatively, if every possible grouping were considered to be equally likely, every off-diagonal cell would be $\frac{B_{n-1}}{B_n}$: \probnum{\Sexpr{numbers::bell(5)/numbers::bell(6)}} for six species.
-Unfortunately, without a null \emph{distribution} of coclassification matrices, it was impossible to test the data-informed coclassification matrices against a null expectation.
-
-However, we could test the row-grouping and column-grouping coclassification matrices against one another.
-By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could perform a second test of the assumption that it is appropriate to use the same grouping for both.
-We did this using a Mantel test, as appropriate for similarity matrices.
-We could also test the coclassification matrices for correlation with an expected dissimilarity matrix.
-We calculated one such dissimilarity matrix based on a species trait: body size (as mean wet mass of female adults, obtained from \cite{terry2021natural}).
-The trait difference matrix was calculated as absolute difference between trait values while the coclassification matrices were converted to dissimilarity matrices by subtracting them from $1$.
-We then performed Mantel tests for correlation between the trait distance matrix and each of the row-grouping and column-grouping coclassification dissimilarity matrices.
-
-\section{Results}
-
-% DBS: Should we add a figure that shows the fit of observed vs predicted? Are we forgetting how much that might resonate with readers and jumping ahead too quickly?
-
-% DBS: As per my comment immediately above, we need to add a reference to the partial residual plots in the supps.
-
-The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
-The {\ic} values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
-The ungrouped model gave an {\ic} value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
-\Cref{fig:ic} shows the distribution of {\ic} values from the models, with some models of interest marked.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.65\textwidth}
-	<<>>=
-		hist(brute_data$statistics[[ic]],
-			main="",
-			xlab=ic_name,
-			xaxs='i',
-			yaxs='i',
-			ylim=c(0,6000)
-		)
-		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
-		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
-	@
-	\end{subfigure}
-
-	\caption{%
-		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
-		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
-		The dotted purple line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
-	}
-	\label{fig:ic}
-\end{figure}
-
-The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
-\Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
-The ungrouped model had an {\ic} just \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]] - min(brute_data$statistics[[ic]])}} units from the most parsimonious model, but the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
-
-Considering only models in which the rows and columns were grouped using the same grouping, the {\ic} values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
-The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; this was more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
-This indicates that the most parsimonious model was not especially likely to be one that grouped the rows and columns equivalently.
-
-\begin{figure}
-	\centering
-
-	<<>>=
-		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
-		best_row_grouping <- brute_data$get_row_grouping(best_model_index)
-		best_col_grouping <- brute_data$get_col_grouping(best_model_index)
-		best_alpha_matrix <- brute_data$parameters[[best_model_index]]$alpha_values
-
-		ordering <- get_ordering(list(best_row_grouping, best_col_grouping))
-		best_species_names <- brute_data$species_names[ordering]
-		best_row_grouping <- best_row_grouping[ordering]
-		best_col_grouping <- best_col_grouping[ordering]
-		best_alpha_matrix <- best_alpha_matrix[ordering,ordering]
-
-		best_row_coclassification <- as_coclassification_matrix(best_row_grouping)
-		best_col_coclassification <- as_coclassification_matrix(best_col_grouping)
-	@
-
-	\begin{subfigure}{\textwidth}
-		\centering
-		<<>>=
-			grouped_alpha_matrix(
-				best_species_names,
-				best_row_grouping,
-				best_col_grouping,
-				best_alpha_matrix
-			)
-		@
-		\caption{Grouped alpha matrix}
-		\label{fig:best-alpha-matrix}
-	\end{subfigure}
-
-	\bigskip
-
-	\begin{subfigure}{0.49\textwidth}
-		\centering
-		<<>>=
-			minimal_coclassification_kable(
-				best_col_coclassification,
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
-		@
-		\caption{Coclassification of competitive effects\\(columns)}
-		\label{fig:best-coclassification-cols}
-	\end{subfigure}
-	%
-	\begin{subfigure}{0.49\textwidth}
-		\centering
-		<<>>=
-			minimal_coclassification_kable(
-				best_row_coclassification,
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
-		@
-		\caption{Coclassification of competitive responses\\(rows)}
-		\label{fig:best-coclassification-rows}
-	\end{subfigure}
-
-	\caption{%
-		The groupings and competition coefficients of a grouped Lotka--Volterra model fitted to the six studied \emph{Drosophila} species.
-		Where results are for the single model with the best {\ic} (\probnum{\Sexpr{brute_data$statistics[best_model_index,ic]}}).
-		\Subref{fig:best-alpha-matrix} We show the inferred matrix of competition coefficients, where a competition coefficient in a block represents the same coefficient being used for multiple interactions (per the identified groupings).
-		\Subref{fig:best-coclassification-cols} and \subref{fig:best-coclassification-rows} We show the coclassification matrices derived from the groupings of the columns and rows, respectively.
-		Species have been reordered so that species that were grouped together appear adjacent, and the ordering is the same in all of \subref{fig:best-alpha-matrix}, \subref{fig:best-coclassification-cols}, and \subref{fig:best-coclassification-rows}.
-	}
-	\label{fig:best-model}
-\end{figure}
-
-\subsection{Coclassification of species}
-
-Overall, no pair of species could confidently be said to be coclassified together in the row or column groupings; the highest probability of classification was \SI[round-mode=figures,round-precision=3]{\Sexpr{max(weighted_col_coclassification_matrix - diag(num_species), weighted_row_coclassification_matrix - diag(num_species))*100}}{\percent} (\cref{fig:coclassification}).
-However, some pairs of species were far more likely to be coclassified than others, suggesting some structure to the best groupings.
-
-The structure of the coclassification matrices was very different in the row groups than in the column groups.
-That is, most pairs of species which had a high probability of being coclassified in one grouping had a very low probability of being coclassified in the other grouping.
-Only one pair of species had a relatively high probability of being coclassified in both groupings: \emph{D. pallidifrons} and \emph{D. sulfurigaster}.
-Overall, more coclassification occurred in the row groupings than in the column groupings.
-A Mantel test of the coclassification matrix for the rows against that for the columns showed that there is no significant correlation between the two ($\mantelstat=\cornum{\Sexpr{mantel_cor(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(weighted_col_coclassification_matrix, weighted_row_coclassification_matrix)}}$).
-Neither the row nor column coclassification matrix was significantly correlated with a dissimilarity matrix based on species body size (column: $\mantelstat=\cornum{\Sexpr{mantel_cor(col_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(col_distance_matrix, body_weight_distance_matrix)}}$; row: $\mantelstat=\cornum{\Sexpr{mantel_cor(row_distance_matrix, body_weight_distance_matrix)}}$, $p=\probnum{\Sexpr{mantel_p(row_distance_matrix, body_weight_distance_matrix)}}$).
-
-A relatively high likelihood of coclassification in the row groupings was typically transitive: for example, \emph{D.
-birchii}, \emph{D.
-pallidifrons} and \emph{D.
-sulfurigaster} each had a relatively high probability of being coclassified with one another.
-More intransitivity was observed in the column groupings: \emph{D.
-pallidifrons} had a relatively high probability of being coclassified with \emph{D.
-sulfurigaster}, and \emph{D.
-sulfurigaster} had a substantial probability of being coclassified with \emph{D.
-simulans}, but \emph{D.
-pallidifrons} had a much lower probability of being coclassified with \emph{D.
-simulans}.
-
-% DBS: But the fact that the labels in figure 3 say effects and responses reminds me of a lingering "doubt" I had when reading the main text.
-We talk almost entirely about rows and columns but there are a number of junctures where I feel like it would be easier to follow for people who aren't us if we were talking about responses and effects.
-As long as we're consistent, I'm fine either way.
-But we need to remember we're writing the paper for the audience and not for ourselves.
-;)
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{\textwidth}
-		\centering
-		<<>>=
-			weighted_coclassification_kable(
-				weighted_col_coclassification_matrix[species_output_order,species_output_order],
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
-		@
-		\caption{Coclassification of competitive effects}
-		\label{fig:coclassification-cols}
-	\end{subfigure}
-
-	\bigskip
-
-	\begin{subfigure}{\textwidth}
-		\centering
-		<<>>=
-			weighted_coclassification_kable(
-				weighted_row_coclassification_matrix[species_output_order,species_output_order],
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
-		@
-		\caption{Coclassification of competitive responses}
-		\label{fig:coclassification-rows}
-	\end{subfigure}
-
-	\caption{%
-		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by Akaike weights.
-		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
-		\Subref{fig:coclassification-cols} We show the grouping of species' competitive effects upon other species (columns of the interaction matrix).
-\subref{fig:coclassification-rows} We show the grouping of species' responses to competition (rows of the interaction matrix).
-	}
-	\label{fig:coclassification}
-\end{figure}
-
-\section{Discussion}
-
-We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
-Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}) than was leaving them ungrouped.
-Which grouping would give the most parsimonious model, however, could not be determined with confidence.
-This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds,kirwan2009diversity,boulangeat2012improving}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic,wilcox2018evolutionary}.
-It also contrasts with previous studies that have succeeded in finding clear groups in other ecological contexts, such as in food webs \parencite{krause2003compartments,allesina2009food} or plant--pollinator networks \parencite{olesen2007modularity}.
-
-One possible explanation for our results is that species simply do not group to the same extent in a quantitative competitive context as in a binary interaction networks.
-That said, the results also suggest that this is unlikely as grouping was useful for increasing parsimony.
-In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
-All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
-A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown less equivocal groupings.
-Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
-Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing an application of this approach to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
-As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
-
-While the results could not definitely identify a single best grouping, it was clear that the model-supported groupings differed for the rows and columns.
-That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
-In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1990components, goldberg1991competitive}.
-Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
-Our results recommend more explicit questioning, and even testing, of this assumption when building future species interaction models.
-%TODO: Discuss the fact that species were coclassified more in the rows than in the columns?
-
-The intransitivity of coclassification for some sets of species even suggests that there may not be a single ``best'' grouping of the species, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
-A single trait like body size might therefore not be able to capture the multivariate nature of species' competitive niches \parencite{blonder2018hypervolume}.
-This could indicate that a Bayesian approach is worth exploring in the future, in which the outcome is not a definitive grouping but a distribution of valid groupings.
-Alternatively, it may suggest adopting a mixed-membership approach in which a species can belong to more than one group \parencite{airoldi2008mixed}, reminiscent of the community-level drivers of \textcite{ovaskainen2017species}.
-
-\FloatBarrier
-\printbibliography
 \end{document}

### 2022-07-26 supp.rnw
Add model fit and partial residual plots to the supplementary material.

@@
 
+%TODO: x and y axis labels.
+<<echo=FALSE>>=
+	model_fit_plot <- function(parameters) {
+		plot_df <- data.frame(
+			observed = input_data$response_vector,
+			fitted = input_data$get_fitted_values(parameters),
+			focal = species_dat$name[input_data$focal_vector]
+		)
+		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
+			ggplot2::geom_point() +
+			ggplot2::geom_smooth(method = lm, formula = y~x) +
+			ggplot2::geom_abline(slope = 1, intercept = 0) +
+			ggplot2::facet_wrap(.~focal)
+		return(plot)
+	}
+
+	partial_residuals_plot <- function(parameters) {
+		#TODO: Give species names on facet plot labels.
+		plot_df <- c()
+		for(row_index in 1:num_species) {
+			for(col_index in 1:num_species) {
+				temp_df <- data.frame(
+					y = input_data$get_partial_residuals(parameters, row_index, col_index),
+					x = input_data$get_partial_residuals_x(row_index, col_index)
+				)
+				temp_df$row_index <- rep(row_index, nrow(temp_df))
+				temp_df$col_index <- rep(col_index, nrow(temp_df))
+				plot_df <- rbind(plot_df, temp_df)
+			}
+		}
+
+		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
+			ggplot2::geom_point() +
+			ggplot2::geom_smooth(method = lm, formula = y~x) +
+			ggplot2::facet_grid(row_index~col_index)
+		return(plot)
+	}
+
+	best_parameters <- brute_data$parameters[[which.max(brute_data$statistics[[ic_weight]])]]
+	average_parameters <- brute_data$average_parameters
+@
+
+%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
+%TODO: Add "S" to figure numbers.
+\begin{figure}
+	<<echo=FALSE>>=
+		plot(model_fit_plot(best_parameters))
+	@
+
+	\caption{%
+		Plot of model fit using the most parsimonious model.
+	}
+	\label{fig:model-fit-best}
+\end{figure}
+
+\begin{figure}
+	<<echo=FALSE>>=
+		plot(model_fit_plot(average_parameters))
+	@
+
+	\caption{%
+		Plot of model fit using the model average model.
+	}
+	\label{fig:model-fit-average}
+\end{figure}
+
+\begin{figure}
+	<<echo=FALSE>>=
+		plot(partial_residuals_plot(best_parameters))
+	@
+
+	\caption{%
+		Partial residuals plot using the most parsimonious model.
+	}
+	\label{fig:partial-residual-best}
+\end{figure}
+
+\begin{figure}
+	<<echo=FALSE>>=
+		plot(partial_residuals_plot(average_parameters))
+	@
+
+	\caption{%
+		Partial residuals plot using the model average model.
+	}
+	\label{fig:partial-residual-average}
+\end{figure}
+
 \end{document}

### 2022-08-02 supp.rnw
Add "S" to figure numbers in the supplementary.
Add axis labels to the supplementary plots of model fit.

@@
 \begin{document}
+\beginsupplementary
 \maketitle
@@
 			ggplot2::geom_abline(slope = 1, intercept = 0) +
-			ggplot2::facet_wrap(.~focal)
+			ggplot2::facet_wrap(.~focal) +
+			labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
 		return(plot)
@@
 %TODO: Reorder partial residual/model fit plots to use same species order as other figures.
-%TODO: Add "S" to figure numbers.
 \begin{figure}

### 2022-08-02 supp.rnw
Describe the lines on the supplementary model fit plots in their captions.
Add missing namespace on a function.

--- 2022-07-26 supp.rnw
@@
 			ggplot2::geom_abline(slope = 1, intercept = 0) +
-			ggplot2::facet_wrap(.~focal)
+			ggplot2::facet_wrap(.~focal) +
+			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
 		return(plot)
@@
 		Plot of model fit using the model average model.
+		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
+		The black line shows $y=x$.
 	}
@@
 		Partial residuals plot using the most parsimonious model.
+		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
+		The black line shows $y=x$.
 	}

### 2022-08-02 supp.rnw
Fix erroneous captions in the supplementary.
Add axis labels to the supplementary partial residual plots.

@@
 
-%TODO: x and y axis labels.
 <<echo=FALSE>>=
@@
 			ggplot2::geom_smooth(method = lm, formula = y~x) +
-			ggplot2::facet_grid(row_index~col_index)
+			ggplot2::facet_grid(row_index~col_index) +
+			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)")
 		return(plot)
@@
 		Plot of model fit using the most parsimonious model.
+		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
+		The black line shows $y=x$.
 	}
@@
 		Partial residuals plot using the most parsimonious model.
-		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
-		The black line shows $y=x$.
 	}

### 2022-08-02 supp.rnw
Ensure the supplementary partial residual are labelled with species names.

--- 2022-08-02 supp.rnw
@@
 	partial_residuals_plot <- function(parameters) {
-		#TODO: Give species names on facet plot labels.
 		plot_df <- c()
@@
 
+		plot_df$row_species <- species_dat$name[plot_df$row_index]
+		plot_df$col_species <- species_dat$name[plot_df$col_index]
+
 		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
@@
 			ggplot2::geom_smooth(method = lm, formula = y~x) +
-			ggplot2::facet_grid(row_index~col_index)
+			ggplot2::facet_grid(row_species~col_species) +
+			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)") +
+			ggplot2::theme(strip.text = ggplot2::element_text(size=7))
 		return(plot)

### 2022-08-03 supp.rnw
Reorder species in supplementary plots to the same order as coclassification matrices.

@@
 <<echo=FALSE>>=
-	model_fit_plot <- function(parameters) {
+	order_species <- function(vec, names, order) {
+		factor(vec, levels = names[order])
+	}
+
+	model_fit_plot <- function(parameters, species_output_order) {
 		plot_df <- data.frame(
@@
 		)
+
+		plot_df$focal <- order_species(plot_df$focal, species_dat$name, species_output_order)
+
 		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
@@
 
-	partial_residuals_plot <- function(parameters) {
+	partial_residuals_plot <- function(parameters, species_output_order) {
 		plot_df <- c()
@@
 		plot_df$col_species <- species_dat$name[plot_df$col_index]
+		plot_df$row_species <- order_species(plot_df$row_species, species_dat$name, species_output_order)
+		plot_df$col_species <- order_species(plot_df$col_species, species_dat$name, species_output_order)
 
@@
 	<<echo=FALSE>>=
-		plot(model_fit_plot(best_parameters))
+		plot(model_fit_plot(best_parameters, species_output_order))
 	@
@@
 	<<echo=FALSE>>=
-		plot(model_fit_plot(average_parameters))
+		plot(model_fit_plot(average_parameters, species_output_order))
 	@
@@
 	<<echo=FALSE>>=
-		plot(partial_residuals_plot(best_parameters))
+		plot(partial_residuals_plot(best_parameters, species_output_order))
 	@
@@
 	<<echo=FALSE>>=
-		plot(partial_residuals_plot(average_parameters))
+		plot(partial_residuals_plot(average_parameters, species_output_order))
 	@

### 2022-08-03 supp.rnw
Fix incorrect words being pluralised in the partial residual plots' captions.

@@
 
-	partial_residuals_plot <- function(parameters, species_output_order) {
+	partial_residual_plot <- function(parameters, species_output_order) {
 		plot_df <- c()
@@
 
-%TODO: Reorder partial residual/model fit plots to use same species order as other figures.
 \begin{figure}
@@
 	<<echo=FALSE>>=
-		plot(partial_residuals_plot(best_parameters, species_output_order))
+		plot(partial_residual_plot(best_parameters, species_output_order))
 	@
@@
 	\caption{%
-		Partial residuals plot using the most parsimonious model.
+		Partial residual plots using the most parsimonious model.
 	}
@@
 	<<echo=FALSE>>=
-		plot(partial_residuals_plot(average_parameters, species_output_order))
+		plot(partial_residual_plot(average_parameters, species_output_order))
 	@
@@
 	\caption{%
-		Partial residuals plot using the model average model.
+		Partial residual plots using the model average model.
 	}

### 2022-08-03 supp.rnw
Explain the supplementary partial residual plots in their captions.

@@
 	\caption{%
-		Partial residual plots using the most parsimonious model.
+		Partial residual plots showing the effects of competition coefficients in the most parsimonious model.
+		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
 	}
@@
 	\caption{%
-		Partial residual plots using the model average model.
+		Partial residual plots showing the effects of competition coefficients in model average model.
+		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
 	}

### 2022-08-03 supp.rnw
Remove a completed TODO.
Make macros for the supplementary plots to prevent text duplication.

@@
 
+\newcommand\modelfitplotcaption[1]{%
+	\caption{%
+		Plot of model fit using the #1.
+		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
+		The black line shows $y=x$.
+	}%
+}
+\newcommand\partialresidualplotcaption[1]{%
+	\caption{%
+		Partial residual plots showing the effects of competition coefficients in the #1.
+		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
+	}%
+}
+
 \begin{figure}
@@
 
-	\caption{%
-		Plot of model fit using the most parsimonious model.
-		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
-		The black line shows $y=x$.
-	}
+	\modelfitplotcaption{most parsimonious model}
 	\label{fig:model-fit-best}
@@
 
-	\caption{%
-		Plot of model fit using the model average model.
-		The blue line shows a linear regression with \SI{95}{\percent} confidence interval.
-		The black line shows $y=x$.
-	}
+	\modelfitplotcaption{model average model}
 	\label{fig:model-fit-average}
@@
 
-	\caption{%
-		Partial residual plots showing the effects of competition coefficients in the most parsimonious model.
-		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
-	}
+	\partialresidualplotcaption{most parsimonious model}
 	\label{fig:partial-residual-best}
@@
 
-	\caption{%
-		Partial residual plots showing the effects of competition coefficients in model average model.
-		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
-	}
+	\partialresidualplotcaption{model average model}
 	\label{fig:partial-residual-average}

### 2022-08-03 supp.rnw
Add a line to the partial residual plots showing the fitted alpha value.

@@
 				temp_df$col_index <- rep(col_index, nrow(temp_df))
+				temp_df$alpha <- parameters$alpha_values[row_index, col_index]
 				plot_df <- rbind(plot_df, temp_df)
@@
 			ggplot2::geom_smooth(method = lm, formula = y~x) +
+			ggplot2::geom_abline(ggplot2::aes(slope = alpha, intercept = 0)) +
 			ggplot2::facet_grid(row_species~col_species) +
@@
 		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
+		The black line shows, by its slope, the alpha value fitted by the model.
+		The blue line shows a linear regression fitted to the plotted points, with \SI{95}{\percent} confidence interval.
 	}%

### 2022-08-03 supp.rnw
Change "fitted" to "predicted" in the supplementary model fit plot axis labels.
To demonstrate that this is the predicted output from the whole model,
not just the fitted growth rate parameter.

@@
 			ggplot2::facet_wrap(.~focal) +
-			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Fitted growth rate (per capita)")
+			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Predicted growth rate (per capita)")
 		return(plot)

### 2022-08-08 supp.rnw
Add short versions of the supplementary figure captions.
Adding xr-hyper breaks with siunitx commands in the captions.
The short captions don't feature any siunitx commands.
As such, this will allow adding xr-hyper.

@@
 \newcommand\modelfitplotcaption[1]{%
-	\caption{%
+	\caption[%
+		Plot of model fit using the #1.
+	]{%
 		Plot of model fit using the #1.
@@
 \newcommand\partialresidualplotcaption[1]{%
-	\caption{%
+	\caption[%
+		Partial residual plots showing the effects of competition coefficients in the #1.
+	]{%
 		Partial residual plots showing the effects of competition coefficients in the #1.

### 2022-08-08 article.rnw
Set up xr to link from the article to the supplementary.
Reference the supplementary figures in the main text.
Update a bioRxiv article reference to the published version.

@@
 @
+
+\externaldocument{supp}
 
@@
 
-One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives, weiss2021disentangling}.
+One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{mutshinda2009drives, weiss2022disentangling}.
 However, weak interactions have been shown to be very important to the stability of ecological communities \parencite{mccann1998weak,neutel2002stability,wootton2016many}.
@@
 
-In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional (i.e., trait) similarity \parencite{uriarte2004spatially,ovaskainen2017species,weiss2021disentangling,martyn2021identifying}.
+In ecological contexts, such groups have been defined \emph{a priori} by phylogeny at some taxonomic level or by functional (i.e., trait) similarity \parencite{uriarte2004spatially,ovaskainen2017species,martyn2021identifying}.
 The argument for grouping based on phylogeny relies on the principle that closely related species will fill similar ecological niches, and hence will interact with other species in a similar fashion \parencite{godoy2014phylogenetic,webb2002phylogenies,darwin1859origin}.
@@
 
-% DBS: Should we add a figure that shows the fit of observed vs predicted? Are we forgetting how much that might resonate with readers and jumping ahead too quickly?
-
-% DBS: As per my comment immediately above, we need to add a reference to the partial residual plots in the supps.
-
+Plots of predicted against observed values and partial residual plots for the fitted alpha values are shown in \cref{fig:model-fit-best,fig:model-fit-average,fig:partial-residual-best,fig:partial-residual-average}.
 The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.

### 2022-08-08 article.rnw
Change the word "correctness" to "accuracy".

@@
 Such data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
-In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
+In this study, we investigate the usefulness and accuracy of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
 We fit a Lotka--Volterra competition model to these data to find the groupings that give the most parsimonious model, and we then compare these groupings to similarity based upon a species trait (body size).

### 2022-08-08 article.rnw
Correct grammar.

@@
 Second, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the models grouping species equivalently in their competitive effects and competitive responses were more parsimonious than all other models.
-To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a equally sized random subset of the models.
+To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of an equally sized random subset of the models.
 

### 2022-08-08 article.rnw
Add an example of different traits governing competitive effect and response.

@@
 That is, species that are similar in their response to competition may not be similar in the competitive effects they have on other species, and vice versa.
-In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1990components, goldberg1991competitive}.
+In hindsight, this should not be overly surprising since it is known that different traits govern species competitive effects than govern their responses \parencite{goldberg1990components, goldberg1991competitive}; for example shading effect and shade tolerance in plants.
 Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.

### 2022-08-08 article.rnw
Change the bin width on the AIC histogram to 2.
Per Hao Ran's suggestion, to ease reading of "significantly different"
AIC values.

@@
 	<<>>=
+		get_breaks <- function(x, bin_width) {
+			lower_bound <- min(x) - min(x)%%bin_width
+			upper_bound <- max(x) + (bin_width - max(x)%%bin_width)%%bin_width
+			return(seq(lower_bound, upper_bound, by = bin_width))
+		}
 		hist(brute_data$statistics[[ic]],
@@
 			yaxs='i',
-			ylim=c(0,6000)
+			ylim=c(0,2500),
+			breaks=get_breaks(brute_data$statistics[[ic]], 2)
 		)

### 2022-08-08 article.rnw
Add the acknowledgements.
Change weighted_coclassification_kable and grouped_alpha_matrix to return strings.
They previously directly printed their output, which prohibited saving it usefully.

@@
 		<<>>=
-			grouped_alpha_matrix(
+			cat(grouped_alpha_matrix(
 				best_species_names,
@@
 				best_alpha_matrix
-			)
+			))
 		@
@@
 		<<>>=
-			minimal_coclassification_kable(
+			cat(minimal_coclassification_kable(
 				best_col_coclassification,
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			))
 		@
@@
 		<<>>=
-			minimal_coclassification_kable(
+			cat(minimal_coclassification_kable(
 				best_row_coclassification,
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			))
 		@
@@
 		<<>>=
-			weighted_coclassification_kable(
+			cat(weighted_coclassification_kable(
 				weighted_col_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			))
 		@
@@
 		<<>>=
-			weighted_coclassification_kable(
+			cat(weighted_coclassification_kable(
 				weighted_row_coclassification_matrix[species_output_order,species_output_order],
 				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			))
 		@
@@
 
+\section{Acknowledgements}
+
+I would like to thank Hao Ran Lai for feedback on a draft of the manuscript.
+
+DBS is also grateful for the support of the Marsden Fund Council, from New Zealand Government funding (grant 16-UOC-008).
+
 \FloatBarrier

### 2022-08-08 r/coclassification-table.R

@@ -139,9 +139,11 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 		outer_tab <- matrix_tab
 	}
 	
-	cat(length_definition)
-	cat(colour_definitions)
-	cat(outer_tab)
+	return(paste0(
+		length_definition,
+		colour_definitions,
+		outer_tab
+	))
 }
 
 #A shortcut for a minimal version.

### 2022-08-08 r/grouped-matrix.R

@@ -237,9 +237,11 @@ grouped_alpha_matrix <- function(species_names, row_grouping, col_grouping, mat,
 	
 	row_lines <- paste(sapply(1:num_species, get_row), collapse="")
 	
-	cat(length_definition)
-	cat(begin)
-	cat(label_line)
-	cat(row_lines)
-	cat(end)
+	return(paste0(
+		length_definition,
+		begin,
+		label_line,
+		row_lines,
+		end
+	))
 }

### 2022-08-08 supp.rnw
Add an explanatory comment to the order_species function in the supplementary.
Its not otherwise clear what it's for.

@@
 	order_species <- function(vec, names, order) {
+		#Takes a vector of species names and redefines them as a factor with correctly ordered levels.
+		#This forces ggplot to use them in the correct order for a facet plot.
 		factor(vec, levels = names[order])

### 2022-08-08 r/coclassification-table.R
Force knitr::kable to always use LaTeX format.
Running it outside of the rnw compilation allows it to default to
other formats, which we don't want.

@@ -111,7 +111,7 @@ weighted_coclassification_kable <- function(mat, colourmap="hot", diagonal_colou
 		ncol=1))
 	}
 	
-	matrix_tab <- knitr::kable(string_mat, escape=FALSE, booktabs=TRUE,
+	matrix_tab <- knitr::kable(string_mat, format="latex", escape=FALSE, booktabs=TRUE,
 		align=ifelse(has_names,
 			c(rep("c",ncol(mat)),"l"),
 			rep("c",ncol(mat))

### 2022-08-08 article.rnw
Move code for the figures into the article-analysis script.

--- 2022-08-08 article.rnw
@@
 	<<>>=
-		hist(brute_data$statistics[[ic]],
-			main="",
-			xlab=ic_name,
-			xaxs='i',
-			yaxs='i',
-			ylim=c(0,6000)
-		)
-		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
-		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
+		ic_histogram(brute_data)
 	@
@@
 
-	<<>>=
-		best_model_index <- which.max(brute_data$statistics[[ic_weight]])
-		best_row_grouping <- brute_data$get_row_grouping(best_model_index)
-		best_col_grouping <- brute_data$get_col_grouping(best_model_index)
-		best_alpha_matrix <- brute_data$parameters[[best_model_index]]$alpha_values
-
-		ordering <- get_ordering(list(best_row_grouping, best_col_grouping))
-		best_species_names <- brute_data$species_names[ordering]
-		best_row_grouping <- best_row_grouping[ordering]
-		best_col_grouping <- best_col_grouping[ordering]
-		best_alpha_matrix <- best_alpha_matrix[ordering,ordering]
-
-		best_row_coclassification <- as_coclassification_matrix(best_row_grouping)
-		best_col_coclassification <- as_coclassification_matrix(best_col_grouping)
-	@
-
 	\begin{subfigure}{\textwidth}
@@
 		<<>>=
-			grouped_alpha_matrix(
-				best_species_names,
-				best_row_grouping,
-				best_col_grouping,
-				best_alpha_matrix
-			)
+			cat(best_model_output_table$grouped_alpha_matrix)
 		@
@@
 		<<>>=
-			minimal_coclassification_kable(
-				best_col_coclassification,
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			cat(best_model_output_table$row_coclassification_table)
 		@
@@
 		<<>>=
-			minimal_coclassification_kable(
-				best_row_coclassification,
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			cat(best_model_output_table$row_coclassification_table)
 		@
@@
 		<<>>=
-			weighted_coclassification_kable(
-				weighted_col_coclassification_matrix[species_output_order,species_output_order],
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			cat(weighted_coclassification_matrices$col)
 		@
@@
 		<<>>=
-			weighted_coclassification_kable(
-				weighted_row_coclassification_matrix[species_output_order,species_output_order],
-				colourmap="coclassification", diagonal_colour="coclassification diagonal"
-			)
+			cat(weighted_coclassification_matrices$row)
 		@

### 2022-08-08 supp.rnw
Move code for the figures into the article-analysis script.

--- 2022-08-08 supp.rnw
@@
 \maketitle
-
-<<echo=FALSE>>=
-	order_species <- function(vec, names, order) {
-		factor(vec, levels = names[order])
-	}
-
-	model_fit_plot <- function(parameters, species_output_order) {
-		plot_df <- data.frame(
-			observed = input_data$response_vector,
-			fitted = input_data$get_fitted_values(parameters),
-			focal = species_dat$name[input_data$focal_vector]
-		)
-
-		plot_df$focal <- order_species(plot_df$focal, species_dat$name, species_output_order)
-
-		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = observed, y = fitted)) +
-			ggplot2::geom_point() +
-			ggplot2::geom_smooth(method = lm, formula = y~x) +
-			ggplot2::geom_abline(slope = 1, intercept = 0) +
-			ggplot2::facet_wrap(.~focal) +
-			ggplot2::labs(x = "Observed growth rate (per capita)", y = "Predicted growth rate (per capita)")
-		return(plot)
-	}
-
-	partial_residual_plot <- function(parameters, species_output_order) {
-		plot_df <- c()
-		for(row_index in 1:num_species) {
-			for(col_index in 1:num_species) {
-				temp_df <- data.frame(
-					y = input_data$get_partial_residuals(parameters, row_index, col_index),
-					x = input_data$get_partial_residuals_x(row_index, col_index)
-				)
-				temp_df$row_index <- rep(row_index, nrow(temp_df))
-				temp_df$col_index <- rep(col_index, nrow(temp_df))
-				temp_df$alpha <- parameters$alpha_values[row_index, col_index]
-				plot_df <- rbind(plot_df, temp_df)
-			}
-		}
-
-		plot_df$row_species <- species_dat$name[plot_df$row_index]
-		plot_df$col_species <- species_dat$name[plot_df$col_index]
-		plot_df$row_species <- order_species(plot_df$row_species, species_dat$name, species_output_order)
-		plot_df$col_species <- order_species(plot_df$col_species, species_dat$name, species_output_order)
-
-		plot <- ggplot2::ggplot(plot_df, ggplot2::aes(x = x, y = y)) +
-			ggplot2::geom_point() +
-			ggplot2::geom_smooth(method = lm, formula = y~x) +
-			ggplot2::geom_abline(ggplot2::aes(slope = alpha, intercept = 0)) +
-			ggplot2::facet_grid(row_species~col_species) +
-			ggplot2::labs(x = "Number of individuals of competing species", y = "Partial residual growth rate of focal species (per capita)") +
-			ggplot2::theme(strip.text = ggplot2::element_text(size=7))
-		return(plot)
-	}
-
-	best_parameters <- brute_data$parameters[[which.max(brute_data$statistics[[ic_weight]])]]
-	average_parameters <- brute_data$average_parameters
-@
 
@@
 	<<echo=FALSE>>=
-		plot(model_fit_plot(best_parameters, species_output_order))
+		plot(best_model_fit_plot)
 	@
@@
 	<<echo=FALSE>>=
-		plot(model_fit_plot(average_parameters, species_output_order))
+		plot(average_model_fit_plot)
 	@
@@
 	<<echo=FALSE>>=
-		plot(partial_residual_plot(best_parameters, species_output_order))
+		plot(best_partial_residual_plot)
 	@
@@
 	<<echo=FALSE>>=
-		plot(partial_residual_plot(average_parameters, species_output_order))
+		plot(average_partial_residual_plot)
 	@

### 2022-08-15 preamble.rnw
Add "S" to figure numbers in the supplementary.
Set up xr to link from the article to the supplementary.
Change the cleveref range conjuntion to an en-dash.
Load xr-hyper to fix the hyperlinks tothe supplementary.
Move code for the figures into the article-analysis script.
Remove unnecessary uses of the knitr namespace.
knitr is loaded in the Makefile,
so explicitly specifying the namespace is unnecessary.

@@
 \usepackage{arydshln}
+\usepackage{xr}
+\usepackage{xr-hyper}
 
@@
 
+\newcommand{\crefrangeconjunction}{--}
+
+%Supplementary
+\newcommand{\beginsupplementary}{%
+	\setcounter{table}{0}
+	\renewcommand{\thetable}{S\arabic{table}}%
+	\setcounter{figure}{0}
+	\renewcommand{\thefigure}{S\arabic{figure}}%
+}
+
 %Title Page
@@
 <<include=FALSE>>=
-	knitr::opts_chunk$set(echo = FALSE) #Never show the code, only output.
-	knitr::opts_chunk$set(results = 'asis') #Text is grey without this.
+	opts_chunk$set(echo = FALSE) #Never show the code, only output.
+	opts_chunk$set(results = 'asis') #Text is grey without this.
 	knit_hooks$set(inline = function(x) {x}) #Disable automatic formatting of in-line material.
@@
 
-\pgfplotsset{%
-	colormap={coclassification}{color=(white) color=(red)}
-}
-\colorlet{coclassification diagonal}{black!20}
+<<>>=
+	cat(coclassification_colour_setup)
+@

### 2022-08-16 preamble.rnw
Fix a bug where the article/supplementary could wind up with one another's figures.

@@
 <<include=FALSE>>=
+	#Compiling more than one document in the same directory leads to theior figures overwriting one another.
+	#This can lead to including the wrong figures when the TeX files are compiled into PDFs.
+	#As such, we set different directories for each file's figures.
+	#'jobname' must be set in the Makefile as the parent document is compiled.
+	opts_chunk$set(fig.path = paste0("figures/", jobname, "/"))
+@
+
+<<include=FALSE>>=
 	library(magrittr)
